### 2014-06-26 Choosing R3 Relations.tex
Added Relation and Proof of Equivalence

\documentclass[11pt]{amsart}

%The package below let's us add todos to the document in a way that will stand out at a glance.  It will also list all of the current things to do, with their respective page numbers on the first page of the document.  You can add a todo like this:
%
%		Text text text \todo{change this text to something useful!}
%
%Among other things, you can edit the color of a todo:
%
%		\todo[color=\ltblue]{this todo will have a light blue background!}
%
%And you can include the todo as a line in the text, rather than in the margins:
%
%		\todo[inline]{this will appear in the middle of the page}

\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
\def\ltblue{blue!20!white}
\def\ltgreen{green!20!white}

\usepackage{amsmath,amssymb,amsthm, MnSymbol}

\newtheorem{thm}{Theorem}[section]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{conj}[thm]{Conjecture}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rem}[thm]{Remark}

\makeatletter
\providecommand\@dotsep{5}
\def\listtodoname{List of Todos}
\def\listoftodos{\@starttoc{tdo}\listtodoname}
\makeatother

\begin{document}

%This adds the list of todos to the first page.
\listoftodos
\newpage

It's not immediately obvious which relations analogous to the original R3 relations we want to choose.  Here we try out several possible relations, in each case trying to prove an analogous lemma to Lemma 4.1 in Barot and Marsh's paper.

\section{Attempts}

\subsection{}
Here we test out the set of relations R3' where if $i_{a_0}, i_{a_1},\ldots,i_{a_{d-1}},i_{a_0}$ is a chordless cycle with all weights 1, then we add in the relation 
$$s_0s_1^{-1}s_2s_3^{-1}\cdots s_{d-2}^{(-1)^{d-2}} s_{d-1}s_{d-2}^{(-1)^{d-1}}\cdots s_4^{-1}s_3s_2^{-1}s_1 = s_1^{-1}s_2s_3^{-1}\cdots s_{d-2}^{(-1)^{d-2}} s_{d-1}s_{d-2}^{(-1)^{d-1}}\cdots s_4^{-1}s_3s_2^{-1}s_1s_0$$

We then have

\begin{align*}
& s_{d-1}s_0^{-1}s_1s_2^{-1}s_3\cdots s_{d-3}^{(-1)^{d-2}} s_{d-2}s_{d-3}^{(-1)^{d-3}}\cdots s_4s_3^{-1}s_2s_1^{-1}s_0\\
&= s_0^{-1}s_0s_{d-1}s_0^{-1}s_1s_2^{-1}s_3\cdots s_{d-3}^{(-1)^{d-2}} s_{d-2}s_{d-3}^{(-1)^{d-3}}\cdots s_4s_3^{-1}s_2s_1^{-1}s_{d-1}s_{d-1}^{-1}s_0\\
&= s_0^{-1}s_{d-1}^{-1}s_0s_{d-1}s_1s_2^{-1}s_3\cdots s_{d-3}^{(-1)^{d-2}} s_{d-2}s_{d-3}^{(-1)^{d-3}}\cdots s_4s_3^{-1}s_2s_1^{-1}s_{d-1}s_{d-1}^{-1}s_0\\
\end{align*}

...so I don't think this direction is going to work from here, simply because I don't see a way to flip all of the generators in the middle to their inverses.

An R3 that seems promising:

\begin{defn}
Using the notation as in Barot - Marsh, given a chordless cycle C in $\gamma$ so that all edges in C have weight 1, we define $r(a, a+1) = s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}$.
\end{defn}

\begin{lem}
The relation r(a,a+1) for some vertex a $\in$ C implies the relation r(b, b+1) for all b $\in$ C.
\end{lem}
\begin{proof}
As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
\begin{align*}
& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}

\end{document}

### 2014-06-26 Choosing R3 Relations.tex
Added Lemma 5.1

@@
 \usepackage{amsmath,amssymb,amsthm, MnSymbol}
+\usepackage{enumerate}
 
@@
 \begin{defn}
-Using the notation as in Barot - Marsh, given a chordless cycle C in $\gamma$ so that all edges in C have weight 1, we define $r(a, a+1) = s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}$.
+Using the notation as in Barot - Marsh, given a chordless cycle C in $\Gamma$ so that all edges in C have weight 1, we define $r(a, a+1) = s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}$.
 \end{defn}
@@
 
+\begin{defn} Let $\Gamma$ be a weighted diagram of finite type, and suppose $\Gamma$' = $\mu_{k}(\Gamma)$. If $s_1$, \dots, $s_n$ are the generators in W$_{\Gamma}$, define: 
+$$t_{i} =
+\begin{cases}
+s_{k}s_{i}s_{k}^{-1} & \text{if there is arrow from i to k} \\
+s_{i} & \text{otherwise}
+\end{cases}$$
+\end{defn}
+
+\begin{lem} (Generalized Lemma 5.1) Let i and j be vertices of $\Gamma$.
+\begin{enumerate}[(a)]
+\item If i = k or j = k, then ($t_{i}t_{j})^{m_{ij}'/2}$ = ($t_{j}t_{i})^{m_{ij}'/2}$.
+\item If at most one of i,j is connected to k, then ($t_{i}t_{j})^{m_{ij}'/2}$ = ($t_{j}t_{i})^{m_{ij}'/2}$
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+We begin with case (a).
+Suppose that i=k.
+As in Barot-Marsh, we have that $m_{ij}$ = $m_{ij}'$, and the only nontrivial case is when there is an arrow from j to k.
+Note that $m_{ij}$ cannot be 2 in this case since there is an arrow from j to k, so suppose $m_{ij}$ = 3.
+Then we have $$s_{j}s_{k}s_{j} = s_{k}s_{j}s_{k},$$ and so $$s_{k}s_{k}s_{j}s_{k} = s_{j}s_{k}s_{j}s_{k}.$$ Multiplying both sides on the right by $s_{k}^{-1}$, we then obtain that $$s_{k}s_{k}s_{j} = s_{k}s_{j}s_{k}s_{j}s_{k}^{-1},$$ and so we find that $$t_{i}t_{j}t_{i} = s_{k}s_{k}s_{j}s_{k}^{-1}s_{k} = s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1} = t_{j}t_{i}t_{j}.$$
+
+Now suppose $m_{ij}$ = 4.
+Then $$s_{k}s_{j}s_{k}s_{j} = s_{j}s_{k}s_{j}s_{k}$$ which means that $$s_{k}s_{k}s_{j}s_{k}s_{j} = s_{k}s_{j}s_{k}s_{j}s_{k}.$$ This then gives us that $$s_{k}s_{k}s_{j}s_{k}s_{j}s_{k}^{-1} = s_{k}s_{j}s_{k}s_{j},$$ and so $$t_{i}t_{j}t_{i}t_{j} = s_{k}s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1} = s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1}s_{k} = t_{j}t_{i}t_{j}t_{i}.$$
+
+Finally, suppose $m_{ij}$ = 6.
+Then we know $$s_{k}s_{j}s_{k}s_{j}s_{k}s_{j} = s_{j}s_{k}s_{j}s_{k}s_{j}s_{k},$$ and so $$s_{k}s_{k}s_{j}s_{k}s_{j}s_{k}s_{j} = s_{k}s_{j}s_{k}s_{j}s_{k}s_{j}s_{k}.$$ Then $$s_{k}s_{k}s_{j}s_{k}s_{j}s_{k}s_{j}m_{k}^{-1} = s_{k}s_{j}s_{k}s_{j}s_{k}s_{j},$$ and so $$t_{i}t_{j}t_{i}t_{j}t_{i}t_{j} = s_{k}s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1} = s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1}s_{k} = t_{j}t_{i}t_{j}t_{i}t_{j}t_{i}.$$ A similar argument holds when j=k.
+This concludes (a).
+
+Now considering case (b), suppose i is connected to k.
+We once again have $m_{ij}$ = $m_{ij}'$, and the only nontrivial case is when the arrow points from i to k.
+Suppose $m_{ij}$ = 2.
+Then we have $$s_{i}s_{j} = s_{j}s_{i},$$ and so we have $$s_{k}s_{i}s_{j} = s_{k}s_{j}s_{i} = s_{j}s_{k}s_{i}$$ since j is not connected to k by assumption.
+But then $$t_{i}t_{j} = s_{k}s_{i}s_{k}^{-1}s_{j} = s_{k}s_{i}s_{j}s_{k}^{-1} = s_{j}s_{k}s_{i}s_{k}^{-1} = t_{j}t_{i}.$$
+
+If $m_{ij}$ = 3, then we have $s_{j}s_{k} = s_{k}s_{j}$, and so we have $s_{k}^{-1}s_{j}s_{k} = s_{j}.$ This means that $$s_{i}s_{k}^{-1}s_{j}s_{k}s_{i} = s_{i}s_{j}s_{i} = s_{j}s_{i}s_{j},$$ and we then have that $$t_{i}t_{j}t_{i} = s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1} = s_{k}s_{j}s_{i}s_{j}s_{k}^{-1} = s_{j}s_{k}s_{i}s_{k}^{-1}s_{j} = t_{j}t_{i}t_{j}.$$
+
+If $m_{ij}$ = 4, we have $s_{i}s_{j}s_{i}s_{j} = s_{j}s_{i}s_{j}s_{i}$.
+Then $$s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{j} = s_{i}s_{k}^{-1}s_{k}s_{j}s_{i}s_{j} = s_{j}s_{i}s_{k}^{-1}s_{k}s_{j}s_{i} = s_{j}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}.$$ But then conjugating the right and left sides by $s_{k}$, we find that $$s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{j}s_{k}^{-1} = s_{k}s_{j}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1},$$ and thus by the commutativity of $s_{j}$ and $s_{k}$, we have $$t_{i}t_{j}t_{i}t_{j} = s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1}s_{j} = s_{j}s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1} = t_{j}t_{i}t_{j}t_{i}.$$
+
+Finally, if $m_{ij}$ = 6, we have $s_{i}s_{j}s_{i}s_{j}s_{i}s_{j} = s_{j}s_{i}s_{j}s_{i}s_{j}s_{i}$.
+Thus conjugating by $s_{k}$ and using the commutativity of  $s_{k}$ and s$_{j}$, we find that $$s_{k}s_{i}s_{j}s_{i}s_{j}s_{i}s_{k}^{-1}s_{j} = s_{j}s_{k}s_{i}s_{j}s_{i}s_{j}s_{i}s_{k}^{-1}.$$ But this occurs if and only if $$t_{i}t_{j}t_{i}t_{j}t_{i}t_{j} = s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1}s_{j} = s_{j}s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1} = t_{j}t_{i}t_{j}t_{i}t_{j}t_{i}.$$
+
+A similar argument holds when j is connected to k, so we are done.
+\end{proof}
+
 \end{document}

### 2014-06-26 Choosing R3 Relations.tex
started ananalog to prop 5.2

@@
 
-\begin{lem} (Generalized Lemma 5.1) Let i and j be vertices of $\Gamma$.
+\begin{lem}[Generalized Lemma 5.1]\label{lem:one_connected_to_k} Let i and j be vertices of $\Gamma$.
 \begin{enumerate}[(a)]
@@
 
+\begin{lem}[Proposition 5.2 Analog] The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)$ and $(R3)$.
+\end{lem}
+
+After Lemma \ref{lem:one_connected_to_k} we have left to check the relations $(R2)$ when both $i$ and $j$ are connected to $k$ and the relations $(R3)$.
+
+Beginning with the relations $(R2)$, and following cases a-f from Corollary 2.3 in Barot and Marsh:
+
+\begin{enumerate}[a)]
+\item
+\begin{enumerate}[i)]
+\item $$t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$$
+\item $$t_it_j = s_is_j = s_js_i = t_jt_i$$
+\end{enumerate}
+\item
+\begin{enumerate}[i)]
+\item
+\begin{align*}
+t_it_jt_i &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}\\
+&= s_ks_is_js_ks_j^{-1}s_is_k^{-1}\\
+&= s_ks_js_is_ks_is_j^{-1}s_k^{-1}\\
+&= s_ks_js_ks_is_ks_j^{-1}s_k^{-1}\\
+&= s_js_ks_js_is_j^{-1}s_k^{-1}s_j\\
+&= s_js_ks_is_k^{-1}s_j\\
+&= t_it_jt_i
+\end{align*}
+\item $$t_it_j = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = t_jt_i$$
+\end{enumerate}
+\item
+\begin{enumerate}[i)]
+\item $$t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$$
+\item $$t_it_j = s_is_j = s_js_i = t_jt_i$$
+\end{enumerate}
+\item
+\begin{enumerate}[i)]
+\item
+\begin{align*}
+t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}\\
+&=s_ks_is_k^{-1}s_js_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
+&=s_ks_is_k^{-1}s_ks_js_ks_is_ks_i^{-1}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
+&=s_ks_js_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}\\
+&= e
+\end{align*}
+\end{enumerate}
+\end{enumerate}
+
 \end{document}

### 2014-06-27 Choosing R3 Relations.tex
Added Lemma 4.6

@@
 ...so I don't think this direction is going to work from here, simply because I don't see a way to flip all of the generators in the middle to their inverses.
+
+\begin{lem} (Analogue of 4.6) 
+Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
+\end{lem}
+\begin{proof}
+One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$.
+To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
+But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in W$_{\Gamma^{Op}}.$ Therefore, we are done.
+\end{proof}
 

### 2014-06-28 Choosing R3 Relations.tex
r3b_rln_fst_try_triangle

@@
 \newtheorem{rem}[thm]{Remark}
+\newcommand\tri{s_3^{-1}}
+\newcommand\tr{s_3}
+\newcommand\twi{s_2^{-1}}
+\newcommand\tw{s_2}
+\newcommand\oni{s_1^{-1}}
+\newcommand\on{s_1}
 
@@
 
+\section{Relations for 2,2,1 triangle, talk to Aaron if you think there's an error}
+
+\begin{lem}
+The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\twi\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
+\end{lem}
+\begin{proof}
+
+To show the first, equivalence, note
+\begin{align*}
+	s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 &=
+\end{align*}
+
+We only have to show the first two imply the third. We can use the first two identities to deduce $\tw\tri = \tri\on\tr\tw\tri\oni,\twi\tri=\tri\oni\tr\twi\tri\on.$ Indeed, we can see
+
+\begin{align*}
+	e &= \tw\tr\tw\tri\twi\tri
+	\\
+	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\tri\oni\tr\twi\tri\on)
+	\\
+	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\tri\oni\tr\twi\on\oni\tri\on)
+	\\
+	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
+	\\
+	&= \tw\tr(\tri\on\tr\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
+	\\
+	&= \tw\tr(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
+\end{align*}
+
+Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ NOTE: I FIGURED OUT HOW TO DO THIS BEFORE, BUT IM TOO TIRED NOW, AND I COULD HAVE MADE A MISTAKE, SO SOMEONE ELSE SHOULD CHECK, IF ITS WRONG THIS IS ALL WRONG.
+This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\twi\tri\on\tr =e.$ Plugging this in yields
+\begin{align*}
+	e &= (\oni\tr\on\tr\on\tw\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
+	\\
+	&= (\oni\tr\on\tr\on\tw\on\oni\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
+	\\
+	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
+	\\
+	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
+	\\
+	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
+\end{align*}
+
+So, since $e = \oni\tr\on\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on\oni\tri\on,$ cancelling three terms from both sides, we get $e =\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on,$ as claimed.
+\end{proof}
+
 \end{document}

### 2014-06-28 Choosing R3 Relations.tex
trying_additional_triangle_relation

@@
 
+\begin{rem}
+I am proposing to add the additonal $s_as_as_b = s_bs_as_a$ whenever there is a 2 edge pointing to $a$, a 1 edge pointing from $a$ to $b$, and a 2 edge pointing out of $b.$ I'm not sure whether this helps the rest of the problem, but it allows us to deduce the analog for $R3(b).$ We can also note that this relation would definitely not show up in the coexeter groups because $s_a^2 = e.$
+\end{rem}
+
 \begin{lem}
-The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\twi\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e. $
+Assuming the additional relation $\tw\tr\tr = \tr\tr\tw.$ The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e.
+$
 \end{lem}
@@
 
-Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ NOTE: I FIGURED OUT HOW TO DO THIS BEFORE, BUT IM TOO TIRED NOW, AND I COULD HAVE MADE A MISTAKE, SO SOMEONE ELSE SHOULD CHECK, IF ITS WRONG THIS IS ALL WRONG.
-This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\twi\tri\on\tr =e.$ Plugging this in yields
+Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\tw\tri\on\tr =e,$ if we can use the relation $\tw\tr\tr = \tr\tr\tw,$ we can obtain $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$
+
+ Plugging this in yields
 \begin{align*}

### 2014-06-28 Choosing R3 Relations.tex
small_square_commuting_relations_edit

@@
 \begin{rem}
-I am proposing to add the additonal $s_as_as_b = s_bs_as_a$ whenever there is a 2 edge pointing to $a$, a 1 edge pointing from $a$ to $b$, and a 2 edge pointing out of $b.$ I'm not sure whether this helps the rest of the problem, but it allows us to deduce the analog for $R3(b).$ We can also note that this relation would definitely not show up in the coexeter groups because $s_a^2 = e.$
+I am proposing to add the additonal $s_as_as_b = s_bs_as_a$ whenever there is a 2 edge pointing to $a$, a 1 edge pointing from $a$ to $b$, and a 2 edge pointing out of $b.$ I'm not sure whether this helps the rest of the problem, but it allows us to deduce the analog for $R3(b).$ We can also note that this relation would definitely not show up in the coexeter groups because $s_a^2 = e.$ It seems the additional relation is in fact preserved under mutations of type b or c, as in Barot and Marsh's classification.
+However, I couldn't get type d to work out.
+I think we may have to add some of these types of relations  $s_as_as_b = s_bs_as_a$ when there are 2's around, such that the mutation in d works out.
 \end{rem}
 
-\begin{lem}
+\begin{lem} (4.2 Analog)
 Assuming the additional relation $\tw\tr\tr = \tr\tr\tw.$ The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e.

### 2014-06-28 Choosing R3 Relations.tex
adding_6_additional_relations

--- 2014-06-28 Choosing R3 Relations.tex
@@
 
+\usepackage[all]{xy}
 \theoremstyle{definition}
@@
 \begin{rem}
-I am proposing to add the additonal $s_as_as_b = s_bs_as_a$ whenever there is a 2 edge pointing to $a$, a 1 edge pointing from $a$ to $b$, and a 2 edge pointing out of $b.$ I'm not sure whether this helps the rest of the problem, but it allows us to deduce the analog for $R3(b).$ We can also note that this relation would definitely not show up in the coexeter groups because $s_a^2 = e.$
+\label{even_more_relations}
+I am proposing to add the following relations whever we have the situation
+
+$\xymatrix{a \ar[r]^2 & b \ar[r]^1 & c},$ or $\xymatrix{a \ar[r]^1 & b \ar[r]^2 & c}:$
+
+Include $s_is_{i+1}^2 = s_{i+1}^2s_i,$ and $s_is_{i-1}^2 = s_{i-1}^2s_i,$ for all $i = 1,2,3.$ I believe these mutate correctly, as in cases b,c,d in Barot-Marsh.
+Note that in the above diagrams, it is fine if we have a 2 edges from a to c or c to a.
 \end{rem}
 
-\begin{lem}
-Assuming the additional relation $\tw\tr\tr = \tr\tr\tw.$ The two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e.
+\begin{lem} (4.2 Analog)
+Assuming the additional relation $\tw\tr\tr = \tr\tr\tw$ from ~\ref{even_more_relations}, the two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e.
 $

### 2014-06-28 Choosing R3 Relations.tex
added_square_r3b

@@
 \newtheorem{rem}[thm]{Remark}
+\newcommand\fri{s_4^{-1}}
+\newcommand\fr{s_4}
 \newcommand\tri{s_3^{-1}}
@@
 
+\usepackage{amsmath}
 \begin{document}
@@
 \listoftodos
+\begin{enumerate}
+	\item Verify ~\ref{square_mutation_preserved}
+	\item Verify that the relations (a),(b) are equivalent in ~\ref{4.2_analog} and ~\ref{4.4_analog}
+	\end{enumerate}
 \newpage
@@
 Using the notation as in Barot - Marsh, given a chordless cycle C in $\Gamma$ so that all edges in C have weight 1, we define $r(a, a+1) = s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}$.
+
+An equivlent relation is as follows
+
+$s_a^{-1} s_{a+1}^{-1}\cdots s_{a-1}^{-1}s_{a-2}\cdots s_a s_{a+1}^{-1}\cdots s_{a-2}^{-1} s_{a-1}\cdots s_{a+1}$
 \end{defn}
@@
 
-\begin{lem}[Proposition 5.2 Analog] The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)$ and $(R3)$.
+\begin{lem}
+\label{5.2 analog}
+[Proposition 5.2 Analog] The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)$ and $(R3)$.
 \end{lem}
@@
 
-\begin{lem} (4.2 Analog)
+\begin{lem} 
+\label{4.2_analog}
+(4.2 Analog)
 Assuming the additional relation $\tw\tr\tr = \tr\tr\tw$ from ~\ref{even_more_relations}, the two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e.
@@
 \begin{proof}
-
-To show the first, equivalence, note
-\begin{align*}
-	s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 &=
-\end{align*}
 
@@
 
-Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\tw\tri\on\tr =e,$ if we can use the relation $\tw\tr\tr = \tr\tr\tw,$ we can obtain $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$
+Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\tw\tri\on\tr =e,$ if we can use the relation $\tw\tr\tr = \tr\tr\tw.$
+To verify this, note:
+\begin{align*}
+	e &= \twi\tri\oni\tr\tw\tri\on\tr \iff \\
+	e &= \twi\tri\oni\tri\tw\tr\on\tr \iff \\
+	e &= \tri\oni\tri\twi\tr\on\tr\tw \iff \\
+	e &= \tri\twi\tr\on\tr\tw\tri\oni \iff \\
+	\tw\tr &= \tr\on\tr\on\tw\tri\oni \iff \\
+	 \tw\tr &= \oni\tr\on\tr\on\on\tw\tri\oni \iff \\
+\end{align*} 
+Where an equivalent form of $\tw\tr\tr = \tr\tr\tw.$ is used in going from the first line to the second in the above computation.
 
@@
 
+\begin{prop}
+\label{commuting_triples}
+For the case of the (2,1,2,1) square, we have $\twi\tri\tw\fri\oni\fr = \fri\oni\fr\twi\tri\tw.$
+By inverting both sides of this relation, we also obtain
+$\fri\on\fr\twi\tr\tw = \tri\tr\tw\fri\on\fr.$
+\end{prop}
+\begin{proof}
+Using the cyclic $r(1,2)$ relation we have
+\begin{align*}
+	e &= \oni\twi\tri\fri\tr\tw\on\twi\tri\fr\tr\tw\\
+	&= \oni\twi\fr\tri\fri\tw\on\twi\fr\tr\fri\tw \\
+	&= \oni\fr\twi\tri\tw\fri\on\fr\twi\tr\tw\fri \iff \\
+	e &= \fri\oni\fr\twi\tri\tw\fri\on\fr\twi\tr\tw \iff \\
+	\twi\tri\tw\fri\oni\fr &= \fri\oni\fr\twi\tri\tw
+\end{align*}
+\end{proof}
+
+\begin{lem}
+\label{4.4_analog} (Analog of 4.4) For the case of the (2,1,2,1) square, assuming the relations from ~\ref{even_more_relations} we get that the analogs of $r(1,2)^2 = e,r(3,4)^2 = e$ are equivalent, and they imply the following relation, which is an analog of R3b:
+
+$$\twi\tr\fri\on\fr\tr\tw\tri\fri\on\fr\tri\twi\tri\fri\oni\fr\tr=e.$$
+\end{lem}
+\begin{proof}
+Hailee said she showed that the analogs of $r(1,2),r(3,4)$ are equivalent.
+
+So, I will only show that these relations imply the analog of $R3b.$
+
+\begin{align*}
+	e &=\twi\tr\fri\on\fr\tr\tw\tri\fri\on\fr\tri\twi\tri\fri\oni\fr\tr \iff
+	\\
+	e &= (\twi\tr\fri\on\fr\tr)(\tw\tri\fri\on\fr\tri)(\twi\tri\fri\oni\fr\tr) \iff
+	\\
+	e &= \tr(\twi\tr\fri\on\fr\tr)\tri\tr(\tw\tri\fri\on\fr\tri)\tri\tr(\twi\tri\fri\oni\fr\tr)\tri
+	\\
+	&= (\tr\twi\tr\fri\on\fr)(\tr\tw\tri\fri\on\fr)(\tr\twi\tri\fri\oni\fr)
+\end{align*}
+
+Now observe that $$\twi\tr\tw\tri\twi = \tr\tw\twi\twi = \tr\twi\tr,$$ by ~\ref{even_more_relations} in the second equality.
+Also, $$\tw\tri\twi\tr\tw = \twi\tri\tw\tr\tw = \tr\tw\tri$$ again using ~\ref{even_more_relations} in the first equality.
+And finally,
+$$\twi\tri\twi\tri\tw = \tri\twi\tri.$$
+So, substituting these three equations in the above, we have 
+\begin{align*}
+	e &= \tr(\twi\tr\fri\on\fr\tr)\tri\tr(\tw\tri\fri\on\fr\tri)\tri\tr(\twi\tri\fri\oni\fr\tr)\tri
+	\\
+	&= ((\tr\twi\tr)\fri\on\fr)((\tr\tw\tri)\fri\on\fr)((\tr\twi\tri)\fri\oni\fr)
+	\\
+	&=((\twi\tr\tw\tr\twi)\fri\on\fr)((\tw\tri\twi\tr\tw)\fri\on\fr)((\twi\tri\twi\tr\tw)\fri\oni\fr)
+\end{align*}
+Now, using ~\ref{commuting_triples} three times, we have
+
+\begin{align*}
+	&((\twi\tr\tw\tr\twi)\fri\on\fr)((\tw\tri\twi\tr\tw)\fri\on\fr)((\twi\tri\twi\tr\tw)\fri\oni\fr)\\
+	&= (\twi\tr(\fri\on\fr\tw\tr\twi))(\twi\tr(\fri\on\fr\twi\tr\tw))(\twi\tri(\fri\oni\fr\twi\tri\tw))
+	&=
+	(\twi\tr\fri\on\tw\fr\tr\twi)(\twi\tr\fri\on\twi\fr\tr\tw)(\twi\tri\fri\oni\twi\fr\tri\tw)
+	\\
+	&= \twi\tr\fri \on\tw\on\twi\oni\twi\fr\tri\tw
+\end{align*}
+
+Therefore,
+
+\begin{align*}
+	e &= \twi\tr\fri \on\tw\on\twi\oni\twi\fr\tri\tw \iff \\
+	e &=  \on\tw\on\twi\oni\twi
+\end{align*}
+Which if of course one of our basic R2 relations.
+\end{proof}
+
+\begin{thm}
+\label{square_mutation_preserved}
+The relations described in ~\ref{even_more_relations} are permuted (and hence preserved) after mutation at any vertex.
+\end{thm}
+\begin{proof}
+This is what additionally needs to be checked in ~\ref{5.2 analog} by adding ~\ref{even_more_relations} in the cases corresponding to cycles with edges of weight 2 in the paper.
+I.e.
+it has to be checked in cases (b,c,d,e,f,g,h).
+It seems like a lot of casework, but there's a fair amount of symmetry to make it a bit easier, and I checked this in a few cases, and it seemed to work out.
+\end{proof}
+
 \end{document}

### 2014-06-29 Choosing R3 Relations.tex
edited_todo
Possible 4.2 Analogue

@@
 
-\begin{lem} (Analogue of 4.6) 
-Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
-\end{lem}
-\begin{proof}
-One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$.
-To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
-But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in W$_{\Gamma^{Op}}.$ Therefore, we are done.
-\end{proof}
-
 An R3 that seems promising:
@@
 
-An equivlent relation is as follows
+An equivalent relation is as follows
 
@@
 
-\begin{lem}
+\begin{lem} (Analogue of 4.1)
 The relation r(a,a+1) for some vertex a $\in$ C implies the relation r(b, b+1) for all b $\in$ C.
@@
 as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
+\end{proof}
+
+\begin{defn} (Possible relations for the weight 2 triangle) Given the cycle in Figure 8 of Barot-Marsh, we define the following relations
+\begin{enumerate}[(a)]
+\item $s_{1}s_{2}^{-1}s_{3}s_{2} = s_{2}^{-1}s_{3}s_{2}s_{1}$
+\item $s_{2}s_{3}^{-1}s_{1}s_{3} = s_{3}^{-1}s_{1}s_{3}s_{2}$
+\item $s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1} = e$
+\end{enumerate}
+\end{defn}
+
+\begin{lem} (Analogue of 4.2)
+In the above definition, if the generators satisfy the relations (R2'), then the relations (a) and (b) are equivalent, and the relations (a) and (b) imply the relation (c).
+\end{lem}
+
+\begin{proof}
+I haven't worked out the equivalence of (a) and (b) yet, so I'll leave it for someone else.
+
+In showing that (a) and (b) imply (c), I will underline the terms being manipulated in each line for emphasis.
+\begin{align*}
+& s_{1}s_{3}s_{1}(s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1})s_{1}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}\underline{s_{1}s_{1}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
+&= \underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{2}\underline{s_{3}^{-1}s_{1}s_{3}s_{1}}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{2}s_{1}s_{3}\underline{s_{1}s_{3}^{-1}s_{3}s_{1}^{-1}}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{2}\underline{e}s_{1}s_{3}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{2}s_{3}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= \underline{s_{2}s_{3}s_{2}}s_{3}^{-1}s_{1}s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{3}s_{2}\underline{s_{3}s_{3}^{-1}}s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{3}s_{2}\underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{3}\underline{s_{2}s_{2}^{-1}}s_{3}^{-1}s_{1}\underline{s_{3}s_{3}^{-1}}s_{1}^{-1} \\
+&= \underline{s_{3}s_{3}^{-1}}\underline{s_{1}s_{1}^{-1}} \\
+&= e
+\end{align*}
+\end{proof}
+
+\begin{lem} (Analogue of 4.6) 
+Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
+\end{lem}
+\begin{proof}
+One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$.
+To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
+But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in W$_{\Gamma^{Op}}.$ Therefore, we are done.
 \end{proof}
@@
 
-\begin{thm}
+\begin{thm}\todo{verify this}
 \label{square_mutation_preserved}

### 2014-07-02 Choosing R3 Relations.tex
small changes
made some rudimentary pictures

@@
 \usepackage{enumerate}
+
+\usepackage{tikz}
+\usepackage{tikz-cd}
+\usetikzlibrary{matrix, calc, arrows}
+\usepackage{latexsym,amsmath,amscd,amssymb,epsfig,verbatim}
+\usepackage[margin=1in,letterpaper,portrait]{geometry}
 
@@
 
-\section{Relations for 2,2,1 triangle, talk to Aaron if you think there's an error}
+\section{Relations for 2,2,1 triangle, Probably ignore this section}
 
@@
 
-\begin{thm}\todo{verify this}
+\begin{thm}
 \label{square_mutation_preserved}
@@
 It seems like a lot of casework, but there's a fair amount of symmetry to make it a bit easier, and I checked this in a few cases, and it seemed to work out.
+d
 \end{proof}
 
+\section{Diagrams}
+picure e
+\begin{tikzpicture}[baseline=-0.5ex]
+\matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+\draw[->]
+  (dl) to node[above]{2} (ur)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \end{tikzpicture}
+Picture g
+   \begin{tikzpicture}[baseline=-0.5ex]
+
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+\draw[->]
+  (dl) to node[above]{2} (ur)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \end{tikzpicture}
+    Picture i
+   \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ml) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(ml)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ml)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ml) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[right]{1}(ul)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \end{tikzpicture}
+
+    picture j
+    \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ml) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(ml)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ml)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ml) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[right]{1}(ul)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \end{tikzpicture}
 \end{document}

### 2014-07-03 Choosing R3 Relations.tex
Lemma 4.6 for Weight 2 Cases

@@
 To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
-But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in W$_{\Gamma^{Op}}.$ Therefore, we are done.
+But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{Op}}.$
+
+For a triangle labeled as in Figure 8, by r'(1, 2) we have $$s_{1}s_{2}^{-1}s_{3}s_{2}s_{1}^{-1} = s_{2}^{-1}s_{3}s_{2}.$$ Hence $$s_{1}s_{3}s_{2}s_{3}^{-1}s_{1}^{-1} = s_{3}s_{2}s_{3}^{-1}.$$ But as before, this can occur if and only if $s_{1}^{-1}, s_{2}^{-1}, s_{3}^{-1}$ satisfy the relation r'(1, 3) in W$_{\Gamma^{Op}}$.
+
+Finally, given a square labeled in figure 9 and the relations r'(1, 2) and r'(3, 4), we have 
+\begin{align*}
+& s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
+&= s_{1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
+&= s_{1}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{1}^{-1} \\
+&= s_{1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2})s_{2}^{-1}s_{1}^{-1} \\
+&= s_{1}s_{2}(s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1})s_{2}^{-1}s_{1}^{-1} \\
+&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{2}s_{2}^{-1}s_{1}^{-1}s_{2} \\
+&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}
+\end{align*}
+But this relation holds if and only if $s_{1}^{-1}, \dots, s_{4}^{-1}$ satisfy r'(2, 1) in W$_{\Gamma^{Op}}$. Therefore, we are done.
 \end{proof}

### 2014-07-04 Choosing R3 Relations.tex

--- 2014-06-29 Choosing R3 Relations.tex
@@
 \end{align*}
+
+\begin{align*}
+t_jt_k^{-1}t_it_k &= s_js_k^{-1}s_ks_is_k^{-1}s_k\\
+&= s_js_i\\
+&= s_is_j\\
+&= t_k^{-1}t_it_kt_j\\
+\end{align*}
+
 \item $$t_it_j = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = t_jt_i$$
@@
 \end{align*}
+
+We also have
+$$t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_is_j = t_k^{-1}t_it_kt_j$$
+
+\item
+\begin{align*}
+t_it_j &= s_is_ks_js_k^{-1}\\
+&= s_is_j^{-1}s_ks_j\\
+&= s_j^{-1}s_ks_js_i\\
+&= s_ks_js_k^{-1}s_i\\
+&= t_jt_i
+\end{align*}
+\end{enumerate}
+\item
+\item
+\begin{enumerate}[i)]
+\item
+\begin{align*}
+s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1} &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
+&= e
+\end{align*}
+
+\begin{align*}
+t_it_j^{-1}t_kt_jt_i^{-1}t_j^{-1}s_k^{-1}t_j &= s_ks_is_k^{-1}s_j^{-1}s_ks_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
+&= s_ks_is_js_ks_j^{-1}s_k^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
+&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
+&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_k^{-1}\\
+&= s_ks_js_ks_j^{-1}s_is_i^{-1}s_js_k^{-1}s_j^{-1}s_k\\
+&= e\\
+\end{align*}
+
+\item This follows from part (i) by symmetry
 \end{enumerate}
 \end{enumerate}
+
+Next we check the (R3) relations, following the cases from Figure 6.
 

### 2014-07-04 Paper.tex

--- 2014-07-04 Choosing R3 Relations.tex
@@
 \listoftodos
-\begin{enumerate}
-	\item Verify ~\ref{square_mutation_preserved}
-	\item Verify that the relations (a),(b) are equivalent in ~\ref{4.2_analog} and ~\ref{4.4_analog}
-	\end{enumerate}
-\newpage
-
-It's not immediately obvious which relations analogous to the original R3 relations we want to choose.
-Here we try out several possible relations, in each case trying to prove an analogous lemma to Lemma 4.1 in Barot and Marsh's paper.
-
-\section{Attempts}
-
-\subsection{}
-Here we test out the set of relations R3' where if $i_{a_0}, i_{a_1},\ldots,i_{a_{d-1}},i_{a_0}$ is a chordless cycle with all weights 1, then we add in the relation 
-$$s_0s_1^{-1}s_2s_3^{-1}\cdots s_{d-2}^{(-1)^{d-2}} s_{d-1}s_{d-2}^{(-1)^{d-1}}\cdots s_4^{-1}s_3s_2^{-1}s_1 = s_1^{-1}s_2s_3^{-1}\cdots s_{d-2}^{(-1)^{d-2}} s_{d-1}s_{d-2}^{(-1)^{d-1}}\cdots s_4^{-1}s_3s_2^{-1}s_1s_0$$
-
-We then have
-
-\begin{align*}
-& s_{d-1}s_0^{-1}s_1s_2^{-1}s_3\cdots s_{d-3}^{(-1)^{d-2}} s_{d-2}s_{d-3}^{(-1)^{d-3}}\cdots s_4s_3^{-1}s_2s_1^{-1}s_0\\
-&= s_0^{-1}s_0s_{d-1}s_0^{-1}s_1s_2^{-1}s_3\cdots s_{d-3}^{(-1)^{d-2}} s_{d-2}s_{d-3}^{(-1)^{d-3}}\cdots s_4s_3^{-1}s_2s_1^{-1}s_{d-1}s_{d-1}^{-1}s_0\\
-&= s_0^{-1}s_{d-1}^{-1}s_0s_{d-1}s_1s_2^{-1}s_3\cdots s_{d-3}^{(-1)^{d-2}} s_{d-2}s_{d-3}^{(-1)^{d-3}}\cdots s_4s_3^{-1}s_2s_1^{-1}s_{d-1}s_{d-1}^{-1}s_0\\
-\end{align*}
-
-...so I don't think this direction is going to work from here, simply because I don't see a way to flip all of the generators in the middle to their inverses.
-
-An R3 that seems promising:
-
-\begin{defn}
-Using the notation as in Barot - Marsh, given a chordless cycle C in $\Gamma$ so that all edges in C have weight 1, we define $r(a, a+1) = s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}$.
-
-An equivalent relation is as follows
-
-$s_a^{-1} s_{a+1}^{-1}\cdots s_{a-1}^{-1}s_{a-2}\cdots s_a s_{a+1}^{-1}\cdots s_{a-2}^{-1} s_{a-1}\cdots s_{a+1}$
-\end{defn}
-
-\begin{lem} (Analogue of 4.1)
-The relation r(a,a+1) for some vertex a $\in$ C implies the relation r(b, b+1) for all b $\in$ C.
-\end{lem}
-\begin{proof}
-As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
-\begin{align*}
-& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
-&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
-\end{align*}
-as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
-\end{proof}
-
-\begin{defn} (Possible relations for the weight 2 triangle) Given the cycle in Figure 8 of Barot-Marsh, we define the following relations
-\begin{enumerate}[(a)]
-\item $s_{1}s_{2}^{-1}s_{3}s_{2} = s_{2}^{-1}s_{3}s_{2}s_{1}$
-\item $s_{2}s_{3}^{-1}s_{1}s_{3} = s_{3}^{-1}s_{1}s_{3}s_{2}$
-\item $s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1} = e$
-\end{enumerate}
-\end{defn}
-
-\begin{lem} (Analogue of 4.2)
-In the above definition, if the generators satisfy the relations (R2'), then the relations (a) and (b) are equivalent, and the relations (a) and (b) imply the relation (c).
-\end{lem}
-
-\begin{proof}
-I haven't worked out the equivalence of (a) and (b) yet, so I'll leave it for someone else.
-
-In showing that (a) and (b) imply (c), I will underline the terms being manipulated in each line for emphasis.
-\begin{align*}
-& s_{1}s_{3}s_{1}(s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1})s_{1}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}\underline{s_{1}s_{1}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
-&= \underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}\underline{s_{3}^{-1}s_{1}s_{3}s_{1}}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}s_{1}s_{3}\underline{s_{1}s_{3}^{-1}s_{3}s_{1}^{-1}}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}\underline{e}s_{1}s_{3}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}s_{3}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= \underline{s_{2}s_{3}s_{2}}s_{3}^{-1}s_{1}s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}s_{2}\underline{s_{3}s_{3}^{-1}}s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}s_{2}\underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}\underline{s_{2}s_{2}^{-1}}s_{3}^{-1}s_{1}\underline{s_{3}s_{3}^{-1}}s_{1}^{-1} \\
-&= \underline{s_{3}s_{3}^{-1}}\underline{s_{1}s_{1}^{-1}} \\
-&= e
-\end{align*}
-\end{proof}
-
-\begin{lem} (Analogue of 4.6) 
-Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
-\end{lem}
-\begin{proof}
-One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$.
-To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
-But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in W$_{\Gamma^{Op}}.$ Therefore, we are done.
-\end{proof}
-
-\begin{defn} Let $\Gamma$ be a weighted diagram of finite type, and suppose $\Gamma$' = $\mu_{k}(\Gamma)$. If $s_1$, \dots, $s_n$ are the generators in W$_{\Gamma}$, define: 
-$$t_{i} =
-\begin{cases}
-s_{k}s_{i}s_{k}^{-1} & \text{if there is arrow from i to k} \\
-s_{i} & \text{otherwise}
-\end{cases}$$
-\end{defn}
-
-\begin{lem}[Generalized Lemma 5.1]\label{lem:one_connected_to_k} Let i and j be vertices of $\Gamma$.
-\begin{enumerate}[(a)]
-\item If i = k or j = k, then ($t_{i}t_{j})^{m_{ij}'/2}$ = ($t_{j}t_{i})^{m_{ij}'/2}$.
-\item If at most one of i,j is connected to k, then ($t_{i}t_{j})^{m_{ij}'/2}$ = ($t_{j}t_{i})^{m_{ij}'/2}$
-\end{enumerate}
-\end{lem}
-
-\begin{proof}
-We begin with case (a).
-Suppose that i=k.
-As in Barot-Marsh, we have that $m_{ij}$ = $m_{ij}'$, and the only nontrivial case is when there is an arrow from j to k.
-Note that $m_{ij}$ cannot be 2 in this case since there is an arrow from j to k, so suppose $m_{ij}$ = 3.
-Then we have $$s_{j}s_{k}s_{j} = s_{k}s_{j}s_{k},$$ and so $$s_{k}s_{k}s_{j}s_{k} = s_{j}s_{k}s_{j}s_{k}.$$ Multiplying both sides on the right by $s_{k}^{-1}$, we then obtain that $$s_{k}s_{k}s_{j} = s_{k}s_{j}s_{k}s_{j}s_{k}^{-1},$$ and so we find that $$t_{i}t_{j}t_{i} = s_{k}s_{k}s_{j}s_{k}^{-1}s_{k} = s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1} = t_{j}t_{i}t_{j}.$$
-
-Now suppose $m_{ij}$ = 4.
-Then $$s_{k}s_{j}s_{k}s_{j} = s_{j}s_{k}s_{j}s_{k}$$ which means that $$s_{k}s_{k}s_{j}s_{k}s_{j} = s_{k}s_{j}s_{k}s_{j}s_{k}.$$ This then gives us that $$s_{k}s_{k}s_{j}s_{k}s_{j}s_{k}^{-1} = s_{k}s_{j}s_{k}s_{j},$$ and so $$t_{i}t_{j}t_{i}t_{j} = s_{k}s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1} = s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1}s_{k} = t_{j}t_{i}t_{j}t_{i}.$$
-
-Finally, suppose $m_{ij}$ = 6.
-Then we know $$s_{k}s_{j}s_{k}s_{j}s_{k}s_{j} = s_{j}s_{k}s_{j}s_{k}s_{j}s_{k},$$ and so $$s_{k}s_{k}s_{j}s_{k}s_{j}s_{k}s_{j} = s_{k}s_{j}s_{k}s_{j}s_{k}s_{j}s_{k}.$$ Then $$s_{k}s_{k}s_{j}s_{k}s_{j}s_{k}s_{j}m_{k}^{-1} = s_{k}s_{j}s_{k}s_{j}s_{k}s_{j},$$ and so $$t_{i}t_{j}t_{i}t_{j}t_{i}t_{j} = s_{k}s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1} = s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1}s_{k}s_{k}s_{j}s_{k}^{-1}s_{k} = t_{j}t_{i}t_{j}t_{i}t_{j}t_{i}.$$ A similar argument holds when j=k.
-This concludes (a).
-
-Now considering case (b), suppose i is connected to k.
-We once again have $m_{ij}$ = $m_{ij}'$, and the only nontrivial case is when the arrow points from i to k.
-Suppose $m_{ij}$ = 2.
-Then we have $$s_{i}s_{j} = s_{j}s_{i},$$ and so we have $$s_{k}s_{i}s_{j} = s_{k}s_{j}s_{i} = s_{j}s_{k}s_{i}$$ since j is not connected to k by assumption.
-But then $$t_{i}t_{j} = s_{k}s_{i}s_{k}^{-1}s_{j} = s_{k}s_{i}s_{j}s_{k}^{-1} = s_{j}s_{k}s_{i}s_{k}^{-1} = t_{j}t_{i}.$$
-
-If $m_{ij}$ = 3, then we have $s_{j}s_{k} = s_{k}s_{j}$, and so we have $s_{k}^{-1}s_{j}s_{k} = s_{j}.$ This means that $$s_{i}s_{k}^{-1}s_{j}s_{k}s_{i} = s_{i}s_{j}s_{i} = s_{j}s_{i}s_{j},$$ and we then have that $$t_{i}t_{j}t_{i} = s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1} = s_{k}s_{j}s_{i}s_{j}s_{k}^{-1} = s_{j}s_{k}s_{i}s_{k}^{-1}s_{j} = t_{j}t_{i}t_{j}.$$
-
-If $m_{ij}$ = 4, we have $s_{i}s_{j}s_{i}s_{j} = s_{j}s_{i}s_{j}s_{i}$.
-Then $$s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{j} = s_{i}s_{k}^{-1}s_{k}s_{j}s_{i}s_{j} = s_{j}s_{i}s_{k}^{-1}s_{k}s_{j}s_{i} = s_{j}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}.$$ But then conjugating the right and left sides by $s_{k}$, we find that $$s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{j}s_{k}^{-1} = s_{k}s_{j}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1},$$ and thus by the commutativity of $s_{j}$ and $s_{k}$, we have $$t_{i}t_{j}t_{i}t_{j} = s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1}s_{j} = s_{j}s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1} = t_{j}t_{i}t_{j}t_{i}.$$
-
-Finally, if $m_{ij}$ = 6, we have $s_{i}s_{j}s_{i}s_{j}s_{i}s_{j} = s_{j}s_{i}s_{j}s_{i}s_{j}s_{i}$.
-Thus conjugating by $s_{k}$ and using the commutativity of  $s_{k}$ and s$_{j}$, we find that $$s_{k}s_{i}s_{j}s_{i}s_{j}s_{i}s_{k}^{-1}s_{j} = s_{j}s_{k}s_{i}s_{j}s_{i}s_{j}s_{i}s_{k}^{-1}.$$ But this occurs if and only if $$t_{i}t_{j}t_{i}t_{j}t_{i}t_{j} = s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1}s_{j} = s_{j}s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1}s_{j}s_{k}s_{i}s_{k}^{-1} = t_{j}t_{i}t_{j}t_{i}t_{j}t_{i}.$$
-
-A similar argument holds when j is connected to k, so we are done.
-\end{proof}
 
@@
 After Lemma \ref{lem:one_connected_to_k} we have left to check the relations $(R2)$ when both $i$ and $j$ are connected to $k$ and the relations $(R3)$.
-
 Beginning with the relations $(R2)$, and following cases a-f from Corollary 2.3 in Barot and Marsh:
@@
 \item
+\begin{enumerate}[i)]
+\item
+\begin{align*}
+t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}\\
+&= s_i^{-1}s_ks_is_js_i^{-1}s_ks_is_js_i^{-1}s_k^{-1}s_is_j^{-1}s_i^{-1}s_k^{-1}s_is_j^{-1}\\
+&= s_i^{-1}s_ks_js_ks_js_k^{-1}s_j^{-1}s_k^{-1}s_j^{-1}s_i\\
+&= e
+\end{align*}
+We also have
+$$ t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_it_j$$
+
+\item
+\begin{align*}
+s_k^{-1}t_it_jt_i^{-1}t_j^{-1}s_k &= s_k^{-1}s_is_ks_js_k^{-1}s_i^{-1}s_ks_j^{-1}\\
+&= s_is_ks_i^{-1}s_js_is_k^{-1}s_i^{-1}s_j^{-1}\\
+&= e
+\end{align*}
+
+\end{enumerate}
 \item
@@
 
-Next we check the (R3) relations, following the cases from Figure 6.
-
-\section{Relations for 2,2,1 triangle, talk to Aaron if you think there's an error}
-
-\begin{rem}
-\label{even_more_relations}
-I am proposing to add the following relations whever we have the situation
-
-$\xymatrix{a \ar[r]^2 & b \ar[r]^1 & c},$ or $\xymatrix{a \ar[r]^1 & b \ar[r]^2 & c}:$
-
-Include $s_is_{i+1}^2 = s_{i+1}^2s_i,$ and $s_is_{i-1}^2 = s_{i-1}^2s_i,$ for all $i = 1,2,3.$ I believe these mutate correctly, as in cases b,c,d in Barot-Marsh.
-Note that in the above diagrams, it is fine if we have a 2 edges from a to c or c to a.
-\end{rem}
-
-\begin{lem} 
-\label{4.2_analog}
-(4.2 Analog)
-Assuming the additional relation $\tw\tr\tr = \tr\tr\tw$ from ~\ref{even_more_relations}, the two relations $s_{1}^{-1}s_2^{-1}s_3^{-1}s_2s_1s_2^{-1}s_3s_2 = e$ and $\twi\tri\oni\tr\tw\tri\on\tr =e$ are equivalent and they imply $\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on=e.
-$
-\end{lem}
-\begin{proof}
-
-We only have to show the first two imply the third. We can use the first two identities to deduce $\tw\tri = \tri\on\tr\tw\tri\oni,\twi\tri=\tri\oni\tr\twi\tri\on.$ Indeed, we can see
-
-\begin{align*}
-	e &= \tw\tr\tw\tri\twi\tri
-	\\
-	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\tri\oni\tr\twi\tri\on)
-	\\
-	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\tri\oni\tr\twi\on\oni\tri\on)
-	\\
-	&= \tw\tr(\tri\on\tr\tw\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
-	\\
-	&= \tw\tr(\tri\on\tr\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
-	\\
-	&= \tw\tr(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
-\end{align*}
-
-Next,I claim $\tw\tr = \oni\tr\on\tr\on\tw\tri\oni.$ This should be easy to verify by manipulating the equation $\twi\tri\oni\tr\tw\tri\on\tr =e,$ if we can use the relation $\tw\tr\tr = \tr\tr\tw.$
-To verify this, note:
-\begin{align*}
-	e &= \twi\tri\oni\tr\tw\tri\on\tr \iff \\
-	e &= \twi\tri\oni\tri\tw\tr\on\tr \iff \\
-	e &= \tri\oni\tri\twi\tr\on\tr\tw \iff \\
-	e &= \tri\twi\tr\on\tr\tw\tri\oni \iff \\
-	\tw\tr &= \tr\on\tr\on\tw\tri\oni \iff \\
-	 \tw\tr &= \oni\tr\on\tr\on\on\tw\tri\oni \iff \\
-\end{align*} 
-Where an equivalent form of $\tw\tr\tr = \tr\tr\tw.$ is used in going from the first line to the second in the above computation.
-
- Plugging this in yields
-\begin{align*}
-	e &= (\oni\tr\on\tr\on\tw\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
-	\\
-	&= (\oni\tr\on\tr\on\tw\on\oni\tri\oni)(\on\tr\on\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
-	\\
-	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni\on\tri\oni)(\on\tr\oni\tri\oni\twi\on\oni\tri\on)
-	\\
-	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
-	\\
-	&= (\oni\tr\on\tr\on\tw\on)(\tri\oni\tw\oni)(\tri\oni\twi\on\oni\tri\on)
-\end{align*}
-
-So, since $e = \oni\tr\on\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on\oni\tri\on,$ cancelling three terms from both sides, we get $e =\tr\on\tw\on\tri\oni\tw\oni\tri\oni\twi\on,$ as claimed.
-\end{proof}
-
-\begin{prop}
-\label{commuting_triples}
-For the case of the (2,1,2,1) square, we have $\twi\tri\tw\fri\oni\fr = \fri\oni\fr\twi\tri\tw.$
-By inverting both sides of this relation, we also obtain
-$\fri\on\fr\twi\tr\tw = \tri\tr\tw\fri\on\fr.$
-\end{prop}
-\begin{proof}
-Using the cyclic $r(1,2)$ relation we have
-\begin{align*}
-	e &= \oni\twi\tri\fri\tr\tw\on\twi\tri\fr\tr\tw\\
-	&= \oni\twi\fr\tri\fri\tw\on\twi\fr\tr\fri\tw \\
-	&= \oni\fr\twi\tri\tw\fri\on\fr\twi\tr\tw\fri \iff \\
-	e &= \fri\oni\fr\twi\tri\tw\fri\on\fr\twi\tr\tw \iff \\
-	\twi\tri\tw\fri\oni\fr &= \fri\oni\fr\twi\tri\tw
-\end{align*}
-\end{proof}
-
-\begin{lem}
-\label{4.4_analog} (Analog of 4.4) For the case of the (2,1,2,1) square, assuming the relations from ~\ref{even_more_relations} we get that the analogs of $r(1,2)^2 = e,r(3,4)^2 = e$ are equivalent, and they imply the following relation, which is an analog of R3b:
-
-$$\twi\tr\fri\on\fr\tr\tw\tri\fri\on\fr\tri\twi\tri\fri\oni\fr\tr=e.$$
-\end{lem}
-\begin{proof}
-Hailee said she showed that the analogs of $r(1,2),r(3,4)$ are equivalent.
-
-So, I will only show that these relations imply the analog of $R3b.$
-
-\begin{align*}
-	e &=\twi\tr\fri\on\fr\tr\tw\tri\fri\on\fr\tri\twi\tri\fri\oni\fr\tr \iff
-	\\
-	e &= (\twi\tr\fri\on\fr\tr)(\tw\tri\fri\on\fr\tri)(\twi\tri\fri\oni\fr\tr) \iff
-	\\
-	e &= \tr(\twi\tr\fri\on\fr\tr)\tri\tr(\tw\tri\fri\on\fr\tri)\tri\tr(\twi\tri\fri\oni\fr\tr)\tri
-	\\
-	&= (\tr\twi\tr\fri\on\fr)(\tr\tw\tri\fri\on\fr)(\tr\twi\tri\fri\oni\fr)
-\end{align*}
-
-Now observe that $$\twi\tr\tw\tri\twi = \tr\tw\twi\twi = \tr\twi\tr,$$ by ~\ref{even_more_relations} in the second equality.
-Also, $$\tw\tri\twi\tr\tw = \twi\tri\tw\tr\tw = \tr\tw\tri$$ again using ~\ref{even_more_relations} in the first equality.
-And finally,
-$$\twi\tri\twi\tri\tw = \tri\twi\tri.$$
-So, substituting these three equations in the above, we have 
-\begin{align*}
-	e &= \tr(\twi\tr\fri\on\fr\tr)\tri\tr(\tw\tri\fri\on\fr\tri)\tri\tr(\twi\tri\fri\oni\fr\tr)\tri
-	\\
-	&= ((\tr\twi\tr)\fri\on\fr)((\tr\tw\tri)\fri\on\fr)((\tr\twi\tri)\fri\oni\fr)
-	\\
-	&=((\twi\tr\tw\tr\twi)\fri\on\fr)((\tw\tri\twi\tr\tw)\fri\on\fr)((\twi\tri\twi\tr\tw)\fri\oni\fr)
-\end{align*}
-Now, using ~\ref{commuting_triples} three times, we have
-
-\begin{align*}
-	&((\twi\tr\tw\tr\twi)\fri\on\fr)((\tw\tri\twi\tr\tw)\fri\on\fr)((\twi\tri\twi\tr\tw)\fri\oni\fr)\\
-	&= (\twi\tr(\fri\on\fr\tw\tr\twi))(\twi\tr(\fri\on\fr\twi\tr\tw))(\twi\tri(\fri\oni\fr\twi\tri\tw))
-	&=
-	(\twi\tr\fri\on\tw\fr\tr\twi)(\twi\tr\fri\on\twi\fr\tr\tw)(\twi\tri\fri\oni\twi\fr\tri\tw)
-	\\
-	&= \twi\tr\fri \on\tw\on\twi\oni\twi\fr\tri\tw
-\end{align*}
-
-Therefore,
-
-\begin{align*}
-	e &= \twi\tr\fri \on\tw\on\twi\oni\twi\fr\tri\tw \iff \\
-	e &=  \on\tw\on\twi\oni\twi
-\end{align*}
-Which if of course one of our basic R2 relations.
-\end{proof}
-
-\begin{thm}\todo{verify this}
-\label{square_mutation_preserved}
-The relations described in ~\ref{even_more_relations} are permuted (and hence preserved) after mutation at any vertex.
-\end{thm}
-\begin{proof}
-This is what additionally needs to be checked in ~\ref{5.2 analog} by adding ~\ref{even_more_relations} in the cases corresponding to cycles with edges of weight 2 in the paper.
-I.e.
-it has to be checked in cases (b,c,d,e,f,g,h).
-It seems like a lot of casework, but there's a fair amount of symmetry to make it a bit easier, and I checked this in a few cases, and it seemed to work out.
-\end{proof}
-
-\end{document}
+'\end{document}

### 2014-07-04 Choosing R3 Relations.tex

--- 2014-07-03 Choosing R3 Relations.tex
@@
 \end{align*}
+
+We also have
+$$t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_is_j = t_k^{-1}t_it_kt_j$$
+
+\item
+\begin{align*}
+t_it_j &= s_is_ks_js_k^{-1}\\
+&= s_is_j^{-1}s_ks_j\\
+&= s_j^{-1}s_ks_js_i\\
+&= s_ks_js_k^{-1}s_i\\
+&= t_jt_i
+\end{align*}
+\end{enumerate}
+\item
+\item
+\begin{enumerate}[i)]
+\item
+\begin{align*}
+s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1} &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
+&= e
+\end{align*}
+
+\begin{align*}
+t_it_j^{-1}t_kt_jt_i^{-1}t_j^{-1}s_k^{-1}t_j &= s_ks_is_k^{-1}s_j^{-1}s_ks_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
+&= s_ks_is_js_ks_j^{-1}s_k^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
+&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
+&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_k^{-1}\\
+&= s_ks_js_ks_j^{-1}s_is_i^{-1}s_js_k^{-1}s_j^{-1}s_k\\
+&= e\\
+\end{align*}
+
+\item This follows from part (i) by symmetry
 \end{enumerate}

### 2014-07-14 Choosing R3 Relations.tex
first draft of sections 2 and 3

--- 2014-07-03 Choosing R3 Relations.tex
@@
 
-\section{Diagrams}
+\section{Diagrams of Finite Type}
+
+In this section, we shall review the structure of diagrams of finite type, and how their cycles are effected by mutation. This section is simply a recap of \cite[Section 2]{barot}
+
+\begin{defn}
+A {\it chordless cycle} of an unoriented graph $G$ is a connected subgraph $H \subset G$ such that the number of vertices in $H$ is equal to the number of edges in $H,$ and the edges in $H$ form a single cycle.
+\end{defn}
+
+\begin{prop}
+Let $\Gamma$ be a diagram of finite type.
+Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$.
+Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a triangle with two edges of weight 2 and one of weight 1, or a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below.
+
+\begin{tikzpicture}[baseline=-0.5ex]
+ \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & &|[name = ul]|\circ& |[name = ur]|\circ&\\
+    %
+    &|[name=lu]| \circ &&&|[name=ru]| \circ \\
+     & |[name = ld]|\circ&&& |[name = rd]|\circ\\
+    %
+    &&|[name=dl]| \circ &|[name=dr]| \circ &\\
+  };
+\draw
+  (ul) -- node[above] {1} (ur)
+  ;
+  \draw
+  (ul) -- node[left]{1}(lu)
+  ;
+  \draw
+  (dr) -- node[right]{1}(rd)
+  ;
+  \draw
+  (lu) -- node[left]{1}(ld)
+  ;
+  \draw
+  (ru) -- node[right]{1}(rd)
+  ;
+  \draw
+  (ur) -- node[right]{1}(ru)
+  ;
+  \draw
+  (dl) -- node[left]{1}(ld)
+  ;
+  \draw[dotted]
+  (dl) -- (dr)
+  ; 
+ \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\circ& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw
+  (ul) -- node[above] {1} (ur)
+  ;
+  \draw
+  (dl) -- node[left]{2}(ul)
+  ;
+  \draw
+  (dr) -- node[below]{1}(dl)
+  ;
+  \draw
+  (ur) -- node[right]{2} (dr)
+  ; 
+   \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (10,0)
+  {
+    && |[name = u]|\circ& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw
+  (u) -- node[right] {2} (dr)
+  ;
+  \draw
+  (dl) -- node[left]{2}(u)
+  ;
+  \draw
+  (dr) -- node[below]{1}(dl)
+  ;
+
+   \end{tikzpicture}
+
+\end{prop}
+\begin{proof}
+See \cite[Proposition 2.1]{barot}.
+\end{proof}
+
+\begin{lem}
+Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
+Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.
+Every chordless cycle in $\Gamma'$ is of one of these types.
+
+\begin{enumerate}[(a)]
+\item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {1} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{1}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+   \end{tikzpicture}
+   \item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {1} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+   \end{tikzpicture}
+   \item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {2} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {2} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{1}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+   \end{tikzpicture}
+	\item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {2} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(dr)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {2} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+   \end{tikzpicture}
+	\item 
+\begin{tikzpicture}[baseline=-0.5ex]
+\matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+\draw[->]
+  (dl) to node[above]{2} (ur)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \end{tikzpicture}
+
+\item \begin{tikzpicture}[baseline=-0.5ex]
+\matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = ur]|\bullet\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dr) to node[right]{2} (ur)
+  ;
+\draw[->]
+  (ul) to node[above]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\circ& |[name = ur]|\bullet\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \end{tikzpicture}
+
+   \item  
+   \begin{tikzpicture}[baseline=-0.5ex]
+
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+\draw[->]
+  (dl) to node[above]{2} (ur)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \end{tikzpicture}
+
+   \item  
+   \begin{tikzpicture}[baseline=-0.5ex]
+
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = ur]|\bullet\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\circ & |[name = ur]|\bullet\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dr) to node[right]{2} (ur)
+  ;
+\draw[->]
+  (ul) to node[above]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \end{tikzpicture}
+
+   \item
+   \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ml) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(ml)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ml)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ml) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[right]{1}(ul)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \end{tikzpicture}
+
+   \item
+   \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ml) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(ml)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ml)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ml) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[right]{1}(ul)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \end{tikzpicture}
+
+    \item $C$ is an oriented cycle in $\Gamma$ not connected to $k$ and $C'$ is the corresponding cycle in $\Gamma'.$
+
+    \item $C$ is an oriented cycle in $\Gamma$ with exactly one vertex in $C$ connected to $k$ by an edge of either weight 1 or 2. Then, $C'$ is the corresponding cycle in $\Gamma'.$  
+\end{enumerate}
+
+\end{lem}
+\begin{proof}
+See \cite[Lemma 2.5]{barot}.
+\end{proof}
+
+\section{The Group of a Diagram in an Artin Group}
+
+\begin{defn}
+For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
+The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the relations
+\begin{itemize}
+	\item[(R2')] For all $i \neq j,$ we add the relations
+	\\
+$	\begin{cases}
+	s_is_j=s_js_i, &\text{ if there is no edge between $i$ and $j$}\\
+	s_is_js_i = s_js_is_j &\text{ if there is an edge of weight 1 between $i$ and $j.$}\\
+	s_is_js_is_j = s_js_is_js_i &\text{ if there is an edge of weight 2 between $i$ and $j$.}\\
+	s_is_js_is_js_is_j = s_js_is_js_is_js_i &\text{ if there is an edge of weight 3 between $i$ and $j$.}
+\end{cases}$
+\item[(R3')(a)] For every chordless cycle of the form
+
+\begin{tikzcd}
+i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
+\end{tikzcd}
+
+such that all edges have weight 1, for all $i,$ with $0 \leq a \leq d-1,$ we include the relation 
+\begin{align*}
+	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}.
+\end{align*}
+Where subscripts are taken $\pmod d.$
+
+\item[(R3')(a)] For every chordless cycle of the form \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){i};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){k};
+   \end{tikzpicture}
+   we include the three relations
+   \begin{enumerate}[(1)]
+\item $s_{i}s_{j}^{-1}s_{k}s_{j} = s_{j}^{-1}s_{k}s_{j}s_{i}$
+\item $s_{j}s_{k}^{-1}s_{i}s_{k} = s_{k}^{-1}s_{i}s_{k}s_{j}$
+\item $s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i} = e.$
+\end{enumerate}
+\end{itemize}
+\end{defn}
+
+\begin{rem}
+Note that if $\Gamma$ is the graph associated to a dynikin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that dynkin diagram.
+This is the case since in this case we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin Group.
+\end{rem}
+
+\section{Additional Pictures}
 picure e
@@
     \end{tikzpicture}
+
+ \begin{thebibliography}{70}
+
+\bibitem{barot}
+Barot and Marsh -- CITE THIS CORRECTLY LATER
+
+\end{thebibliography}
 \end{document}

### 2014-07-15 Choosing R3 Relations.tex
additional pdf update

@@
 
-In this section, we shall review the structure of diagrams of finite type, and how their cycles are effected by mutation. This section is simply a recap of \cite[Section 2]{barot}
+In this section, we shall review the structure of diagrams of finite type, and how their cycles are effected by mutation. This section is simply a recap of \cite[Section 2]{barot}.
 
@@
 \section{Additional Pictures}
-picure e
 \begin{tikzpicture}[baseline=-0.5ex]

### 2014-07-15 Paper.tex
moved Sections 3 and 4 to Paper.tex and added bibliography to Paper.tex

@@
 \usepackage{enumerate}
+\usepackage{natbib}
+
+\usepackage{tikz}
+\usepackage{tikz-cd}
+\usetikzlibrary{matrix, calc, arrows}
+\usepackage{latexsym,amscd,epsfig,verbatim}
+\usepackage[margin=1in,letterpaper,portrait]{geometry}
 
@@
 
-\usepackage[all]{xy}
+%\usepackage[all]{xy}
 \theoremstyle{definition}
@@
 
-\usepackage{amsmath}
 \begin{document}
@@
 \listoftodos
+
+\section{Diagrams of Finite Type}
+
+In this section, we shall review the structure of diagrams of finite type, and how their cycles are effected by mutation. This section is simply a recap of \cite[Section 2]{BM13}.
+
+\begin{defn}
+A {\it chordless cycle} of an unoriented graph $G$ is a connected subgraph $H \subset G$ such that the number of vertices in $H$ is equal to the number of edges in $H,$ and the edges in $H$ form a single cycle.
+\end{defn}
+
+\begin{prop}
+Let $\Gamma$ be a diagram of finite type.
+Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$.
+Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a triangle with two edges of weight 2 and one of weight 1, or a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below.
+
+\begin{tikzpicture}[baseline=-0.5ex]
+ \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & &|[name = ul]|\circ& |[name = ur]|\circ&\\
+    %
+    &|[name=lu]| \circ &&&|[name=ru]| \circ \\
+     & |[name = ld]|\circ&&& |[name = rd]|\circ\\
+    %
+    &&|[name=dl]| \circ &|[name=dr]| \circ &\\
+  };
+\draw
+  (ul) -- node[above] {1} (ur)
+  ;
+  \draw
+  (ul) -- node[left]{1}(lu)
+  ;
+  \draw
+  (dr) -- node[right]{1}(rd)
+  ;
+  \draw
+  (lu) -- node[left]{1}(ld)
+  ;
+  \draw
+  (ru) -- node[right]{1}(rd)
+  ;
+  \draw
+  (ur) -- node[right]{1}(ru)
+  ;
+  \draw
+  (dl) -- node[left]{1}(ld)
+  ;
+  \draw[dotted]
+  (dl) -- (dr)
+  ; 
+ \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\circ& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw
+  (ul) -- node[above] {1} (ur)
+  ;
+  \draw
+  (dl) -- node[left]{2}(ul)
+  ;
+  \draw
+  (dr) -- node[below]{1}(dl)
+  ;
+  \draw
+  (ur) -- node[right]{2} (dr)
+  ; 
+   \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (10,0)
+  {
+    && |[name = u]|\circ& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw
+  (u) -- node[right] {2} (dr)
+  ;
+  \draw
+  (dl) -- node[left]{2}(u)
+  ;
+  \draw
+  (dr) -- node[below]{1}(dl)
+  ;
+
+   \end{tikzpicture}
+
+\end{prop}
+\begin{proof}
+See \cite[Proposition 2.1]{BM13}.
+\end{proof}
+
+\begin{lem}
+Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
+Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.
+Every chordless cycle in $\Gamma'$ is of one of these types.
+
+\begin{enumerate}[(a)]
+\item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {1} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{1}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+   \end{tikzpicture}
+   \item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {1} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+   \end{tikzpicture}
+   \item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {2} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {2} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{1}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+   \end{tikzpicture}
+	\item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {2} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(dr)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {2} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+   \end{tikzpicture}
+	\item 
+\begin{tikzpicture}[baseline=-0.5ex]
+\matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+\draw[->]
+  (dl) to node[above]{2} (ur)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \end{tikzpicture}
+
+\item \begin{tikzpicture}[baseline=-0.5ex]
+\matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = ur]|\bullet\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dr) to node[right]{2} (ur)
+  ;
+\draw[->]
+  (ul) to node[above]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\circ& |[name = ur]|\bullet\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \end{tikzpicture}
+
+   \item  
+   \begin{tikzpicture}[baseline=-0.5ex]
+
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\bullet& |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+\draw[->]
+  (dl) to node[above]{2} (ur)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k=1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \end{tikzpicture}
+
+   \item  
+   \begin{tikzpicture}[baseline=-0.5ex]
+
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = ur]|\bullet\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+
+   \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\circ & |[name = ur]|\bullet\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ur) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dr) to node[right]{2} (ur)
+  ;
+\draw[->]
+  (ul) to node[above]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+    \end{tikzpicture}
+
+   \item
+   \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ml) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(ml)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ml)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ml) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[right]{1}(ul)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \end{tikzpicture}
+
+   \item
+   \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ml) to node[above] {1} (ul)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(ml)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & |[name = ul]|\circ& |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& &&& |[name = mr]|\vdots \\
+    %
+    & |[name = dl]|\circ& |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ml)
+  ;
+  \draw[->]
+  (ul) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ml) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[right]{1}(ul)
+  ;
+    \node at (ml.west){$k$};
+    \node at (ul.north){1};
+    \node at (um.north){2};
+    \node at (dm.south){$h-1$};
+    \node at (dl.south){$h$};
+    \end{tikzpicture}
+
+    \item $C$ is an oriented cycle in $\Gamma$ not connected to $k$ and $C'$ is the corresponding cycle in $\Gamma'.$
+
+    \item $C$ is an oriented cycle in $\Gamma$ with exactly one vertex in $C$ connected to $k$ by an edge of either weight 1 or 2. Then, $C'$ is the corresponding cycle in $\Gamma'.$  
+\end{enumerate}
+
+\end{lem}
+\begin{proof}
+See \cite[Lemma 2.5]{BM13}.
+\end{proof}
+
+\section{The Group of a Diagram in an Artin Group}
+
+\begin{defn}
+For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
+The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the relations
+\begin{itemize}
+	\item[(R2')] For all $i \neq j,$ we add the relations
+	\\
+$	\begin{cases}
+	s_is_j=s_js_i, &\text{ if there is no edge between $i$ and $j$}\\
+	s_is_js_i = s_js_is_j &\text{ if there is an edge of weight 1 between $i$ and $j.$}\\
+	s_is_js_is_j = s_js_is_js_i &\text{ if there is an edge of weight 2 between $i$ and $j$.}\\
+	s_is_js_is_js_is_j = s_js_is_js_is_js_i &\text{ if there is an edge of weight 3 between $i$ and $j$.}
+\end{cases}$
+\item[(R3')(a)] For every chordless cycle of the form
+
+\begin{tikzcd}
+i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
+\end{tikzcd}
+
+such that all edges have weight 1, for all $i,$ with $0 \leq a \leq d-1,$ we include the relation 
+\begin{align*}
+	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}.
+\end{align*}
+Where subscripts are taken $\pmod d.$
+
+\item[(R3')(a)] For every chordless cycle of the form \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){i};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){k};
+   \end{tikzpicture}
+   we include the three relations
+   \begin{enumerate}[(1)]
+\item $s_{i}s_{j}^{-1}s_{k}s_{j} = s_{j}^{-1}s_{k}s_{j}s_{i}$
+\item $s_{j}s_{k}^{-1}s_{i}s_{k} = s_{k}^{-1}s_{i}s_{k}s_{j}$
+\item $s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i} = e.$
+\end{enumerate}
+\end{itemize}
+\end{defn}
+
+\begin{rem}
+Note that if $\Gamma$ is the graph associated to a dynikin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that dynkin diagram.
+This is the case since in this case we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin Group.
+\end{rem}
 
@@
 
-'\end{document}
+\bibliography{References}
+\bibliographystyle{alpha}
+
+\end{document}

### 2014-07-15 Paper.tex
Added Section 4

@@
 
-\begin{defn}
+\begin{defn} \label{grp def}
 For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
@@
 \end{rem}
+
+\section{Symmetry among (R3') Relations}
+
+As in \cite{Barot}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,
+
+\begin{lem}
+Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
+\begin{tikzcd}
+i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
+\end{tikzcd}
+so that all edges have weight 1.
+Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and r(i_{a}, i_{a+1}) for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
+\end{lem}
+
+\begin{proof}
+As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
+\begin{align*}
+& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
+&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
+&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
+\end{align*}
+as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
+\end{proof}
+
+Furthermore, we obtain similar results for cycles containing edges of weight 2.
+
+\begin{lem} 
+Let $\Gamma$ be a diagram of finite type containing a 3-cycle as in (R3')(b) of ~\ref{grp def}.
+Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$.
+Then the relations (1) and (2) of (R3')(b) are equivalent, and they together imply the relation (3).
+\end{lem}
+
+\begin{proof}
+The equivalence of (1) and (2) follows from the fact that
+\begin{align*}
+& s_{1}^{-1}s_{3}s_{2}s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1}s_{3}s_{3}^{-1}s_{1} \\
+&= s_{1}^{-1}s_{3}s_{2}s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}s_{3}^{-1} \\
+&= s_{1}^{-1}s_{2}^{-1}s_{3}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{2}
+\end{align*}
+
+In showing that (1) and (2) imply (3), we will underline the terms being manipulated in each line for emphasis.
+\begin{align*}
+& s_{1}s_{3}s_{1}(s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1})s_{1}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}\underline{s_{1}s_{1}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
+&= \underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{2}\underline{s_{3}^{-1}s_{1}s_{3}s_{1}}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{2}s_{1}s_{3}\underline{s_{1}s_{3}^{-1}s_{3}s_{1}^{-1}}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{2}\underline{e}s_{1}s_{3}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{2}s_{3}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= \underline{s_{2}s_{3}s_{2}}s_{3}^{-1}s_{1}s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{3}s_{2}\underline{s_{3}s_{3}^{-1}}s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{3}s_{2}\underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
+&= s_{3}\underline{s_{2}s_{2}^{-1}}s_{3}^{-1}s_{1}\underline{s_{3}s_{3}^{-1}}s_{1}^{-1} \\
+&= \underline{s_{3}s_{3}^{-1}}\underline{s_{1}s_{1}^{-1}} \\
+&= e
+\end{align*}
+\end{proof}
+
+\begin{lem} 
+Let $\Gamma$ be a diagram of finite type containing a 4-cycle as in (R3')(c) of ~\ref{grp def}.
+Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$.
+Then the relations (1) and (2) of (R3')(c) are equivalent.
+\end{lem}
+
+\begin{proof}
+We have that
+\begin{align*}
+& s_{3}^{-1}s_{4}^{-1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{4}^{-1}s_{3}s_{2})s_{2}^{-1}s_{4}s_{3} \\
+&= s_{3}^{-1}s_{4}^{-1}(s_{2}s_{1}s_{2}^{-1})(s_{3}^{-1}s_{4}s_{3})(s_{2}s_{1}^{-1}s_{2}^{-1})s_{3}^{-1}s_{4}^{-1}s_{3}s_{4}s_{3} \\
+&= s_{3}^{-1}s_{4}^{-1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1}s_{3}^{-1}(s_{4}^{-1}s_{3}s_{4})s_{3} \\
+&= s_{3}^{-1}s_{4}^{-1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1}s_{4}
+\end{align*}
+\end{proof}
+
+Finally, we conclude the section by establishing a relationship between the groups defined by $\Gamma$ and $\Gamma^{op}$.
+
+\begin{lem} (Analogue of 4.6) 
+Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
+\end{lem}
+\begin{proof}
+One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$.
+To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
+But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$
+
+For a triangle as in (R3')(b) of ~\ref{grp def}, by the relation r'(1, 2) we have $$s_{1}s_{2}^{-1}s_{3}s_{2}s_{1}^{-1} = s_{2}^{-1}s_{3}s_{2}.$$ Hence $$s_{1}s_{3}s_{2}s_{3}^{-1}s_{1}^{-1} = s_{3}s_{2}s_{3}^{-1}.$$ But as before, this can occur if and only if $s_{1}^{-1}, s_{2}^{-1}, s_{3}^{-1}$ satisfy the relation r'(1, 3) in W$_{\Gamma^{op}}$.
+
+Finally, given a square labeled as in (R3')(c) and the relations r'(1, 2) and r'(3, 4), we have 
+\begin{align*}
+& s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
+&= s_{1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
+&= s_{1}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{1}^{-1} \\
+&= s_{1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2})s_{2}^{-1}s_{1}^{-1} \\
+&= s_{1}s_{2}(s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1})s_{2}^{-1}s_{1}^{-1} \\
+&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{2}s_{2}^{-1}s_{1}^{-1}s_{2} \\
+&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}
+\end{align*}
+But this relation holds if and only if $s_{1}^{-1}, \dots, s_{4}^{-1}$ satisfy r'(2, 1) in W$_{\Gamma^{Op}}$. Therefore, we are done.
+\end{proof}
+
+\section{Main Results}
 

### 2014-07-16 Paper.tex
added r3c relations

@@
 
-\item[(R3')(a)] For every chordless cycle of the form \begin{tikzpicture}[baseline=-0.5ex]
+\item[(R3')(b)] For every chordless cycle of the form \begin{tikzpicture}[baseline=-0.5ex]
     \matrix[matrix of math nodes,column sep={25pt,between origins},row
@@
   {
-    && |[name = u]|\bullet& \\
+    && |[name = u]|\circ& \\
     %
@@
 \end{enumerate}
+\item[(R3')(c)] For every chordless cycle of the form
+\begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\circ & |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){i};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){j};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){k};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){l};
+
+   \end{tikzpicture}
+
+   we include the two relations
+   \begin{enumerate}[(1)]
+\item $s_{i}s_{j}^{-1}s_{k}^{-1}s_ls_{k}s_j = s_{j}^{-1}s_{k}^{-1}s_ls_ks_{j}s_{i}$
+\item $s_{k}s_{l}^{-1}s_{i}^{-1}s_js_{i}s_l = s_{l}^{-1}s_{i}^{-1}s_js_is_{l}s_{k}$
+\end{enumerate}
 \end{itemize}
@@
 so that all edges have weight 1.
-Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and r(i_{a}, i_{a+1}) for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
+Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
 \end{lem}

### 2014-07-16 Paper.tex
Added background and definitions

@@
 \newcommand\on{s_1}
+\newcommand{\V}{$V(\Gamma)$}
 
@@
 \begin{document}
-
 %This adds the list of todos to the first page.
 \listoftodos
+
+\title{Artin Group Presentations of Reflection Groups}
+\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
+\address{you can put addresses for authors\\
+here \\
+}
+\email{..., hpeck@millikin.edu}
+\date{\today}
+\keywords{Artin group, cluster algebra, diagram representations}
+
+\begin{abstract}
+In 2003, Fomin and Zelevinsky proved that finite-type cluster algebras can be classified by Dynkin diagrams.
+Then in 2013, Barot and Marsh defined the presentation of a reflection group associated to a Dynkin diagram in terms of an edge-weighted, oriented graph, and proved that this group is invariant (up to isomorphism) under diagram mutations.
+In this paper, we extend Barot and Marsh's results to Artin group presentations, defining new relations for when the generators are not self-inverses, and again showing mutation-invariance for these presentations.
+\end{abstract}
+
+\maketitle
+
+\section{Introduction \& Motivation}
+
+In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras.
+This introductory paper focused on structural features of cluster algebras, specifically that, in a given cluster, when any cluster variable is viewed as a rational function in the variables of the given cluster, this cluster variable is a Laurent polynomial.
+Fomin and Zelevinsky initially defined this type of commutative ring in order to make further strides in the areas of representation theory, Lie theory, and total positivity.
+Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations.
+Of particular interest were \textit{finite-type} cluster algebras; that is, cluster algebras whose variables are generated through mutation on a finite number of \textit{seeds}.
+In the 2003 sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3.
+In particular, this proves that finite-type cluster algebras can be classified by Dynkin diagrams.
+\\
+\indent Barot and Marsh extended Fomin and Zelevinsky's results in \cite{BM13}, providing a presentation of the reflection group associated to a Dynkin diagram with generators that correspond to elements of a companion basis associated to a seed of a finite-type cluster algebra.
+They also proved that this group presentation is invariant up to isomorphism under the mutation equivalence relation.
+That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
+\\
+\indent Section 2 provides the necessary definitions and fundamental results from \cite{BM13} to provide motivation for our own results.
+For further definitions and references on the topic, we refer the reader to \cite{FZ02}.
+Section 3  will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles.
+In this section we also define the appropriate relations for our Artin group presentations.
+Section 4 specifies a relation for each case of the chordless cycles which suffices to show all the other relations in the group presentation hold.
+Finally, section 5 will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
+\\
+
+\section{Definitions and Notation}
+
+We begin by introducing some preliminary notations and definitions which will aid the reader in understanding the results in the following sections.
+For further references on cluster algebras, we refer the reader to \cite{FZ02} and \cite{FZ03} and for a more detailed description of Artin group presentations, we direct attention to \cite{FN61}.
+We also provide references to several lemmas and propositions from \cite{BM13} which were helpful in formulating our own results.
+\\
+
+A \textit{cluster algebra} is a commutative ring with unity but without zero-divisors, and it can be generated by a set of generators called \textit{cluster variables} that satisfy certain exchange relations.
+Following the style of \cite{FZ02} and \cite{BM13}, we will define cluster algebras in terms of \textit{skew-symmetrisable} matrices (that is, a matrix $B$ such that there exists a diagonal matrix $D$ of the same size with $D_{ii} >0$ such that $DB$ is skew-symmetric).
+Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$.
+We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \left{x_1, \ldots, x_n\right}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix.
+Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
+\begin{displaymath}
+x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{--B_{ik}}}
+\end{displaymath}
+Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\textbf{x}, B) = (\textbf{x^{\prime}}, B^{\prime})$ where:
+\begin{displaymath}
+B_{ij}^{\prime} = \begin{cases} -- B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
+																B_{ij} + \frac{|B_{ik}|B_{kj} + B_{ik}|B_{kj}|}{2} & \mbox{ otherwise. }\\
+									\end{cases}
+\end{displaymath}
+and $\textbf{x^{\prime}} = {x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n}$. 
+Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = {x_1, \ldots, x_n}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables.
+\\
+
+ A cluster algebra is said to be of \textit{finite type} if the number of cluster variables that generate it is finite (if it has finitely many seeds).
+For each finite type cluster algebra, we can associate to its corresponding skew-symmetrisable matrix an edge-weighted, oriented graph, called a \textit{diagram}.
+We will often denote this diagram by $\Gamma$, and the vertex set of $\Gamma$ by $\V$.
+We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified.
+The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B{ij}B_{ji}|$ is the weight of the edge.
+A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B{ij}B_{ji}| \leq 3$ for $i, j \in {1, \ldots, n}$.
+By \cite{FZ02}[7.5], we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically.
+\\
+
+Just as we can define mutations of the seeds of a cluster variable, we can also define mutations of a diagram associated to a cluster algebra by the following set of rules:
+\begin{proposition}\cite{BM13}[Proposition 1.4]
+Let $B$ be a 2-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows: 
+\begin{itemize}
+\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
+\item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e.
+with $a,b$ positive), let $c$ be the weight on the edge $j \rightarrow i$, taken to be zero if there is no such arrow.
+Let $c'$ be determined by $c'\geq 0$ and
+$c+c' =$ max$(a,b)$. 
+Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.
+\end{itemize}
+\end{proposition}
+
+We notate this mutation of $\Gamma(B)$ at vertex $k$ by $\mu_k(\Gamma)$. \\
+
+\indent Given a diagram $\Gamma$, Barot and Marsh define for $i, j \in \V$,
+\begin{displaymath}
+m_{ij} = \begin{cases}    2 & \mbox{if } i \mbox{ and } j \mbox{ are not connected;} \\
+																	3 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 1;\\
+																	4 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 2;\\
+																	6 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 3.\\
+					\end{cases}
+\end{displaymath}
+
+Then, they define $W(\Gamma)$ to be the group generated by $s_i$, for $i \in \V$, under the following relations. Note that $e$ will denote the identity element of $W(\Gamma)$. 
+\begin{enumerate}
+\item $s_i^2 = e$ for all $i$;
+\item $(s_is_j)^{m_{ij}} = e$ for all $i \neq j$;
+\item For any chordless cycle $C$ in $\Gamma$, where
+\begin{displaymath}
+C = i_0 \rightarrow i_1 \rightarrow \cdots \rightarrow i_{d-1} \rightarrow i_0
+\end{displaymath}
+and all of the weights $w_k$ are $1$ or $w_0 = 2$, we have
+\begin{displaymath}
+(s_{i_0}s_{i_1}\cdots s_{i_{d-2}}s_{i_{d-1}}s_{i_{d-2}}\cdots s_{i_1})^2 =e.
+\end{displaymath}
+
+Using this group presentation, Barot and Marsh state the following result:
+\begin{theorem}\cite{BM13}[Theorem A]
+Let $\Gamma$ be the diagram associated to a seed in a cluster algebra of finite type. Then $W(\Gamma)$ is isomorphic to the corresponding reflection group.
+\end{theorem}
+
+In Section 3 of \cite{BM13}, Barot and Marsh provide an alteration of the group $W(\Gamma)$ in order to extend the group definition to any diagram of finite type. The group they define is as follows:
+
+\begin{definition}
+Let $W_{\Gamma}$ be the group with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations:
+\begin{itemize}
+\item{(R1)} $s_i^2 = e$ for all $i$
+\item{(R2)} $\left(s_is_j\right)^{m_{ij}} = e$ for all $i \neq j$
+\end{itemize}
+Furthermore, for a chordless cycle $C : i_0 \rightarrow i_1 \rightarrow \cdots \rightarrow i_{d-1} \rightarrow i_0$ and for $a = 0,1,2,\ldots, d-1$, define \textbf{$r\left(i_a, i_{a+1}\right) = s_{i_a}s_{i_{a+1}} \cdots s_{i_{a+d-1}}s_{i_{a+d-2}} \cdots s_{i_{a+1}}$}.\\
+
+\vspace{0.1cm}
+Then we have the following relations:
+\begin{itemize}
+\item{(R3)(a)} If all the weights in the edges of $C$ are $1$, then $r(i_a, i_{a+1})^2 = e$
+\item{(R3)(b)} If $C$ has some edges of weight $2$, then $r(i_a, i_{a+1})^k = e$ where $k = 4-w_a$ and $w_a$ is the weight of the edge $i_a\--\ i_{a-1}$
+\end{itemize}
+\end{definition}
+
+Defining the group $W_{\Gamma}$ with relations as shown above allows them to prove certain characteristics about the interaction between the relations in this group for the chordless cycles underlying the diagrams in question.
+In particular, they prove the following result, which we include as our main goal was to define analogous relations for an Artin group that would satisfy the same result.
+\begin{theorem}\cite{BM13}[Theorem 5.4a]
+Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
+\end{theorem}
+
+The rest of the paper will be devoted to building up our relations and Artin group structure in order to prove this result in the case of Artin groups.
 

### 2014-07-16 Paper.tex
added to section 5

--- 2014-07-15 Paper.tex
@@
 
-\begin{lem}
+\begin{lem}\label{lem:chordless_cycles}
 Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
@@
 
-\begin{defn} \label{grp def}
+\begin{defn}
 For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
@@
 \end{rem}
-
-\section{Symmetry among (R3') Relations}
-
-As in \cite{Barot}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,
-
-\begin{lem}
-Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
-\begin{tikzcd}
-i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
-\end{tikzcd}
-so that all edges have weight 1.
-Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and r(i_{a}, i_{a+1}) for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
-\end{lem}
-
-\begin{proof}
-As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
-\begin{align*}
-& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
-&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
-\end{align*}
-as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
-\end{proof}
-
-Furthermore, we obtain similar results for cycles containing edges of weight 2.
-
-\begin{lem} 
-Let $\Gamma$ be a diagram of finite type containing a 3-cycle as in (R3')(b) of ~\ref{grp def}.
-Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$.
-Then the relations (1) and (2) of (R3')(b) are equivalent, and they together imply the relation (3).
-\end{lem}
-
-\begin{proof}
-The equivalence of (1) and (2) follows from the fact that
-\begin{align*}
-& s_{1}^{-1}s_{3}s_{2}s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1}s_{3}s_{3}^{-1}s_{1} \\
-&= s_{1}^{-1}s_{3}s_{2}s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}s_{3}^{-1} \\
-&= s_{1}^{-1}s_{2}^{-1}s_{3}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{2}
-\end{align*}
-
-In showing that (1) and (2) imply (3), we will underline the terms being manipulated in each line for emphasis.
-\begin{align*}
-& s_{1}s_{3}s_{1}(s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1})s_{1}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}\underline{s_{1}s_{1}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
-&= \underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}\underline{s_{3}^{-1}s_{1}s_{3}s_{1}}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}s_{1}s_{3}\underline{s_{1}s_{3}^{-1}s_{3}s_{1}^{-1}}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}\underline{e}s_{1}s_{3}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}s_{3}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= \underline{s_{2}s_{3}s_{2}}s_{3}^{-1}s_{1}s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}s_{2}\underline{s_{3}s_{3}^{-1}}s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}s_{2}\underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}\underline{s_{2}s_{2}^{-1}}s_{3}^{-1}s_{1}\underline{s_{3}s_{3}^{-1}}s_{1}^{-1} \\
-&= \underline{s_{3}s_{3}^{-1}}\underline{s_{1}s_{1}^{-1}} \\
-&= e
-\end{align*}
-\end{proof}
-
-\begin{lem} 
-Let $\Gamma$ be a diagram of finite type containing a 4-cycle as in (R3')(c) of ~\ref{grp def}.
-Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$.
-Then the relations (1) and (2) of (R3')(c) are equivalent.
-\end{lem}
-
-\begin{proof}
-We have that
-\begin{align*}
-& s_{3}^{-1}s_{4}^{-1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{4}^{-1}s_{3}s_{2})s_{2}^{-1}s_{4}s_{3} \\
-&= s_{3}^{-1}s_{4}^{-1}(s_{2}s_{1}s_{2}^{-1})(s_{3}^{-1}s_{4}s_{3})(s_{2}s_{1}^{-1}s_{2}^{-1})s_{3}^{-1}s_{4}^{-1}s_{3}s_{4}s_{3} \\
-&= s_{3}^{-1}s_{4}^{-1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1}s_{3}^{-1}(s_{4}^{-1}s_{3}s_{4})s_{3} \\
-&= s_{3}^{-1}s_{4}^{-1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1}s_{4}
-\end{align*}
-\end{proof}
-
-Finally, we conclude the section by establishing a relationship between the groups defined by $\Gamma$ and $\Gamma^{op}$.
-
-\begin{lem} (Analogue of 4.6) 
-Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
-\end{lem}
-\begin{proof}
-One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$.
-To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
-But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$
-
-For a triangle as in (R3')(b) of ~\ref{grp def}, by the relation r'(1, 2) we have $$s_{1}s_{2}^{-1}s_{3}s_{2}s_{1}^{-1} = s_{2}^{-1}s_{3}s_{2}.$$ Hence $$s_{1}s_{3}s_{2}s_{3}^{-1}s_{1}^{-1} = s_{3}s_{2}s_{3}^{-1}.$$ But as before, this can occur if and only if $s_{1}^{-1}, s_{2}^{-1}, s_{3}^{-1}$ satisfy the relation r'(1, 3) in W$_{\Gamma^{op}}$.
-
-Finally, given a square labeled as in (R3')(c) and the relations r'(1, 2) and r'(3, 4), we have 
-\begin{align*}
-& s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
-&= s_{1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
-&= s_{1}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{1}^{-1} \\
-&= s_{1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2})s_{2}^{-1}s_{1}^{-1} \\
-&= s_{1}s_{2}(s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1})s_{2}^{-1}s_{1}^{-1} \\
-&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{2}s_{2}^{-1}s_{1}^{-1}s_{2} \\
-&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}
-\end{align*}
-But this relation holds if and only if $s_{1}^{-1}, \dots, s_{4}^{-1}$ satisfy r'(2, 1) in W$_{\Gamma^{Op}}$. Therefore, we are done.
-\end{proof}
-
-\section{Main Results}
 
@@
 
+Next we check that the $t_i$ satisfy the (R3) relations defined by the chordless cycles in $\Gamma'$.
+We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that the corresponding cycle relations hold in each case.
+By Lemmas \todo{add relevant lemma references}, we will only need one relation for each cycle, as this relation holding will imply that the others hold as well.
+Note that we have already checked cases (a)-(d) above, so we only need to check cases (e)-(l).
+
+\begin{enumerate}[a)]
+\setcounter{enumi}{4}
+\item
+Without loss of generality we label the vertices as follows:\todo{insert diagrams}
+
+\begin{align*}
+t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= (s_1s_2^{-1}s_1^{-1}s_1s_2s_1^{-1})s_1s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
+&= s_1s_2^{-1}s_1^{-1}\underline{s_1s_2s_1s_2^{-1}s_1^{-1}}s_3^{-1}s_4s_3s_1s_2s_1^{-1}\\
+&= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
+&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}}\\
+&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
+&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
+\end{align*}
+
+\item
+\begin{align*}
+t_4^{-1}t_1^{-1}t_2^{-1}t_3t_2t_1 &= s_4\underline{s_1^{-1}s_1}s_2^{-1}\underline{s_1^{-1}s_3s_1}s_2 \underline{s_1^{-1}s_1}\\
+&= s_4s_2^{-1}s_3s_2\\
+&= s_2^{-1}s_3s_2s_4\\
+&= (s_1^{-1}s_1)s_2^{-1}(s_1^{-1}\underline{s_1)s_3(s_1^{-1}}s_1)s_2(s_1^{-1}s_1s_4\\
+&= s_1^{-1}1s_2^{-1}s_1^{-1}s_3s_1s_2s_1^{-1}s_1s_4\\
+&= t_1^{-1}t_1^{-1}t_3t_2t_1t_4\\
+\end{align*}
+
+\item
+\begin{align*}
+t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4 &= \underline{s_3s_1}s_4^{-1}s_1^{-1}s_2s_1s_4\underline{s_1^{-1}s_3^{-1}s_1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4s_1^{-1}\\
+&= s_1\underline{s_3s_4^{-1}s_1^{-1}s_2s_1s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4}s_1^{-1}\\
+&= s_1s_1^{-1}\\
+&= e\\
+\end{align*}
+
+\item
+\begin{align*}
+t_2t_3^{-1}t_4t_3 &= s_2s_3^{-1}\underline{s_1s_4s_1^{-1}}s_3\\
+&= s_2s_3^{-1}s_4^{-1}s_1s_4s_3\\
+&= s_3^{-1}\underline{s_4^{-1}s_1s_4}s_3s_2\\
+&= s_3^{-1}s_1s_4s_1^{-1}s_3s_2\\
+&= t_3^{-1}t_4t_3t_2\\
+\end{align*}
+
+\item
+\begin{align*}
+t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2 &= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
+&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
+&= e\\
+\end{align*}
+
+\item
+\begin{align*}
+t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_k &= \underline{s_ks_hs_k^{-1}}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
+&= s_h^{-1}s_k\underline{s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_1}\\
+&=  s_h^{-1}s_ks_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_1s_h\\
+\end{align*}
+
+\end{enumerate}
+
 \bibliography{References}

### 2014-07-16 Paper.tex
small changes

@@
 \newcommand\on{s_1}
-\newcommand{\V}{$V(\Gamma)$}
+\newcommand\V{V(\Gamma)}
 
@@
 }
-\email{..., hpeck@millikin.edu}
+\email{...,david.hemminger@duke.edu, hpeck@millikin.edu}
 \date{\today}
@@
 
-\section{Introduction \& Motivation}
-
+\section{Introduction \& Motivation}\todo{let's add the statement of the main theorem to the introduction - David}
+
+\todo{use section labels rather than explicit numbers}
 In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras.
@@
 Section 4 specifies a relation for each case of the chordless cycles which suffices to show all the other relations in the group presentation hold.
-Finally, section 5 will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
+Finally, section \todo{for example}\ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
 \\
@@
 Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$.
-We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \left{x_1, \ldots, x_n\right}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix.
+We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix.
 Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
@@
 \end{displaymath}
-Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\textbf{x}, B) = (\textbf{x^{\prime}}, B^{\prime})$ where:
+Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\boldsymbol{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
 \begin{displaymath}
@@
 \end{displaymath}
-and $\textbf{x^{\prime}} = {x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n}$. 
+and $\textbf{x}^{\prime} = {x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n}$. 
 Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = {x_1, \ldots, x_n}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables.
@@
 Just as we can define mutations of the seeds of a cluster variable, we can also define mutations of a diagram associated to a cluster algebra by the following set of rules:
-\begin{proposition}\cite{BM13}[Proposition 1.4]
+\begin{prop}\cite{BM13}[Proposition 1.4]
 Let $B$ be a 2-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows: 
@@
 \end{itemize}
-\end{proposition}
+\end{prop}
 
@@
 \end{displaymath}
+\end{enumerate}
 
 Using this group presentation, Barot and Marsh state the following result:
-\begin{theorem}\cite{BM13}[Theorem A]
+\begin{thm}\cite{BM13}[Theorem A]
 Let $\Gamma$ be the diagram associated to a seed in a cluster algebra of finite type. Then $W(\Gamma)$ is isomorphic to the corresponding reflection group.
-\end{theorem}
+\end{thm}
 
@@
 
-\begin{definition}
+\begin{defn}
 Let $W_{\Gamma}$ be the group with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations:
@@
 \end{itemize}
-\end{definition}
+\end{defn}
 
@@
 In particular, they prove the following result, which we include as our main goal was to define analogous relations for an Artin group that would satisfy the same result.
-\begin{theorem}\cite{BM13}[Theorem 5.4a]
+\begin{thm}\cite{BM13}[Theorem 5.4a]
 Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
-\end{theorem}
+\end{thm}
 
@@
 
-\section{Main Results}
+\section{Proof of Main Result}\label{sec:proof_of_main}
 

### 2014-07-17 Paper.tex
added to Section 6

@@
 
-\begin{lem} (Analogue of 4.6) 
+\begin{lem}\label{lem:op_homomorphism}
 Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
@@
 
-\begin{lem}
-\label{5.2 analog}
-[Proposition 5.2 Analog] The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)$ and $(R3)$.
-\end{lem}
-
+In this section we prove our main result:
+
+\begin{thm}\label{thm:main}
+Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$.
+Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$\todo{we should pick notation for this}.
+\end{thm}
+
+Throughout this section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.
+To help us define an isomorphism from $A_{\Gamma}$ to $A_{\Gamma^{\prime}}$ we define an element $t_i\in A_{\Gamma}$ for each vertex $i\in \Gamma$ by
+
+\begin{displaymath}
+t_i = \begin{cases}    s_ks_is_k^{-1} & \mbox{if there is a (possibly weighted) arrow} i \rightarrow k \mbox{ in } \Gamma\\
+				s_i & \mbox{otherwise}\\
+	\end{cases}
+\end{displaymath}
+
+In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, whose proof we will defer until after the proof of Theorem \ref{thm:main}.
+
+\begin{prop}\label{prop:ti_relations}
+The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)^{\prime}$ and $(R3)^{\prime}$ associated to $\Gamma^{\prime}$.
+\end{prop}
+
+\begin{proof}[Proof of Theorem \ref{thm:main}]
+Define a homomorphism $\varphi\colon A(\Gamma^{\prime}) \rightarrow A(\Gamma)$ by sending each generator $s_i\in A(\Gamma^{\prime})$ to $t_i\in A(\Gamma)$.
+This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.
+By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta\colon A(\Gamma) \rightarrow A(\Gamma^{op})$ that sends $s_i\in A(\Gamma)$ to $s_i^{-1}$ in $A(\Gamma^{op})$ is well-defined.
+Define a homomorphism
+$$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
+
+Note that here we use the facts that $\left(\Gamma^{op}\right)^{op} = \Gamma$ and $\left(\Gamma^{op}\right)^{\prime} = \left(\Gamma^{\prime}\right)^{op}$.
+Suppose that there is an arrow $i\rightarrow k$ in $\Gamma$.
+Then there will be an arrow $k\rightarrow i$ in $\Gamma^{op}$ and hence an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^{\prime}$, so we have that
+
+$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(s_k^{-1}s_i^{-1}s_k)) = \Delta(s_i^{-1}) = s_i$$
+
+Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.
+In each of these cases we have that
+
+$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_i))) = \Delta(\varphi(s_i^{-1})) = \Delta(s_i^{-1}) = s_i$$
+
+Thus $\psi\circ\varphi$ is the identity map on $A(\Gamma^{\prime})$.  By a similar argument $\varphi\circ\psi$ is the identity map on $A(\Gamma)$, and hence $A(\Gamma)\cong A(\Gamma^{\prime}))$.
+\end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
 After Lemma \ref{lem:one_connected_to_k} we have left to check the relations $(R2)$ when both $i$ and $j$ are connected to $k$ and the relations $(R3)$.
@@
 \begin{align*}
-t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_k &= \underline{s_ks_hs_k^{-1}}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
-&= s_h^{-1}s_k\underline{s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_1}\\
-&=  s_h^{-1}s_ks_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_1s_h\\
+& t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
+&= s_h\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}s_h^{-1}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2 \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
+&= s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_2s_1s_h^{-1}s_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2s_1\\
+&= e\\
 \end{align*}
@@
 \end{enumerate}
+\end{proof}
 

### 2014-07-17 Paper.tex
rewrote Lemma 6.3 and incorporated it into proof of Prop 6.2

@@
 \begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
-After Lemma \ref{lem:one_connected_to_k} we have left to check the relations $(R2)$ when both $i$ and $j$ are connected to $k$ and the relations $(R3)$.
-Beginning with the relations $(R2)$, and following cases a-f from Corollary 2.3 in Barot and Marsh:
+First we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when $i=k$ or $j=k$.
+Without loss of generality suppose that $i=k$.
+Note that $m_{ij}^\prime = m_{ij}$.
+The only nontrivial case is when there is an arrow $j\rightarrow k =i$.
+Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.
+Suppose $m_{ij} = 3$.
+Then $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, and we have
+
+$$t_it_jt_i = s_is_is_js_i^{-1}s_i = s_is_is_j = s_is_js_is_js_i^{-1} = t_jt_it_j$$
+
+\noindent If $m_{ij} = 4$, then $s_is_js_is_j = s_js_is_js_i$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore
+
+$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{1-}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$
+
+\noindent If $m_{ij} = 6$, then $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$, so
+
+$$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$
+
+Next we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when at most one of $i$ and $j$ is connected to $k$.
+The only nontrivial case is when there is an arrow $i\rightarrow k$ or $j\rightarrow k$.
+Without loss of generality, suppose there is an arrow $i\rightarrow k$.
+Since $j$ is not connected to $k$, we know that $s_js_k = s_ks_j$.
+Suppose $m_{ij} = 2$.
+Then $s_is_j = s_js_i$, so we have that
+
+$$t_it_j = s_ks_is_k^{-1}s_j = s_js_ks_is_k^{-1} = t_jt_i$$
+
+\noindent If $m_{ij} = 3$, then $s_is_js_i = s_js_is_j$, so we have that
+
+$$t_it_jt_i = s_ks_is_k^{-1}s_js_ks_is_k^{-1} = s_ks_is_js_is_k^{-1} = s_ks_js_is_js_k^{-1} = s_js_ks_is_k^{-1}s_j = t_jt_it_j$$
+
+\noindent If $m_{ij} = 4$, then $s_is_js_is_j = s_js_is_js_i$, so we have that
+
+$$t_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = s_js_is_js_i$$
+
+\noindent Finally if $m_{ij} = 6$, then $s_is_js_is_js_is_j = s_js_is_js_is_js_i$, so we have that
+
+$$t_it_jt_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_is_js_k^{-1} = s_ks_js_is_js_is_js_is_k^{-1} = t_jt_it_jt_it_jt_i$$
+
+The remaining $(R2)'$ relations that need to be check are the relations for $t_i$ and $t_j$ when both $i$ and $j$ are connected to $k$.
+The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in \todo{where are they enumerated?}.
+We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.
+We also check that the corresponding $(R3^\prime)$ relations hold in cases (b), (d), (e), and (f).
 

### 2014-07-17 Paper.tex
section labels and main thm to intro

@@
 
-\section{Introduction \& Motivation}\todo{let's add the statement of the main theorem to the introduction - David}
-
-\todo{use section labels rather than explicit numbers}
+\section{Introduction \& Motivation}
+\label{sec:Intro}
+
 In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras.
@@
 They also proved that this group presentation is invariant up to isomorphism under the mutation equivalence relation.
+
+\begin{theorem}\cite[Theorem 5.4]{BM13}
+\begin{enumerate}
+\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
+\item Let $\mathscr{A}$ be a cluster algebra of finite type.
+Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
+\end{enumerate}
+\end{theorem}
+
 That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
 \\
-\indent Section 2 provides the necessary definitions and fundamental results from \cite{BM13} to provide motivation for our own results.
+
+\indent Section \ref{sec:main_definitions} provides the necessary definitions and fundamental results from \cite{BM13} to provide motivation for our own results.
 For further definitions and references on the topic, we refer the reader to \cite{FZ02}.
-Section 3  will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles.
-In this section we also define the appropriate relations for our Artin group presentations.
-Section 4 specifies a relation for each case of the chordless cycles which suffices to show all the other relations in the group presentation hold.
-Finally, section \todo{for example}\ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
+Section \ref{sec:finite-type_diagrams}  will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles.
+In Section \ref{sec:defn_artingroup} we define the appropriate relations for our Artin group presentations.
+Section \ref{sec:one_relation} specifies a relation for each case of the chordless cycles which suffices to show all the other relations in the group presentation hold.
+Finally, Section \todo{for example}\ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
 \\
@@
 \section{Definitions and Notation}
+\label{sec:main_definitions}
 
@@
 A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B{ij}B_{ji}| \leq 3$ for $i, j \in {1, \ldots, n}$.
-By \cite{FZ02}[7.5], we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically.
+By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically.
 \\
@@
 Just as we can define mutations of the seeds of a cluster variable, we can also define mutations of a diagram associated to a cluster algebra by the following set of rules:
-\begin{prop}\cite{BM13}[Proposition 1.4]
+\begin{prop}\cite[Proposition 1.4]{BM13}
 Let $B$ be a 2-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows: 
@@
 Using this group presentation, Barot and Marsh state the following result:
-\begin{thm}\cite{BM13}[Theorem A]
+\begin{thm}\cite[Theorem A]{BM13}
 Let $\Gamma$ be the diagram associated to a seed in a cluster algebra of finite type. Then $W(\Gamma)$ is isomorphic to the corresponding reflection group.
@@
 In particular, they prove the following result, which we include as our main goal was to define analogous relations for an Artin group that would satisfy the same result.
-\begin{thm}\cite{BM13}[Theorem 5.4a]
+\begin{thm}\cite[Theorem 5.4a]{BM13}
 Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
@@
 \section{Diagrams of Finite Type}
-
-In this section, we shall review the structure of diagrams of finite type, and how their cycles are effected by mutation. This section is simply a recap of \cite[Section 2]{BM13}.
+\label{sec:finite-type_diagrams}
+
+In this section, we shall review the structure of diagrams of finite type, and how their cycles are affected by mutation. This section is simply a recap of \cite[Section 2]{BM13}.
 
@@
 \section{The Group of a Diagram in an Artin Group}
+\label{sec:defn_artingroup}
 
@@
 \section{Symmetry among (R3') Relations}
-
-As in \cite{Barot}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,
+\label{sec:one_relation}
+
+As in \cite{BM13}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,
 

### 2014-07-18 Paper.tex
edited hailee's section and added cor 2.3 -from Aaron

@@
 \newtheorem{defn}[thm]{Definition}
+\newtheorem{note}[thm]{Notation}
 \newtheorem{rem}[thm]{Remark}
@@
 This introductory paper focused on structural features of cluster algebras, specifically that, in a given cluster, when any cluster variable is viewed as a rational function in the variables of the given cluster, this cluster variable is a Laurent polynomial.
-Fomin and Zelevinsky initially defined this type of commutative ring in order to make further strides in the areas of representation theory, Lie theory, and total positivity.
+\todo{The first sentence seems to be run on, and I'm very confused by it} Fomin and Zelevinsky defined cluster algebras in order to make further strides in the areas of representation theory, Lie theory, and total positivity.
 Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations.
-Of particular interest were \textit{finite-type} cluster algebras; that is, cluster algebras whose variables are generated through mutation on a finite number of \textit{seeds}.
-In the 2003 sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3.
+Of particular interest were \textit{finite-type} cluster algebras, that is, cluster algebras whose variables are generated through mutation on a finite number of \textit{seeds}.
+In the sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3.
 In particular, this proves that finite-type cluster algebras can be classified by Dynkin diagrams.
@@
 
-\begin{theorem}\cite[Theorem 5.4]{BM13}
+\todo{Fix mathscr on Hailee's first theorem which is commented out}
+
+\iffalse
+\begin{thm}\cite[Theorem 5.4]{BM13}
 \begin{enumerate}
@@
 \end{enumerate}
-\end{theorem}
+\end{thm}
+\fi
 
@@
 
-\indent Section \ref{sec:main_definitions} provides the necessary definitions and fundamental results from \cite{BM13} to provide motivation for our own results.
+\indent Section \ref{sec:main_definitions} provides the necessary definitions and fundamental results from \cite{BM13} to motivate our own results.
 For further definitions and references on the topic, we refer the reader to \cite{FZ02}.
 Section \ref{sec:finite-type_diagrams}  will review theory from \cite{FZ02}, \cite{FZ03} as well as review the classifications (from \cite{BM13}) of mutations of diagrams and their oriented chordless cycles.
-In Section \ref{sec:defn_artingroup} we define the appropriate relations for our Artin group presentations.
-Section \ref{sec:one_relation} specifies a relation for each case of the chordless cycles which suffices to show all the other relations in the group presentation hold.
+In Section \ref{sec:defn_artingroup}, we define the appropriate relations for our Artin group presentations.
+Section \ref{sec:one_relation} specifies how certain relations in chordless cycles imply other relations in those chordless cycles.
 Finally, Section \todo{for example}\ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
@@
 $c+c' =$ max$(a,b)$. 
-Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.
+Then $\Gamma(B)$ changes in a predetermined way, \todo{Say what this way is?} taking the case $c' = 0$ to mean no arrow between $i$ and $j$.
 \end{itemize}
@@
 
+\begin{note}
 We notate this mutation of $\Gamma(B)$ at vertex $k$ by $\mu_k(\Gamma)$. \\
+\end{note}
 
@@
 \end{displaymath}
+\todo{Maybe it's worth presenting definition 2.4 before this, and then saying it is equivalent to removing certain the (R3)(b) relations.
+Don't they actually present the definition you refer to in Definition 2.4 as the presentation?
+You say it is an alteration there, but I think it's the original definition}
 \end{enumerate}
@@
 Defining the group $W_{\Gamma}$ with relations as shown above allows them to prove certain characteristics about the interaction between the relations in this group for the chordless cycles underlying the diagrams in question.
-In particular, they prove the following result, which we include as our main goal was to define analogous relations for an Artin group that would satisfy the same result.
+In particular, they prove the following result.
 \begin{thm}\cite[Theorem 5.4a]{BM13}
@@
 
-The rest of the paper will be devoted to building up our relations and Artin group structure in order to prove this result in the case of Artin groups.
+The rest of the paper will be devoted to building up analogous relations, defined in ~\ref{grp def} to prove a similar result in the case of Artin groups.
 
@@
 See \cite[Proposition 2.1]{BM13}.
+\end{proof}
+
+\begin{cor}
+Let $\Gamma$ be the a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$
+
+\begin{enumerate}[(a)]
+\item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {1} (u)
+  ;
+  \draw[->]
+  (dl)to node[left]{1}(u) 
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+   (u)to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (u) to node[left]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+   \end{tikzpicture}
+	\item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl)to node[left]{1}(u) 
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {1}(u) 
+  ;
+  \draw[->]
+  (u) to node[left]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(dr)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+   \end{tikzpicture}
+
+\item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {2} (u)
+  ;
+  \draw[->]
+  (dl)to node[left]{1}(u) 
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+   (u)to node[right] {2} (dr)
+  ;
+  \draw[->]
+  (u) to node[left]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+   \end{tikzpicture}
+   \item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr)to node[right] {1} (u) 
+  ;
+  \draw[->]
+  (u) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{2}(dr)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+   \end{tikzpicture}
+   \item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {2} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{1}(u)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {2} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{1}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{2}(dr)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+   \end{tikzpicture}
+	\item 	
+	\begin{tikzpicture}[baseline=-0.5ex]
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+   (u) to node[right] {2}(dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (dr) to node[right] {2} (u)
+  ;
+  \draw[->]
+  (u) to node[left]{2}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{1}(dr)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+   \end{tikzpicture}
+\end{enumerate}
+
+\end{cor}
+\begin{proof}
+See \cite[Corollary 2.3]{BM13}.
 \end{proof}

### 2014-07-18 Paper.tex
Edited First 5 Sections

@@
 here \\
-}
-\email{...,david.hemminger@duke.edu, hpeck@millikin.edu}
+Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556}
+\email{..., jhaley3@nd.edu, david.hemminger@duke.edu, hpeck@millikin.edu}
 \date{\today}
@@
 Then in 2013, Barot and Marsh defined the presentation of a reflection group associated to a Dynkin diagram in terms of an edge-weighted, oriented graph, and proved that this group is invariant (up to isomorphism) under diagram mutations.
-In this paper, we extend Barot and Marsh's results to Artin group presentations, defining new relations for when the generators are not self-inverses, and again showing mutation-invariance for these presentations.
+In this paper, we extend Barot and Marsh's results to Artin group presentations, defining new relations for when the generators are not self-inverses and again showing mutation-invariance for these presentations.
 \end{abstract}
@@
 
-A \textit{cluster algebra} is a commutative ring with unity but without zero-divisors, and it can be generated by a set of generators called \textit{cluster variables} that satisfy certain exchange relations.
+A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations.
 Following the style of \cite{FZ02} and \cite{BM13}, we will define cluster algebras in terms of \textit{skew-symmetrisable} matrices (that is, a matrix $B$ such that there exists a diagonal matrix $D$ of the same size with $D_{ii} >0$ such that $DB$ is skew-symmetric).
@@
 \begin{displaymath}
-x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{--B_{ik}}}
+x_k^{\prime}x_k = \prod_{B_{ik} > 0}{x_i^{B_{ik}}} + \prod_{B_{ik} < 0}{x_i^{-B_{ik}}}
 \end{displaymath}
@@
 \begin{displaymath}
-B_{ij}^{\prime} = \begin{cases} -- B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
+B_{ij}^{\prime} = \begin{cases} - B_{ij} & \mbox{ if } i = k \mbox{ or } j = k;\\
 																B_{ij} + \frac{|B_{ik}|B_{kj} + B_{ik}|B_{kj}|}{2} & \mbox{ otherwise. }\\
@@
 We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified.
-The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B{ij}B_{ji}|$ is the weight of the edge.
-A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B{ij}B_{ji}| \leq 3$ for $i, j \in {1, \ldots, n}$.
+The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge.
+A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in {1, \ldots, n}$.
 By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically.
@@
 
-Just as we can define mutations of the seeds of a cluster variable, we can also define mutations of a diagram associated to a cluster algebra by the following set of rules:
+Just as we can define mutations of the seeds of a cluster variable, we can also define mutations of a diagram associated to a cluster algebra of finite type by the following set of rules:
 \begin{prop}\cite[Proposition 1.4]{BM13}
@@
 
-Defining the group $W_{\Gamma}$ with relations as shown above allows them to prove certain characteristics about the interaction between the relations in this group for the chordless cycles underlying the diagrams in question.
+Defining the group $W_{\Gamma}$ with relations as shown above allows them to prove certain characteristics of the interaction between the relations in this group for the chordless cycles underlying the diagrams in question.
 In particular, they prove the following result.
@@
 \item $s_{i}s_{j}^{-1}s_{k}s_{j} = s_{j}^{-1}s_{k}s_{j}s_{i}$
-\item $s_{j}s_{k}^{-1}s_{i}s_{k} = s_{k}^{-1}s_{i}s_{k}s_{j}$
-\item $s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i} = e.$
+\item $s_{k}s_{i}^{-1}s_{j}s_{i} = s_{i}^{-1}s_{j}s_{i}s_{k}$
+\item $s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$
 \end{enumerate}
@@
 \begin{rem}
-Note that if $\Gamma$ is the graph associated to a dynikin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that dynkin diagram.
-This is the case since in this case we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin Group.
+Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that Dynkin diagram.
+This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin Group.
 \end{rem}
@@
 \end{proof}
-
 Furthermore, we obtain similar results for cycles containing edges of weight 2.
-
 \begin{lem} 
@@
 \begin{align*}
-& s_{1}^{-1}s_{3}s_{2}s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1}s_{3}s_{3}^{-1}s_{1} \\
-&= s_{1}^{-1}s_{3}s_{2}s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}s_{3}^{-1} \\
-&= s_{1}^{-1}s_{2}^{-1}s_{3}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{2}
+& s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
+&= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
+&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i}
 \end{align*}
@@
 \begin{align*}
-& s_{1}s_{3}s_{1}(s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1})s_{1}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}\underline{s_{1}s_{1}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
-&= \underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}\underline{s_{3}^{-1}s_{1}s_{3}s_{1}}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}s_{1}s_{3}\underline{s_{1}s_{3}^{-1}s_{3}s_{1}^{-1}}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}\underline{e}s_{1}s_{3}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{2}s_{3}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= \underline{s_{2}s_{3}s_{2}}s_{3}^{-1}s_{1}s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}s_{2}\underline{s_{3}s_{3}^{-1}}s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}s_{2}\underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
-&= s_{3}\underline{s_{2}s_{2}^{-1}}s_{3}^{-1}s_{1}\underline{s_{3}s_{3}^{-1}}s_{1}^{-1} \\
-&= \underline{s_{3}s_{3}^{-1}}\underline{s_{1}s_{1}^{-1}} \\
+& s_{k}s_{j}s_{k}(s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k})s_{k}^{-1}s_{j}^{-1}s_{k}^{-1} \\
+&= s_{k}\underline{s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}\underline{s_{k}s_{k}^{-1}}s_{j}^{-1}s_{k}^{-1} \\
+&= \underline{s_{k}s_{k}^{-1}}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
+&= s_{i}\underline{s_{j}^{-1}s_{k}s_{j}s_{k}}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
+&= s_{i}s_{k}s_{j}\underline{s_{k}s_{j}^{-1}s_{j}s_{k}^{-1}}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
+&= s_{i}\underline{e}s_{k}s_{j}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
+&= s_{i}s_{j}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
+&= \underline{s_{i}s_{j}s_{i}}s_{j}^{-1}s_{k}s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
+&= s_{j}s_{i}\underline{s_{j}s_{j}^{-1}}s_{k}\underline{s_{j}s_{k}s_{j}^{-1}s_{k}^{-1}}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1} \\
+&= s_{j}s_{i}\underline{s_{k}s_{k}^{-1}}\underline{s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}}s_{j}^{-1}s_{k}^{-1} \\
+&= s_{j}\underline{s_{i}s_{i}^{-1}}s_{j}^{-1}s_{k}\underline{s_{j}s_{j}^{-1}}s_{k}^{-1} \\
+&= \underline{s_{j}s_{j}^{-1}}\underline{s_{k}s_{k}^{-1}} \\
 &= e
@@
 \begin{align*}
-& s_{3}^{-1}s_{4}^{-1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{4}^{-1}s_{3}s_{2})s_{2}^{-1}s_{4}s_{3} \\
-&= s_{3}^{-1}s_{4}^{-1}(s_{2}s_{1}s_{2}^{-1})(s_{3}^{-1}s_{4}s_{3})(s_{2}s_{1}^{-1}s_{2}^{-1})s_{3}^{-1}s_{4}^{-1}s_{3}s_{4}s_{3} \\
-&= s_{3}^{-1}s_{4}^{-1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1}s_{3}^{-1}(s_{4}^{-1}s_{3}s_{4})s_{3} \\
-&= s_{3}^{-1}s_{4}^{-1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1}s_{4}
+& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{l}^{-1}s_{k}s_{j})s_{j}^{-1}s_{l}s_{k} \\
+&= s_{k}^{-1}s_{l}^{-1}(s_{j}s_{i}s_{j}^{-1})(s_{k}^{-1}s_{l}s_{k})(s_{j}s_{i}^{-1}s_{j}^{-1})s_{k}^{-1}s_{l}^{-1}s_{k}s_{l}s_{k} \\
+&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{k}^{-1}(s_{l}^{-1}s_{k}s_{l})s_{k} \\
+&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{l}
 \end{align*}
@@
 
-Finally, we conclude the section by establishing a relationship between the groups defined by $\Gamma$ and $\Gamma^{op}$.
+Finally, we conclude the section by establishing a relationship between the groups defined by $\Gamma$ and $\Gamma^{op}$, the diagram obtained by reversing all arrows in $\Gamma$.
 
@@
 \begin{proof}
-One can see that the elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the relation in W$_{\Gamma}$.
+One can see that the inverse elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in W$_{\Gamma}$.
 To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
-But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this can only occur if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$
-
-For a triangle as in (R3')(b) of ~\ref{grp def}, by the relation r'(1, 2) we have $$s_{1}s_{2}^{-1}s_{3}s_{2}s_{1}^{-1} = s_{2}^{-1}s_{3}s_{2}.$$ Hence $$s_{1}s_{3}s_{2}s_{3}^{-1}s_{1}^{-1} = s_{3}s_{2}s_{3}^{-1}.$$ But as before, this can occur if and only if $s_{1}^{-1}, s_{2}^{-1}, s_{3}^{-1}$ satisfy the relation r'(1, 3) in W$_{\Gamma^{op}}$.
+But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$
+
+For a triangle as in (R3')(b) of ~\ref{grp def}, by the relation r'(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation r'(k, j) in W$_{\Gamma^{op}}$.
 
@@
 \begin{align*}
-& s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
-&= s_{1}s_{1}^{-1}s_{2}s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1} \\
-&= s_{1}s_{2}s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{1}^{-1} \\
-&= s_{1}s_{2}(s_{1}s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2})s_{2}^{-1}s_{1}^{-1} \\
-&= s_{1}s_{2}(s_{2}^{-1}s_{3}^{-1}s_{4}s_{3}s_{2}s_{1})s_{2}^{-1}s_{1}^{-1} \\
-&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{2}s_{2}^{-1}s_{1}^{-1}s_{2} \\
-&= s_{1}s_{4}s_{3}s_{4}^{-1}s_{1}^{-1}s_{2}
-\end{align*}
-But this relation holds if and only if $s_{1}^{-1}, \dots, s_{4}^{-1}$ satisfy r'(2, 1) in W$_{\Gamma^{Op}}$. Therefore, we are done.
+& s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
+&= s_{i}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1} \\
+&= s_{i}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{i}^{-1} \\
+&= s_{i}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j})s_{j}^{-1}s_{i}^{-1} \\
+&= s_{i}s_{j}s_{j}^{-1}(s_{k}^{-1}s_{l}s_{k})s_{j}(s_{i}s_{j}^{-1}s_{i}^{-1}) \\
+&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{j}s_{j}^{-1}s_{i}^{-1}s_{j} \\
+&= s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}
+\end{align*}
+But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy r'(j, i) in W$_{\Gamma^{op}}$. Therefore, we are done.
 \end{proof}

### 2014-07-18 Paper.tex
small changes

--- 2014-07-18 Paper.tex
@@
 \usepackage{natbib}
+\usepackage[mathscr]{euscript}
 
@@
 
-\todo{Fix mathscr on Hailee's first theorem which is commented out}
-
-\iffalse
 \begin{thm}\cite[Theorem 5.4]{BM13}
@@
 \end{thm}
-\fi
 
@@
 Section \ref{sec:one_relation} specifies how certain relations in chordless cycles imply other relations in those chordless cycles.
-Finally, Section \todo{for example}\ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
+Finally, Section \ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
 \\
@@
 \begin{displaymath}
-t_i = \begin{cases}    s_ks_is_k^{-1} & \mbox{if there is a (possibly weighted) arrow} i \rightarrow k \mbox{ in } \Gamma\\
+t_i = \begin{cases}    s_ks_is_k^{-1} & \mbox{if there is a (possibly weighted) arrow } i \rightarrow k \mbox{ in } \Gamma\\
 				s_i & \mbox{otherwise}\\

### 2014-07-18 Paper.tex
made some edits to jacob's part -aaron

--- 2014-07-18 Paper.tex
@@
 Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
+
+\begin{equation*}
 \begin{tikzcd}
@@
 \end{tikzcd}
+\end{equation*}
 so that all edges have weight 1.
@@
 \end{prop}
+\todo{This propositions seems to be worded confusingly.
+I see this is what they say in Barot and Marsh, but I still find it confusing.
+Maybe it's clearer to say that if we take $p_i$ to be the generators of $\Gamma',$ and they satisfy a relation $r(p_1,\ldots, p_{|\Gamma|}) = e,$ if and only if $t_i$ satisfy the same relation $r(t_1,\ldots, t_{|\Gamma|}) = e.$}
+\todo{Maybe it would make more sense to break this up into 2 lemmas, like Barot and Marsh do}
 
@@
 Define a homomorphism $\varphi\colon A(\Gamma^{\prime}) \rightarrow A(\Gamma)$ by sending each generator $s_i\in A(\Gamma^{\prime})$ to $t_i\in A(\Gamma)$.
-This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.
+\todo{Weren't the $t_i$ defined in terms of the $s_i$ for $A(\Gamma)$?
+It seems like there are two different $s_i,$ one for $\Gamma$ and one for $\Gamma'$ and this is confusing me.}  This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.
 By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta\colon A(\Gamma) \rightarrow A(\Gamma^{op})$ that sends $s_i\in A(\Gamma)$ to $s_i^{-1}$ in $A(\Gamma^{op})$ is well-defined.
@@
 $$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
-
+\todo{It seems like there is an abuse of notation here.
+You have defined $\phi:A(\Gamma') \rightarrow A(\Gamma),$ but it looks like it is mapping $A(\Gamma^{op} \rightarrow A((\Gamma^{op})')$ here.
+Please make clearer what this map $\phi$ is.}
 Note that here we use the facts that $\left(\Gamma^{op}\right)^{op} = \Gamma$ and $\left(\Gamma^{op}\right)^{\prime} = \left(\Gamma^{\prime}\right)^{op}$.
@@
 $$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(s_k^{-1}s_i^{-1}s_k)) = \Delta(s_i^{-1}) = s_i$$
-
+\todo{I think you have the right idea, but I don't understand how you always have elements in $A(\Gamma)$ and never elements in $A(\Gamma').$ I think the problem lies in the definition of $\phi.$}
 Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.
@@
 The only nontrivial case is when there is an arrow $j\rightarrow k =i$.
-Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.
+\todo{Isn't there also the case of an arrow from k to j?
+Obviously it's symmetric, but isn't it worth saying?}  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.
 Suppose $m_{ij} = 3$.
@@
 
-$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{1-}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$
+$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$
+
+\todo{An extra step inserting and removing inverses here would be helpful.}
 
@@
 $$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$
+\todo{An extra step inserting and removing inverses here would be helpful, as above}
+
+\todo{Instead of saying If mij = 3, try \vskip.1in
+\noindent
+{\sf The case $m_{ij} = 3$}}
 
@@
 Suppose $m_{ij} = 2$.
-Then $s_is_j = s_js_i$, so we have that
+\todo{It seems like the previous two sentences should be switched?
+Again try using cases to break it up more clearly for the reader, as I mentioned in a previous todo.} Then $s_is_j = s_js_i$, so we have that
 
 $$t_it_j = s_ks_is_k^{-1}s_j = s_js_ks_is_k^{-1} = t_jt_i$$
+\todo{It looks like you're also using here that $s_j$ commutes with $s_k^{-1}.$ I agree it's obvious, but maybe it's worth spelling out}
 

### 2014-07-18 Paper.tex

@@
 Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
-
-\begin{equation*}
 \begin{tikzcd}
@@
 \end{tikzcd}
-\end{equation*}
 so that all edges have weight 1.
@@
 \end{prop}
-\todo{This propositions seems to be worded confusingly.
-I see this is what they say in Barot and Marsh, but I still find it confusing.
-Maybe it's clearer to say that if we take $p_i$ to be the generators of $\Gamma',$ and they satisfy a relation $r(p_1,\ldots, p_{|\Gamma|}) = e,$ if and only if $t_i$ satisfy the same relation $r(t_1,\ldots, t_{|\Gamma|}) = e.$}
-\todo{Maybe it would make more sense to break this up into 2 lemmas, like Barot and Marsh do}
 
@@
 Define a homomorphism $\varphi\colon A(\Gamma^{\prime}) \rightarrow A(\Gamma)$ by sending each generator $s_i\in A(\Gamma^{\prime})$ to $t_i\in A(\Gamma)$.
-\todo{Weren't the $t_i$ defined in terms of the $s_i$ for $A(\Gamma)$?
-It seems like there are two different $s_i,$ one for $\Gamma$ and one for $\Gamma'$ and this is confusing me.}  This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.
+This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.
 By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta\colon A(\Gamma) \rightarrow A(\Gamma^{op})$ that sends $s_i\in A(\Gamma)$ to $s_i^{-1}$ in $A(\Gamma^{op})$ is well-defined.
@@
 $$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
-\todo{It seems like there is an abuse of notation here.
-You have defined $\phi:A(\Gamma') \rightarrow A(\Gamma),$ but it looks like it is mapping $A(\Gamma^{op} \rightarrow A((\Gamma^{op})')$ here.
-Please make clearer what this map $\phi$ is.}
+
 Note that here we use the facts that $\left(\Gamma^{op}\right)^{op} = \Gamma$ and $\left(\Gamma^{op}\right)^{\prime} = \left(\Gamma^{\prime}\right)^{op}$.
@@
 $$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(s_k^{-1}s_i^{-1}s_k)) = \Delta(s_i^{-1}) = s_i$$
-\todo{I think you have the right idea, but I don't understand how you always have elements in $A(\Gamma)$ and never elements in $A(\Gamma').$ I think the problem lies in the definition of $\phi.$}
+
 Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.
@@
 The only nontrivial case is when there is an arrow $j\rightarrow k =i$.
-\todo{Isn't there also the case of an arrow from k to j?
-Obviously it's symmetric, but isn't it worth saying?}  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.
+Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.
 Suppose $m_{ij} = 3$.
@@
 
-$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$
-
-\todo{An extra step inserting and removing inverses here would be helpful.}
+$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{1-}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$
 
@@
 $$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$
-\todo{An extra step inserting and removing inverses here would be helpful, as above}
-
-\todo{Instead of saying If mij = 3, try \vskip.1in
-\noindent
-{\sf The case $m_{ij} = 3$}}
 
@@
 Suppose $m_{ij} = 2$.
-\todo{It seems like the previous two sentences should be switched?
-Again try using cases to break it up more clearly for the reader, as I mentioned in a previous todo.} Then $s_is_j = s_js_i$, so we have that
+Then $s_is_j = s_js_i$, so we have that
 
 $$t_it_j = s_ks_is_k^{-1}s_j = s_js_ks_is_k^{-1} = t_jt_i$$
-\todo{It looks like you're also using here that $s_j$ commutes with $s_k^{-1}.$ I agree it's obvious, but maybe it's worth spelling out}
 

### 2014-07-19 Paper.tex
just after first meeting
made edits to section -aaron

--- 2014-07-18 Paper.tex
@@
 \newtheorem{note}[thm]{Notation}
+\newtheorem{ex}[thm]{Example}
 \newtheorem{rem}[thm]{Remark}
@@
 Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556}
-\email{..., jhaley3@nd.edu, david.hemminger@duke.edu, hpeck@millikin.edu}
+\email{aaronlandesman@college.harvard.com, jhaley3@nd.edu, david.hemminger@duke.edu, hpeck@millikin.edu}
 \date{\today}
@@
 \begin{displaymath}
+\label{mij_defn}
 m_{ij} = \begin{cases}    2 & \mbox{if } i \mbox{ and } j \mbox{ are not connected;} \\
@@
 
-In this section, we shall review the structure of diagrams of finite type, and how their cycles are affected by mutation. This section is simply a recap of \cite[Section 2]{BM13}.
+In this section, we shall review the structure of diagrams of finite type, and how their cycles are affected by mutation.
+This section is simply a recap of \cite[Section 2]{BM13}.
+First, in Proposition ~\ref{cycle_types}, all types of chordless cycles in diagrams of finite type are classified.
+Second, in Corollary ~\ref{local_three_picture} all possible local pictures between a mutated vertex and two adjacent vertices are drawn.
+Finally, in ~\ref{lem:chordless_cycles}, all chordless cycles introduced from a mutation are drawn.
+These three lemmas will be crucial in proving the main result Theorem ~\ref{thm:main}, as they will allow us to inspect precisely which relations are added and removed after mutating at a prescribed vertex.
 
@@
 \begin{prop}
+\label{cycle_types}
 Let $\Gamma$ be a diagram of finite type.
@@
 \begin{cor}
+\label{local_three_picture}
 Let $\Gamma$ be the a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$
@@
     \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
   {
@@
     \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
+    \node [yshift = -.9 cm] at (u){$C'$};
    \end{tikzpicture}
@@
     \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
   {
@@
     \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
-
+ 	\node [yshift = -.7 cm,xshift = .7 cm] at (ul){$C'$};
    \end{tikzpicture}
@@
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
   {
@@
     \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+ 	\node [yshift = -.95 cm,xshift = .95 cm] at (ul){$C'$};
     \end{tikzpicture}
@@
     \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+ 	\node [yshift = -.95 cm,xshift = .3 	5 cm] at (ul){$C'$};
     \end{tikzpicture}
@@
     \node at (dl.south){$h$};
+
+ 	\node [yshift = -.9 cm] at (um){$C'$};
     \end{tikzpicture}
@@
     \node at (dl.south){$h$};
+ 	\node [yshift = -.9 cm] at (um){$C'$};
     \matrix[matrix of math nodes,column sep={40pt,between origins},row
@@
 
-\section{The Group of a Diagram in an Artin Group}
+\section{The Artin Group of a Diagram}
 \label{sec:defn_artingroup}
 
+In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin Group associated to a finite type diagram.
+This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since artin groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
+
+\subsection{Artin Groups}
+
+\begin{note}
+Let 
+\begin{align*}
+	\langle x_i,x_j \rangle ^k = \begin{cases}
+	(x_ix_j)^{\frac{k}{2}}, &\text{ if }k \equiv 0 \pmod 2\\
+	(x_ix_j)^{\frac{k-1}{2}}x_i &\text{ if } k \equiv 1 \pmod 2
+\end{cases}
+\end{align*}
+That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k.$
+
+\end{note}
+\begin{defn}
+For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix which whose entries can take values in the real numbers or infinity, satisfying $m_{i,j} = m_{j,i}$ we define the associated {\it Artin Group} in terms of generators and relations by
+\begin{align*}
+	A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
+\end{align*}
+\end{defn}
+
+\begin{rem}
+Each Artin group has an associated Coxeter Group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type.
+To each Artin group of finite type we can assign it the same dynkin diagram which is assigned to the coxeter group associated to the Artin group.
+\end{rem}
+
+\subsection{The Group associated to Diagram}
+
 \begin{defn} \label{grp def}
+
 For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
-The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the relations
+The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
 \begin{itemize}
-	\item[(R2')] For all $i \neq j,$ we add the relations
-	\\
-$	\begin{cases}
-	s_is_j=s_js_i, &\text{ if there is no edge between $i$ and $j$}\\
-	s_is_js_i = s_js_is_j &\text{ if there is an edge of weight 1 between $i$ and $j.$}\\
-	s_is_js_is_j = s_js_is_js_i &\text{ if there is an edge of weight 2 between $i$ and $j$.}\\
-	s_is_js_is_js_is_j = s_js_is_js_is_js_i &\text{ if there is an edge of weight 3 between $i$ and $j$.}
-\end{cases}$
-\item[(R3')(a)] For every chordless cycle of the form
+	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
+	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$
+
+\item[(R3)] For every ordered chordless cycle of the form
 
@@
 
-such that all edges have weight 1, for all $i,$ with $0 \leq a \leq d-1,$ we include the relation 
+such that either
+\begin{enumerate}
+	\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
+	\item All edges in the chordless cycle have weight $1.$
+\end{enumerate}
+we include the relation
 \begin{align*}
@@
 Where subscripts are taken $\pmod d.$ 
-
-\item[(R3')(b)] For every chordless cycle of the form \begin{tikzpicture}[baseline=-0.5ex]
-    \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
-  {
-    && |[name = u]|\circ& \\
-    %
-    &|[name=dl]| \circ & &|[name=dr]| \circ \\
-  };
-\draw[->]
-  (u) to node[right] {1} (dr)
-  ;
-  \draw[->]
-  (dl) to node[left]{2}(u)
-  ;
-  \draw[->]
-  (dr) to node[below]{2}(dl)
-  ;
-  \node [yshift = .4 cm] at (u){i};
-    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
-    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){k};
-   \end{tikzpicture}
-   we include the three relations
-   \begin{enumerate}[(1)]
-\item $s_{i}s_{j}^{-1}s_{k}s_{j} = s_{j}^{-1}s_{k}s_{j}s_{i}$
-\item $s_{k}s_{i}^{-1}s_{j}s_{i} = s_{i}^{-1}s_{j}s_{i}s_{k}$
-\item $s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$
-\end{enumerate}
-\item[(R3')(c)] For every chordless cycle of the form
-\begin{tikzpicture}[baseline=-0.5ex]
+\end{itemize}
+\end{defn}
+
+\begin{rem}
+In the above definition, the chordless cycle is ordered, which means that two cycles are considered different if they are cyclic rotations of eachother.
+\end{rem}
+
+\begin{rem}
+We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analagous to that of \cite{BM13} at the beginning of Section 3.
+Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13}.
+Namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma,$ then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of section 3 in \cite{BM13}.
+\end{rem}
+
+\begin{rem}
+Throughout the remainder of the paper, we shall frequently discuss relations on one diagram of finite type, $\Gamma,$ and another diagram of finite type $\Gamma^\prime.$ In order to distinguish the relations in these two groups, we shall refer to the relations on $\Gamma$ as $(R2),(R3)$ and the relations on $\Gamma^\prime$ as $(R2^\prime),(R3^\prime).$
+\end{rem}
+
+\begin{ex}
+The relations $(R2),(R3)$ in that $\Gamma$ is a square with all edges of weight 1 are as follows:
+\[\Gamma =\begin{tikzpicture}[baseline=-0.5ex]
  \matrix[matrix of math nodes,column sep={40pt,between origins},row
@@
   {
-    & |[name = ul]|\circ & |[name = ur]|\circ\\
+    & |[name = ul]|\circ& |[name = ur]|\circ\\
     %
@@
   };
-\draw[->]
-  (ul) to node[above] {1} (ur)
-  ;
-  \draw[->]
-  (dl) to node[left]{2}(ul)
-  ;
-  \draw[->]
-  (dr) to node[below]{1}(dl)
-  ;
-  \draw[->]
-  (ur) to node[right]{2} (dr)
-  ;
-    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){i};
-   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){j};
-    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){k};
-    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){l};
-
-   \end{tikzpicture}
-
-   we include the two relations
-   \begin{enumerate}[(1)]
-\item $s_{i}s_{j}^{-1}s_{k}^{-1}s_ls_{k}s_j = s_{j}^{-1}s_{k}^{-1}s_ls_ks_{j}s_{i}$
-\item $s_{k}s_{l}^{-1}s_{i}^{-1}s_js_{i}s_l = s_{l}^{-1}s_{i}^{-1}s_js_is_{l}s_{k}$
+\draw
+  (ul) -- node[above] {1} (ur)
+  ;
+  \draw
+  (dl) -- node[left]{1}(ul)
+  ;
+  \draw
+  (dr) -- node[below]{1}(dl)
+  ;
+  \draw
+  (ur) -- node[right]{1} (dr)
+  ;  
+      \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
+   \end{tikzpicture}\]
+   \begin{enumerate}
+	\item[(R2)]
+	\begin{itemize}
+	\item $\langle s_1,s_2 \rangle^3 = \langle s_2,s_21 \rangle^3$
+	\item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3$
+	\item $\langle s_3,s_4 \rangle^3 = \langle s_4,s_3 \rangle^3$
+	\item $\langle s_4,s_1 \rangle^3 = \langle s_1,s_4 \rangle^3$
+\end{itemize} 
+	\item[(R3)]
+	\begin{itemize}
+	\item $s_{1}s_{2}^{-1}s_{3}^{-1}s_4s_{3}s_2 = s_{2}^{-1}s_{3}^{-1}s_4s_3s_{2}s_{1}$
+	\item $s_{2}s_{3}^{-1}s_{4}^{-1}s_1s_{4}s_3 = s_{3}^{-1}s_{4}^{-1}s_1s_4s_{3}s_{2}$
+	\item $s_{3}s_{4}^{-1}s_{1}^{-1}s_2s_{1}s_4 = s_{4}^{-1}s_{1}^{-1}s_2s_1s_{4}s_{3}$
+	\item $s_{4}s_{1}^{-1}s_{2}^{-1}s_3s_{2}s_1 = s_{1}^{-1}s_{2}^{-1}s_3s_2s_{1}s_{4}$
+\end{itemize} 
 \end{enumerate}
-\end{itemize}
-\end{defn}
+\end{ex}
 

### 2014-07-19 Paper.tex
correctly capitalized Artin -aaron

@@
 In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin Group associated to a finite type diagram.
-This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since artin groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
+This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
 
@@
 For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
-The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
+The associated Artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
 \begin{itemize}

### 2014-07-20 Paper.tex
fixed title

@@
 
-\title{Artin Group Presentations of Reflection Groups}
+\title{Artin Group Presentations Arising from Cluster Algebras}
 \author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
@@
 Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556}
-\email{aaronlandesman@college.harvard.com, jhaley3@nd.edu, david.hemminger@duke.edu, hpeck@millikin.edu}
+\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
 \date{\today}

### 2014-07-20 Paper.tex
Section 5 Edits

@@
 \begin{align*}
-	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}.
-\end{align*}
-Where subscripts are taken $\pmod d.$ 
+	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
+\end{align*}
+where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
 \end{itemize}
@@
 
-\section{Symmetry among (R3') Relations}
+\section{Symmetry among (R3) Relations}
 \label{sec:one_relation}
 
-As in \cite{BM13}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,
+Given the relations (R2), many of the relations in (R3) become redundant. For example,
 
@@
 \end{equation*}
+
 so that all edges have weight 1.
-Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
+Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2) and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3) hold for C.
 \end{lem}
@@
 \begin{proof}
-As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
+As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $A_{\Gamma}$ satisfies the relation r(0, 1). Then we have 
 \begin{align*}
@@
 Furthermore, we obtain similar results for cycles containing edges of weight 2.
-\begin{lem} 
-Let $\Gamma$ be a diagram of finite type containing a 3-cycle as in (R3')(b) of ~\ref{grp def}.
-Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$.
-Then the relations (1) and (2) of (R3')(b) are equivalent, and they together imply the relation (3).
+\begin{lem} \label{2tri}
+Let $\Gamma$ be a diagram of finite type containing the following 3-cycle:
+
+\begin{tikzpicture}[baseline=-0.5ex]
+   \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (10,0)
+  {
+    && |[name = u]| {k} \circ& \\
+    %
+    &|[name=dl]|{j} \circ & &|[name=dr]| \circ {i} \\
+  };
+\draw[->]
+  (u) to node[right] {2} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+
+   \end{tikzpicture}
+and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations r(i, j) and r(k, i) are equivalent.
 \end{lem}
@@
 \begin{proof}
-The equivalence of (1) and (2) follows from the fact that
+The lemma follows from the fact that
 \begin{align*}
@@
 \end{align*}
-
-In showing that (1) and (2) imply (3), we will underline the terms being manipulated in each line for emphasis.
+\end{proof}
+
+In the setting of the previous lemma, we also obtain the following relation, which will play an important role in later proofs.
+
+\begin{lem}
+Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that 
+$$s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
+\end{lem}
+
+\begin{proof}
+We first show that 
+$$s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$ 
+The result then follows by inverting the relation and conjugating by $s_{j}$. In the following computation, we will underline the terms being manipulated in each line for emphasis.
+
 \begin{align*}
@@
 
-\begin{lem} 
-Let $\Gamma$ be a diagram of finite type containing a 4-cycle as in (R3')(c) of ~\ref{grp def}.
-Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$.
-Then the relations (1) and (2) of (R3')(c) are equivalent.
+\begin{lem} \label{2sqr}
+Let $\Gamma$ be a diagram of finite type containing the following 4-cycle: 
+\begin{tikzpicture}[baseline=-0.5ex]
+\matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|{i}\circ& |[name = ur]|\circ{j}\\
+    %
+    &|[name=dl]|{l} \circ &|[name=dr]| \circ{k} \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ; 
+\end{tikzpicture}
+and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations r(i, j) and r(k, l) are equivalent.
 \end{lem}
@@
 
+As a result of these lemmas, we immediately obtain the following corollary:
+
+\begin{cor}
+Let $\Gamma$ be a diagram of finite type. Then the group A($\Gamma$) defined in the introduction is isomorphic to the group A$_{\Gamma}$
+\end{cor}
+
 Finally, we conclude the section by establishing a relationship between the groups defined by $\Gamma$ and $\Gamma^{op}$, the diagram obtained by reversing all arrows in $\Gamma$.
@@
 \begin{lem}\label{lem:op_homomorphism}
-Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
+Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2) and (R3) in A$_{\Gamma^{op}}$.
 \end{lem}
 \begin{proof}
-One can see that the inverse elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in W$_{\Gamma}$.
-To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
-But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$
-
-For a triangle as in (R3')(b) of ~\ref{grp def}, by the relation r'(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation r'(k, j) in W$_{\Gamma^{op}}$.
-
-Finally, given a square labeled as in (R3')(c) and the relations r'(1, 2) and r'(3, 4), we have 
+One can see that the inverse elements satisfy (R2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$.
+To see that the elements satisfy (R3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3) in A$_{\Gamma}$.
+But then applying relations from (R2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in A$_{\Gamma^{op}}.$
+
+For a triangle labeled as in ~\ref{2tri}, by the relation r(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation r(k, j) in A$_{\Gamma^{op}}$.
+
+Finally, given a square labeled as in ~\ref{2sqr} and the relations r(1, 2) and r(3, 4), we have 
 \begin{align*}
@@
 \end{align*}
-But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy r'(j, i) in W$_{\Gamma^{op}}$. Therefore, we are done.
+But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy r(j, i) in A$_{\Gamma^{op}}$. Therefore, we are done.
 \end{proof}

### 2014-07-20 Paper.tex
Intro and Background edits

@@
 
-In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras.
-This introductory paper focused on structural features of cluster algebras, specifically that, in a given cluster, when any cluster variable is viewed as a rational function in the variables of the given cluster, this cluster variable is a Laurent polynomial.
-\todo{The first sentence seems to be run on, and I'm very confused by it} Fomin and Zelevinsky defined cluster algebras in order to make further strides in the areas of representation theory, Lie theory, and total positivity.
+In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras in order to make further strides in the areas of representation theory, Lie theory, and total positivity.
 Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations.
@@
 \indent Barot and Marsh extended Fomin and Zelevinsky's results in \cite{BM13}, providing a presentation of the reflection group associated to a Dynkin diagram with generators that correspond to elements of a companion basis associated to a seed of a finite-type cluster algebra.
-They also proved that this group presentation is invariant up to isomorphism under the mutation equivalence relation.
-
-\begin{thm}\cite[Theorem 5.4]{BM13}
-\begin{enumerate}
-\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
-\item Let $\mathscr{A}$ be a cluster algebra of finite type.
+They also proved that this group presentation is invariant up to isomorphism under the mutation equivalence relation.That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
+
+%%\begin{thm}\cite[Theorem 5.4]{BM13}
+%\begin{enumerate}
+%\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
+%\item Let $\mathscr{A}$ be a cluster algebra of finite type.
 Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
-\end{enumerate}
+%\end{enumerate}
+%\end{thm}
+
+In our paper, we define $A_{\Gamma}$ to be the Artin group presentation arising from a cluster algebra, where $\Gamma$ is the diagram associated to the cluster algebra.
+We provide the necessary relations for the generators of the group, and show that these relations hold under mutations of chordless cycles in a diagram.
+Our main result is to show that this Artin group presentation is invariant up to isomorphism under the mutation equivalence relation.
+We state the result here, but present the detailed proof in Section \ref{sec:proof_of_main}.
+
+\begin{thm}[Theorem \ref{thm:main}]
+Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$.  Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$.
 \end{thm}
-
-That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
-\\
 
@@
 
-\section{Definitions and Notation}
+\section{Background}
 \label{sec:main_definitions}
@@
 $c+c' =$ max$(a,b)$. 
-Then $\Gamma(B)$ changes in a predetermined way, \todo{Say what this way is?} taking the case $c' = 0$ to mean no arrow between $i$ and $j$.
+Then $\Gamma(B)$ changes as in Figure \ref{mutation}, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.
 \end{itemize}
 \end{prop}
+
+\begin{center}
+\begin{tikzpicture}[baseline=-0.5ex]
+\label{mutation}
+
+	 \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \bullet & &|[name=dr]| \bullet \\
+  };
+\draw[->]
+  (u) to node[right] {b} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{a}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{c}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
+  {
+    && |[name = u]|\bullet& \\
+    %
+    &|[name=dl]| \bullet & &|[name=dr]| \bullet \\
+  };
+\draw[->]
+  (dr)to node[right] {b} (u) 
+  ;
+  \draw[->]
+  (u) to node[left]{a}(dl)
+  ;
+  \draw[->]
+  (dl) to node[below]{c'}(dr)
+  ;
+  \node [yshift = .4 cm] at (u){k};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){i};
+
+   \end{tikzpicture}
+   \end{center}
 
@@
 The rest of the paper will be devoted to building up analogous relations, defined in ~\ref{grp def} to prove a similar result in the case of Artin groups.
+For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
+
+\begin{defn}
+
+The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
+\begin{itemize}
+	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
+	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$
+
+\item[(R3)] For every ordered chordless cycle of the form
+
+\begin{tikzcd}
+i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
+\end{tikzcd}
+
+such that either
+\begin{enumerate}
+	\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
+	\item All edges in the chordless cycle have weight $1.$
+\end{enumerate}
+we include the relation
+\begin{align*}
+	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
+\end{align*}
+where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
+\end{itemize}
+\end{defn}
+
+ We will use these group relations to prove the mutation invariance of $A_{\Gamma}$ in Section \ref{sec:proof_of_main}
 
@@
 Each Artin group has an associated Coxeter Group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type.
-To each Artin group of finite type we can assign it the same dynkin diagram which is assigned to the coxeter group associated to the Artin group.
+To each Artin group of finite type we can assign it the same Dynkin diagram which is assigned to the Coxeter group associated to the Artin group.
 \end{rem}
@@
 
-For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
-The associated Artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
+Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
+The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
 \begin{itemize}
@@
 \begin{rem}
-In the above definition, the chordless cycle is ordered, which means that two cycles are considered different if they are cyclic rotations of eachother.
+In the above definition, the chordless cycle is ordered, which means that two cycles are considered different if they are cyclic rotations of each other.
 \end{rem}
@@
 \begin{rem}
-We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analagous to that of \cite{BM13} at the beginning of Section 3.
-Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13}.
-Namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma,$ then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of section 3 in \cite{BM13}.
+We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3.
+Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of section 3 in \cite{BM13}.
 \end{rem}

### 2014-07-20 Paper.tex
minor abstract adjustments

@@
 Then in 2013, Barot and Marsh defined the presentation of a reflection group associated to a Dynkin diagram in terms of an edge-weighted, oriented graph, and proved that this group is invariant (up to isomorphism) under diagram mutations.
-In this paper, we extend Barot and Marsh's results to Artin group presentations, defining new relations for when the generators are not self-inverses and again showing mutation-invariance for these presentations.
+In this paper, we extend Barot and Marsh's results to Artin group presentations, defining new generator relations and showing mutation-invariance for these presentations.
 \end{abstract}

### 2014-07-21 Paper.tex
small changes

--- 2014-07-20 Paper.tex
@@
 \usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
-\def\ltblue{blue!20!white}
-\def\ltgreen{green!20!white}
+%\def\ltblue{blue!20!white}
+%\def\ltgreen{green!20!white}
 
@@
 \newtheorem{note}[thm]{Notation}
-\newtheorem{ex}[thm]{Example}
 \newtheorem{rem}[thm]{Remark}
@@
 
-\title{Artin Group Presentations Arising from Cluster Algebras}
+\title{Artin Group Presentations of Reflection Groups}
 \author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
@@
 Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556}
-\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
+\email{..., jhaley3@nd.edu, david.hemminger@duke.edu, hpeck@millikin.edu}
 \date{\today}
@@
 \begin{displaymath}
-\label{mij_defn}
 m_{ij} = \begin{cases}    2 & \mbox{if } i \mbox{ and } j \mbox{ are not connected;} \\
@@
 
-In this section, we shall review the structure of diagrams of finite type, and how their cycles are affected by mutation.
-This section is simply a recap of \cite[Section 2]{BM13}.
-First, in Proposition ~\ref{cycle_types}, all types of chordless cycles in diagrams of finite type are classified.
-Second, in Corollary ~\ref{local_three_picture} all possible local pictures between a mutated vertex and two adjacent vertices are drawn.
-Finally, in ~\ref{lem:chordless_cycles}, all chordless cycles introduced from a mutation are drawn.
-These three lemmas will be crucial in proving the main result Theorem ~\ref{thm:main}, as they will allow us to inspect precisely which relations are added and removed after mutating at a prescribed vertex.
+In this section, we shall review the structure of diagrams of finite type, and how their cycles are affected by mutation. This section is simply a recap of \cite[Section 2]{BM13}.
 
@@
 \begin{prop}
-\label{cycle_types}
 Let $\Gamma$ be a diagram of finite type.
@@
 \begin{cor}
-\label{local_three_picture}
 Let $\Gamma$ be the a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$
@@
     \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
   {
@@
     \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){1};
-    \node [yshift = -.9 cm] at (u){$C'$};
    \end{tikzpicture}
@@
     \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
   {
@@
     \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
- 	\node [yshift = -.7 cm,xshift = .7 cm] at (ul){$C'$};
+
    \end{tikzpicture}
@@
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
   {
@@
     \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
- 	\node [yshift = -.95 cm,xshift = .95 cm] at (ul){$C'$};
     \end{tikzpicture}
@@
     \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
- 	\node [yshift = -.95 cm,xshift = .3 	5 cm] at (ul){$C'$};
     \end{tikzpicture}
@@
     \node at (dl.south){$h$};
-
- 	\node [yshift = -.9 cm] at (um){$C'$};
     \end{tikzpicture}
@@
     \node at (dl.south){$h$};
- 	\node [yshift = -.9 cm] at (um){$C'$};
     \matrix[matrix of math nodes,column sep={40pt,between origins},row
@@
 
-\section{The Artin Group of a Diagram}
+\section{The Group of a Diagram in an Artin Group}
 \label{sec:defn_artingroup}
 
-In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin Group associated to a finite type diagram.
-This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
-
-\subsection{Artin Groups}
-
-\begin{note}
-Let 
-\begin{align*}
-	\langle x_i,x_j \rangle ^k = \begin{cases}
-	(x_ix_j)^{\frac{k}{2}}, &\text{ if }k \equiv 0 \pmod 2\\
-	(x_ix_j)^{\frac{k-1}{2}}x_i &\text{ if } k \equiv 1 \pmod 2
-\end{cases}
-\end{align*}
-That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k.$
-
-\end{note}
-\begin{defn}
-For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix which whose entries can take values in the real numbers or infinity, satisfying $m_{i,j} = m_{j,i}$ we define the associated {\it Artin Group} in terms of generators and relations by
-\begin{align*}
-	A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
-\end{align*}
-\end{defn}
-
-\begin{rem}
-Each Artin group has an associated Coxeter Group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type.
-To each Artin group of finite type we can assign it the same dynkin diagram which is assigned to the coxeter group associated to the Artin group.
-\end{rem}
-
-\subsection{The Group associated to Diagram}
-
 \begin{defn} \label{grp def}
-
 For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
-The associated Artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
+The associated artin group $W_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the relations
 \begin{itemize}
-	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
-	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$
-
-\item[(R3)] For every ordered chordless cycle of the form
+	\item[(R2')] For all $i \neq j,$ we add the relations
+	\\
+$	\begin{cases}
+	s_is_j=s_js_i, &\text{ if there is no edge between $i$ and $j$}\\
+	s_is_js_i = s_js_is_j &\text{ if there is an edge of weight 1 between $i$ and $j.$}\\
+	s_is_js_is_j = s_js_is_js_i &\text{ if there is an edge of weight 2 between $i$ and $j$.}\\
+	s_is_js_is_js_is_j = s_js_is_js_is_js_i &\text{ if there is an edge of weight 3 between $i$ and $j$.}
+\end{cases}$
+\item[(R3')(a)] For every chordless cycle of the form
 
@@
 
-such that either
-\begin{enumerate}
-	\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
-	\item All edges in the chordless cycle have weight $1.$
+such that all edges have weight 1, for all $i,$ with $0 \leq a \leq d-1,$ we include the relation 
+\begin{align*}
+	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a}.
+\end{align*}
+Where subscripts are taken $\pmod d.$
+
+\item[(R3')(b)] For every chordless cycle of the form \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    && |[name = u]|\circ& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (u) to node[right] {1} (dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{2}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){i};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){j};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){k};
+   \end{tikzpicture}
+   we include the three relations
+   \begin{enumerate}[(1)]
+\item $s_{i}s_{j}^{-1}s_{k}s_{j} = s_{j}^{-1}s_{k}s_{j}s_{i}$
+\item $s_{k}s_{i}^{-1}s_{j}s_{i} = s_{i}^{-1}s_{j}s_{i}s_{k}$
+\item $s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$
 \end{enumerate}
-we include the relation
-\begin{align*}
-	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
-\end{align*}
-where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
+\item[(R3')(c)] For every chordless cycle of the form
+\begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|\circ & |[name = ur]|\circ\\
+    %
+    &|[name=dl]| \circ &|[name=dr]| \circ \\
+  };
+\draw[->]
+  (ul) to node[above] {1} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{2} (dr)
+  ;
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){i};
+   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){j};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){k};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){l};
+
+   \end{tikzpicture}
+
+   we include the two relations
+   \begin{enumerate}[(1)]
+\item $s_{i}s_{j}^{-1}s_{k}^{-1}s_ls_{k}s_j = s_{j}^{-1}s_{k}^{-1}s_ls_ks_{j}s_{i}$
+\item $s_{k}s_{l}^{-1}s_{i}^{-1}s_js_{i}s_l = s_{l}^{-1}s_{i}^{-1}s_js_is_{l}s_{k}$
+\end{enumerate}
 \end{itemize}
 \end{defn}
-
-\begin{rem}
-In the above definition, the chordless cycle is ordered, which means that two cycles are considered different if they are cyclic rotations of eachother.
-\end{rem}
-
-\begin{rem}
-We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analagous to that of \cite{BM13} at the beginning of Section 3.
-Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13}.
-Namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma,$ then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of section 3 in \cite{BM13}.
-\end{rem}
-
-\begin{rem}
-Throughout the remainder of the paper, we shall frequently discuss relations on one diagram of finite type, $\Gamma,$ and another diagram of finite type $\Gamma^\prime.$ In order to distinguish the relations in these two groups, we shall refer to the relations on $\Gamma$ as $(R2),(R3)$ and the relations on $\Gamma^\prime$ as $(R2^\prime),(R3^\prime).$
-\end{rem}
-
-\begin{ex}
-The relations $(R2),(R3)$ in that $\Gamma$ is a square with all edges of weight 1 are as follows:
-\[\Gamma =\begin{tikzpicture}[baseline=-0.5ex]
- \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
-  {
-    & |[name = ul]|\circ& |[name = ur]|\circ\\
-    %
-    &|[name=dl]| \circ &|[name=dr]| \circ \\
-  };
-\draw
-  (ul) -- node[above] {1} (ur)
-  ;
-  \draw
-  (dl) -- node[left]{1}(ul)
-  ;
-  \draw
-  (dr) -- node[below]{1}(dl)
-  ;
-  \draw
-  (ur) -- node[right]{1} (dr)
-  ;  
-      \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
-   \node  [yshift = .4 cm,xshift = .4 cm] at (ur){2};
-    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){3};
-    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){4};
-   \end{tikzpicture}\]
-   \begin{enumerate}
-	\item[(R2)]
-	\begin{itemize}
-	\item $\langle s_1,s_2 \rangle^3 = \langle s_2,s_21 \rangle^3$
-	\item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3$
-	\item $\langle s_3,s_4 \rangle^3 = \langle s_4,s_3 \rangle^3$
-	\item $\langle s_4,s_1 \rangle^3 = \langle s_1,s_4 \rangle^3$
-\end{itemize} 
-	\item[(R3)]
-	\begin{itemize}
-	\item $s_{1}s_{2}^{-1}s_{3}^{-1}s_4s_{3}s_2 = s_{2}^{-1}s_{3}^{-1}s_4s_3s_{2}s_{1}$
-	\item $s_{2}s_{3}^{-1}s_{4}^{-1}s_1s_{4}s_3 = s_{3}^{-1}s_{4}^{-1}s_1s_4s_{3}s_{2}$
-	\item $s_{3}s_{4}^{-1}s_{1}^{-1}s_2s_{1}s_4 = s_{4}^{-1}s_{1}^{-1}s_2s_1s_{4}s_{3}$
-	\item $s_{4}s_{1}^{-1}s_{2}^{-1}s_3s_{2}s_1 = s_{1}^{-1}s_{2}^{-1}s_3s_2s_{1}s_{4}$
-\end{itemize} 
-\end{enumerate}
-\end{ex}
 
@@
 
-\section{Symmetry among (R3) Relations}
+\section{Symmetry among (R3') Relations}
 \label{sec:one_relation}
 
-Given the relations (R2), many of the relations in (R3) become redundant. For example,
+As in \cite{BM13}, given the relations (R2'), many of the relations in (R3')(a) and (b) become redundant. For example,
 
@@
 \end{equation*}
-
 so that all edges have weight 1.
-Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2) and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3) hold for C.
+Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2') and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3)(a) hold for C.
 \end{lem}
@@
 \begin{proof}
-As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $A_{\Gamma}$ satisfies the relation r(0, 1). Then we have 
+As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
 \begin{align*}
@@
 Furthermore, we obtain similar results for cycles containing edges of weight 2.
-\begin{lem} \label{2tri}
-Let $\Gamma$ be a diagram of finite type containing the following 3-cycle:
-
-\begin{tikzpicture}[baseline=-0.5ex]
-   \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (10,0)
-  {
-    && |[name = u]| {k} \circ& \\
-    %
-    &|[name=dl]|{j} \circ & &|[name=dr]| \circ {i} \\
-  };
-\draw[->]
-  (u) to node[right] {2} (dr)
-  ;
-  \draw[->]
-  (dl) to node[left]{2}(u)
-  ;
-  \draw[->]
-  (dr) to node[below]{1}(dl)
-  ;
-
-   \end{tikzpicture}
-and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations r(i, j) and r(k, i) are equivalent.
+\begin{lem} 
+Let $\Gamma$ be a diagram of finite type containing a 3-cycle as in (R3')(b) of ~\ref{grp def}.
+Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$.
+Then the relations (1) and (2) of (R3')(b) are equivalent, and they together imply the relation (3).
 \end{lem}
@@
 \begin{proof}
-The lemma follows from the fact that
+The equivalence of (1) and (2) follows from the fact that
 \begin{align*}
@@
 \end{align*}
-\end{proof}
-
-In the setting of the previous lemma, we also obtain the following relation, which will play an important role in later proofs.
-
-\begin{lem}
-Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that 
-$$s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
-\end{lem}
-
-\begin{proof}
-We first show that 
-$$s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$ 
-The result then follows by inverting the relation and conjugating by $s_{j}$. In the following computation, we will underline the terms being manipulated in each line for emphasis.
-
+
+In showing that (1) and (2) imply (3), we will underline the terms being manipulated in each line for emphasis.
 \begin{align*}
@@
 
-\begin{lem} \label{2sqr}
-Let $\Gamma$ be a diagram of finite type containing the following 4-cycle: 
-\begin{tikzpicture}[baseline=-0.5ex]
-\matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
-  {
-    & |[name = ul]|{i}\circ& |[name = ur]|\circ{j}\\
-    %
-    &|[name=dl]|{l} \circ &|[name=dr]| \circ{k} \\
-  };
-\draw[->]
-  (ul) to node[above] {1} (ur)
-  ;
-  \draw[->]
-  (dl) to node[left]{2}(ul)
-  ;
-  \draw[->]
-  (dr) to node[below]{1}(dl)
-  ;
-  \draw[->]
-  (ur) to node[right]{2} (dr)
-  ; 
-\end{tikzpicture}
-and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations r(i, j) and r(k, l) are equivalent.
+\begin{lem} 
+Let $\Gamma$ be a diagram of finite type containing a 4-cycle as in (R3')(c) of ~\ref{grp def}.
+Let W be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$.
+Then the relations (1) and (2) of (R3')(c) are equivalent.
 \end{lem}
@@
 
-As a result of these lemmas, we immediately obtain the following corollary:
-
-\begin{cor}
-Let $\Gamma$ be a diagram of finite type. Then the group A($\Gamma$) defined in the introduction is isomorphic to the group A$_{\Gamma}$
-\end{cor}
-
 Finally, we conclude the section by establishing a relationship between the groups defined by $\Gamma$ and $\Gamma^{op}$, the diagram obtained by reversing all arrows in $\Gamma$.
@@
 \begin{lem}\label{lem:op_homomorphism}
-Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2) and (R3) in A$_{\Gamma^{op}}$.
+Let W$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2') and (R3') in W$_{\Gamma^{op}}$.
 \end{lem}
 \begin{proof}
-One can see that the inverse elements satisfy (R2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$.
-To see that the elements satisfy (R3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3) in A$_{\Gamma}$.
-But then applying relations from (R2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in A$_{\Gamma^{op}}.$
-
-For a triangle labeled as in ~\ref{2tri}, by the relation r(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation r(k, j) in A$_{\Gamma^{op}}$.
-
-Finally, given a square labeled as in ~\ref{2sqr} and the relations r(1, 2) and r(3, 4), we have 
+One can see that the inverse elements satisfy (R2') in W$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in W$_{\Gamma}$.
+To see that the elements satisfy (R3') in W$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3') in W$_{\Gamma}$.
+But then applying relations from (R2'), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle in chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r'(0, d-1) in W$_{\Gamma^{op}}.$
+
+For a triangle as in (R3')(b) of ~\ref{grp def}, by the relation r'(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation r'(k, j) in W$_{\Gamma^{op}}$.
+
+Finally, given a square labeled as in (R3')(c) and the relations r'(1, 2) and r'(3, 4), we have 
 \begin{align*}
@@
 \end{align*}
-But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy r(j, i) in A$_{\Gamma^{op}}$. Therefore, we are done.
+But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy r'(j, i) in W$_{\Gamma^{op}}$. Therefore, we are done.
 \end{proof}

### 2014-07-21 Paper.tex
improved section 6 and small changes

--- 2014-07-20 Paper.tex
@@
 \usepackage{latexsym,amscd,epsfig,verbatim}
-\usepackage[margin=1in,letterpaper,portrait]{geometry}
+%\usepackage[margin=1in,letterpaper,portrait]{geometry}
 
@@
 \newtheorem{rem}[thm]{Remark}
-\newcommand\fri{s_4^{-1}}
-\newcommand\fr{s_4}
-\newcommand\tri{s_3^{-1}}
-\newcommand\tr{s_3}
-\newcommand\twi{s_2^{-1}}
-\newcommand\tw{s_2}
-\newcommand\oni{s_1^{-1}}
-\newcommand\on{s_1}
+%\newcommand\fri{s_4^{-1}}
+%\newcommand\fr{s_4}
+%\newcommand\tri{s_3^{-1}}
+%\newcommand\tr{s_3}
+%\newcommand\twi{s_2^{-1}}
+%\newcommand\tw{s_2}
+%\newcommand\oni{s_1^{-1}}
+%\newcommand\on{s_1}
 \newcommand\V{V(\Gamma)}
@@
 \label{local_three_picture}
-Let $\Gamma$ be the a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$
+Let $\Gamma$ be a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$
 
@@
 
-In this section we prove our main result:
+\noindent In this section we prove our main result:
 
 \begin{thm}\label{thm:main}
-Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$.
-Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$\todo{we should pick notation for this}.
+Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$.  Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$
 \end{thm}
@@
 Throughout this section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.
-To help us define an isomorphism from $A_{\Gamma}$ to $A_{\Gamma^{\prime}}$ we define an element $t_i\in A_{\Gamma}$ for each vertex $i\in \Gamma$ by
-
+We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively.
+We will also abuse notation and write $u_i$ for the generators of $A_{\left(\Gamma^{op}\right)^\prime}$ as well, making use of the fact that $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.
+
+In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, whose proof we will defer until after the proof of Theorem \ref{thm:main} and then split into Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.
+
+\begin{prop}\label{prop:ti_relations}
+The map $\varphi \colon A_{\Gamma^\prime}\rightarrow A_{\Gamma}$ defined by
 \begin{displaymath}
-t_i = \begin{cases}    s_ks_is_k^{-1} & \mbox{if there is a (possibly weighted) arrow } i \rightarrow k \mbox{ in } \Gamma\\
+\varphi(r_i) = \begin{cases}    s_ks_is_k^{-1} & \mbox{if there is a (possibly weighted) arrow } i \rightarrow k \mbox{ in } \Gamma\\
 				s_i & \mbox{otherwise}\\
@@
 
-In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, whose proof we will defer until after the proof of Theorem \ref{thm:main}.
-
-\begin{prop}\label{prop:ti_relations}
-The elements $t_i$, for $i$ a vertex of $\Gamma$, satisfy the relations $(R2)^{\prime}$ and $(R3)^{\prime}$ associated to $\Gamma^{\prime}$.
+\noindent is a group homomorphism.
 \end{prop}
-\todo{This propositions seems to be worded confusingly.
-I see this is what they say in Barot and Marsh, but I still find it confusing.
-Maybe it's clearer to say that if we take $p_i$ to be the generators of $\Gamma',$ and they satisfy a relation $r(p_1,\ldots, p_{|\Gamma|}) = e,$ if and only if $t_i$ satisfy the same relation $r(t_1,\ldots, t_{|\Gamma|}) = e.$}
-\todo{Maybe it would make more sense to break this up into 2 lemmas, like Barot and Marsh do}
+
+\todo{do we define $m_{ij}'$ somewhere?}
 
 \begin{proof}[Proof of Theorem \ref{thm:main}]
-Define a homomorphism $\varphi\colon A(\Gamma^{\prime}) \rightarrow A(\Gamma)$ by sending each generator $s_i\in A(\Gamma^{\prime})$ to $t_i\in A(\Gamma)$.
-\todo{Weren't the $t_i$ defined in terms of the $s_i$ for $A(\Gamma)$?
-It seems like there are two different $s_i,$ one for $\Gamma$ and one for $\Gamma'$ and this is confusing me.}  This gives a well-defined homomorphism by Proposition \ref{prop:ti_relations}.
-By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta\colon A(\Gamma) \rightarrow A(\Gamma^{op})$ that sends $s_i\in A(\Gamma)$ to $s_i^{-1}$ in $A(\Gamma^{op})$ is well-defined.
-Define a homomorphism
+By Proposition \ref{prop:ti_relations} $\varphi\colon A_{\Gamma^\prime}\rightarrow A_\Gamma$ is a group homomorphism.
+We also abuse notation and write $\varphi\colon A_{\Gamma^{op}}\rightarrow A_{\left(\Gamma^{op}\right)^\prime}$ by letting $\varphi(q_i)$ equal $u_ku_iu_k^{-1}$ if there is an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^\prime$, and $u_i$ otherwise, and this is a homomorphism by Proposition \ref{prop:ti_relations} as well.
+By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta$ that sends $s_i\in A(\Gamma)$ to $q_i^{-1}\in A(\Gamma^{op})$ and $u_i\in A_{\left(\Gamma^\prime\right)^{op}}$ to $r_i\in A_{\Gamma^\prime}$ is well-defined.
+We then have a homomorphism
 $$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
-\todo{It seems like there is an abuse of notation here.
-You have defined $\phi:A(\Gamma') \rightarrow A(\Gamma),$ but it looks like it is mapping $A(\Gamma^{op} \rightarrow A((\Gamma^{op})')$ here.
-Please make clearer what this map $\phi$ is.}
-Note that here we use the facts that $\left(\Gamma^{op}\right)^{op} = \Gamma$ and $\left(\Gamma^{op}\right)^{\prime} = \left(\Gamma^{\prime}\right)^{op}$.
+
 Suppose that there is an arrow $i\rightarrow k$ in $\Gamma$.
@@
 
-$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(s_k^{-1}s_i^{-1}s_k)) = \Delta(s_i^{-1}) = s_i$$
-\todo{I think you have the right idea, but I don't understand how you always have elements in $A(\Gamma)$ and never elements in $A(\Gamma').$ I think the problem lies in the definition of $\phi.$}
+$$\psi\circ\varphi(r_i) = \Delta(\varphi(\Delta(\varphi(r_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(q_k^{-1}q_i^{-1}q_k)) = \Delta(u_i^{-1}) = r_i$$
+
 Similarly if there is an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\Gamma$ then there will be an arrow $k\rightarrow i$ or no arrow between $i$ and $k$ in $\left(\Gamma^{op}\right)^{\prime}$, respectively.
@@
 
-$$\psi\circ\varphi(s_i) = \Delta(\varphi(\Delta(\varphi(s_i)))) = \Delta(\varphi(\Delta(s_i))) = \Delta(\varphi(s_i^{-1})) = \Delta(s_i^{-1}) = s_i$$
+$$\psi\circ\varphi(r_i) = \Delta(\varphi(\Delta(\varphi(r_i)))) = \Delta(\varphi(\Delta(s_i))) = \Delta(\varphi(q_i^{-1})) = \Delta(u_i^{-1}) = r_i$$
 
@@
 
-\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
-First we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when $i=k$ or $j=k$.
-Without loss of generality suppose that $i=k$.
+We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(R2^\prime)$ and $(R3^\prime)$ relations in $A_{\Gamma^\prime}$.
+Proofs that the $t_i$ satisfy these relations are divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.
+Throughout the proofs we write $t_i = \varphi(r_i)$ for convenience.
+
+\begin{lem}\label{lem:r2a_relations}
+Let $i,j$ be distinct vertices of $\Gamma$.
+\begin{enumerate}[(a)]
+\item If $i=k$ or $j=k$, then $\langle t_it_j \rangle^k = e$.
+\item If at most of $i,j$ is connected to $k$ in $\Gamma$, then $\langle t_it_j \rangle^k = e$.
+\end{enumerate}
+\end{lem}
+
+\begin{proof}
+For case $(a)$, suppose without loss of generality that $i=k$.
 Note that $m_{ij}^\prime = m_{ij}$.
 The only nontrivial case is when there is an arrow $j\rightarrow k =i$.
-\todo{Isn't there also the case of an arrow from k to j?
-Obviously it's symmetric, but isn't it worth saying?}  Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.
-Suppose $m_{ij} = 3$.
-Then $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, and we have
+Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.
+
+\vskip.1in
+\noindent
+{\sf Case $m_{ij} = 3$}.
+Here we have $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, so
 
@@
 
-\noindent If $m_{ij} = 4$, then $s_is_js_is_j = s_js_is_js_i$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore
-
-$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$
-
-\todo{An extra step inserting and removing inverses here would be helpful.}
-
-\noindent If $m_{ij} = 6$, then $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$, so
+\vskip.1in
+\noindent
+{\sf Case $m_{ij} = 4$}.  Here we have $s_is_js_is_j = s_js_is_js_i$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore
+
+$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_is_js_is_js_i^{-1} = s_is_js_is_j = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$
+
+\vskip.1in
+\noindent
+{\sf Case $m_{ij} = 6$}.  Here we have $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$.  As in the previous case, we add an remove pairs $s_is_i^{-1}$ as necessary, giving
 
 $$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$
-\todo{An extra step inserting and removing inverses here would be helpful, as above}
-
-\todo{Instead of saying If mij = 3, try \vskip.1in
-\noindent
-{\sf The case $m_{ij} = 3$}}
-
-Next we check the $(R2)'$ relation for $t_i$ and $t_j$ in the case when at most one of $i$ and $j$ is connected to $k$.
-The only nontrivial case is when there is an arrow $i\rightarrow k$ or $j\rightarrow k$.
+
+For case $(b)$, the only nontrivial case is when there is an arrow $i\rightarrow k$ or $j\rightarrow k$.
 Without loss of generality, suppose there is an arrow $i\rightarrow k$.
 Since $j$ is not connected to $k$, we know that $s_js_k = s_ks_j$.
-Suppose $m_{ij} = 2$.
-\todo{It seems like the previous two sentences should be switched?
-Again try using cases to break it up more clearly for the reader, as I mentioned in a previous todo.} Then $s_is_j = s_js_i$, so we have that
+
+\vskip.1in
+\noindent
+{\sf Case $m_{ij} = 2$}.  Here $s_is_j = s_js_i$, so we have that
 
 $$t_it_j = s_ks_is_k^{-1}s_j = s_js_ks_is_k^{-1} = t_jt_i$$
-\todo{It looks like you're also using here that $s_j$ commutes with $s_k^{-1}.$ I agree it's obvious, but maybe it's worth spelling out}
-
-\noindent If $m_{ij} = 3$, then $s_is_js_i = s_js_is_j$, so we have that
+
+\vskip.1in
+\noindent
+{\sf Case $m_{ij} = 3$}.  Here $s_is_js_i = s_js_is_j$, so we have that
 
@@
 
-\noindent If $m_{ij} = 4$, then $s_is_js_is_j = s_js_is_js_i$, so we have that
-
-$$t_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = s_js_is_js_i$$
-
-\noindent Finally if $m_{ij} = 6$, then $s_is_js_is_js_is_j = s_js_is_js_is_js_i$, so we have that
+\vskip.1in
+\noindent
+{\sf Case $m_{ij} = 4$}.  Here $s_is_js_is_j = s_js_is_js_i$, so we have that
+
+$$t_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = t_jt_it_jt_i$$
+
+\vskip.1in
+\noindent
+{\sf Case $m_{ij} = 6$}.  Here $s_is_js_is_js_is_j = s_js_is_js_is_js_i$, so we have that
 
@@
 
-The remaining $(R2)'$ relations that need to be check are the relations for $t_i$ and $t_j$ when both $i$ and $j$ are connected to $k$.
-The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in \todo{where are they enumerated?}.
+\end{proof}
+
+\begin{lem}\label{lem:r2b_relations}
+Let $i,j$ be distinct vertices of $\Gamma$ such that $i$ and $j$ are connected.  Then $\langle t_it_j \rangle^k = e$.
+\end{lem}
+
+\begin{proof}
+The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.
 We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.
 We also check that the corresponding $(R3^\prime)$ relations hold in cases (b), (d), (e), and (f).
+Within each case we view the subdiagram on the left as a subdiagram of $\Gamma$ in the subcase $(i)$ and as a subdiagram of $\Gamma^\prime$ in the subcase $(ii)$.\todo{Disaster.
+Open to suggestions for how to make this more clear}
+
+Throughout the proof we will make frequent use of the fact that if $m$ and $n$ are vertices of $\Gamma$, then
+
+$$s_ms_ns_m = s_ns_ms_n \Leftrightarrow s_ms_ns_m^{-1} = s_n^{-1}s_ms_n \Leftrightarrow s_ms_n^{-1}s_m^{-1} = s_n^{-1}s_m^{-1}s_n \Leftrightarrow s_m^{-1}s_n^{-1}s_m^{-1} = s_n^{-1}s_m^{-1}s_n^{-1}$$
+
+When helpful, we underline the sections of an expression that are about to be manipulated.
+We also frequently combine two applications of $A_{\Gamma}$ relations when one manipulation is simply commuting pairs of variables.
 
@@
 \begin{enumerate}[i)]
-\item $$t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$$
-\item $$t_it_j = s_is_j = s_js_i = t_jt_i$$
+\item We have $t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$.
+\item We have $t_it_j = s_is_j = s_js_i = t_jt_i$.
 \end{enumerate}
@@
 \begin{enumerate}[i)]
-\item
-\begin{align*}
-t_it_jt_i &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}\\
-&= s_ks_is_js_ks_j^{-1}s_is_k^{-1}\\
-&= s_ks_js_is_ks_is_j^{-1}s_k^{-1}\\
-&= s_ks_js_ks_is_ks_j^{-1}s_k^{-1}\\
-&= s_js_ks_js_is_j^{-1}s_k^{-1}s_j\\
+\item We have
+\begin{align*}
+t_it_jt_i &= s_ks_i\underline{s_k^{-1}s_js_k}s_is_k^{-1}\\
+&= s_k\underline{s_is_j}s_k\underline{s_j^{-1}s_i}s_k^{-1}\\
+&= s_ks_j\underline{s_is_ks_i}s_j^{-1}s_k^{-1}\\
+&= \underline{s_ks_js_k}s_i\underline{s_ks_j^{-1}s_k^{-1}}\\
+&= s_js_k\underline{s_js_is_j^{-1}}s_k^{-1}s_j\\
 &= s_js_ks_is_k^{-1}s_j\\
@@
 
-\begin{align*}
-t_jt_k^{-1}t_it_k &= s_js_k^{-1}s_ks_is_k^{-1}s_k\\
-&= s_js_i\\
-&= s_is_j\\
-&= t_k^{-1}t_it_kt_j\\
-\end{align*}
-
-\item $$t_it_j = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = t_jt_i$$
+\item We have $t_it_j = s_i\underline{s_ks_js_k^{-1}} = \underline{s_is_j^{-1}s_ks_j} = \underline{s_j^{-1}s_ks_j}s_i = s_ks_js_k^{-1}s_i = t_jt_i$
 \end{enumerate}
@@
 \begin{enumerate}[i)]
-\item $$t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$$
-\item $$t_it_j = s_is_j = s_js_i = t_jt_i$$
+\item We have $t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$
+\item We have $t_it_j = s_is_j = s_js_i = t_jt_i$
 \end{enumerate}
@@
 \begin{enumerate}[i)]
-\item
-\begin{align*}
-t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}\\
-&=s_ks_is_k^{-1}s_js_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
-&=s_ks_is_k^{-1}s_ks_js_ks_is_ks_i^{-1}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
-&=s_ks_js_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}\\
+\item We have
+\begin{align*}
+t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_i\underline{s_k^{-1}s_js_k}s_i^{-1}\underline{s_k^{-1}s_j^{-1}s_k}s_i^{-1}s_k^{-1}s_j^{-1}\\
+&=s_ks_is_k^{-1}\underline{s_js_ks_is_j}s_k\underline{s_j^{-1}s_i^{-1}s_j}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
+&=s_k\underline{s_is_k^{-1}s_ks_j}s_ks_is_ks_i^{-1}s_k^{-1}\underline{s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}}\\
+&=s_ks_j\underline{s_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}}s_j^{-1}s_k^{-1}\\
 &= e
@@
 
-We also have
-$$t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_is_j = t_k^{-1}t_it_kt_j$$
-
-\item
-\begin{align*}
-t_it_j &= s_is_ks_js_k^{-1}\\
-&= s_is_j^{-1}s_ks_j\\
-&= s_j^{-1}s_ks_js_i\\
-&= s_ks_js_k^{-1}s_i\\
-&= t_jt_i
-\end{align*}
+\item We have $t_it_j = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = t_jt_i$
 \end{enumerate}
@@
 \begin{enumerate}[i)]
-\item
-\begin{align*}
-t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}\\
-&= s_i^{-1}s_ks_is_js_i^{-1}s_ks_is_js_i^{-1}s_k^{-1}s_is_j^{-1}s_i^{-1}s_k^{-1}s_is_j^{-1}\\
-&= s_i^{-1}s_ks_js_ks_js_k^{-1}s_j^{-1}s_k^{-1}s_j^{-1}s_i\\
+\item We have
+\begin{align*}
+t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= \underline{s_ks_is_k^{-1}}s_j\underline{s_ks_is_k^{-1}}s_j\underline{s_ks_i^{-1}s_k^{-1}}s_j^{-1}\underline{s_ks_i^{-1}s_k^{-1}}s_j^{-1}\\
+&= s_i^{-1}s_k\underline{s_is_js_i^{-1}}s_k\underline{s_is_js_i^{-1}}s_k^{-1}\underline{s_is_j^{-1}s_i^{-1}}s_k^{-1}\underline{s_is_j^{-1}}\\
+&= s_i^{-1}\underline{s_ks_js_ks_js_k^{-1}s_j^{-1}s_k^{-1}s_j^{-1}}s_i\\
 &= e
 \end{align*}
-We also have
-$$ t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_it_j$$
-
-\item
-\begin{align*}
-s_k^{-1}t_it_jt_i^{-1}t_j^{-1}s_k &= s_k^{-1}s_is_ks_js_k^{-1}s_i^{-1}s_ks_j^{-1}\\
-&= s_is_ks_i^{-1}s_js_is_k^{-1}s_i^{-1}s_j^{-1}\\
+
+\item Since $s_js_k^{-1}s_is_k = s_k^{-1}s_is_ks_j$, we have that $s_js_k^{-1}s_i^{-1}s_k = s_k^{-1}s_i^{-1}s_ks_j$, hence
+
+$$t_it_jt_i^{-1}t_j^{-1} = s_is_k\underline{s_js_k^{-1}s_i^{-1}s_k}s_j^{-1}s_k^{-1} = s_is_ks_k^{-1}s_i^{-1}s_ks_js_j^{-1}s_k^{-1} = e$$
+
+\end{enumerate}
+\item
+\begin{enumerate}[i)]
+\item We have that \todo{refer to lemma}
+\begin{align*}
+s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1}s_k &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
 &= e
@@
 
+\item This follows from part (i) by symmetry
 \end{enumerate}
-\item
-\begin{enumerate}[i)]
-\item
-\begin{align*}
-s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1} &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
-&= e
-\end{align*}
-
+\end{enumerate}
+\end{proof}
+
+\begin{lem}\label{lem:r3_relations}
+The elements $t_i$ satisfy the $(R3^\prime)$ relations in $\Gamma^\prime$.
+\end{lem}
+
+\begin{proof}
+We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that the corresponding cycle relations hold in each case.
+By Lemmas \todo{add relevant lemma references}, we will only need one relation for each cycle, as this relation holding will imply that the others hold as well.
+
+\begin{enumerate}[a)]
+\item We have $t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_k^{-1}t_it_kt_j$
+
+\item We have $t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_is_j = t_k^{-1}t_it_kt_j$
+
+\item We have $ t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_it_j$
+
+\item We have that
 \begin{align*}
@@
 
-\item This follows from part (i) by symmetry
-\end{enumerate}
-\end{enumerate}
-
-Next we check that the $t_i$ satisfy the (R3) relations defined by the chordless cycles in $\Gamma'$.
-We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that the corresponding cycle relations hold in each case.
-By Lemmas \todo{add relevant lemma references}, we will only need one relation for each cycle, as this relation holding will imply that the others hold as well.
-Note that we have already checked cases (a)-(d) above, so we only need to check cases (e)-(l).
-
-\begin{enumerate}[a)]
-\setcounter{enumi}{4}
 \item
@@
 \begin{align*}
-t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2 &= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
+& t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
+&= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
 &= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
@@
 \end{align*}
-
 \end{enumerate}
@@
 
+\begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
+Lemma \ref{lem:r2a_relations} and Lemma \ref{lem:r2b_relations} show that the elements $t_i$ satisfy the $(R2^\prime)$ relations for $A_{\Gamma^\prime}$.
+Lemma \ref{lem:r3_relations} shows that they satisfy the $(R3^\prime)$ relations.
+Since these are all of the relations defining $A_{\Gamma^\prime}$, it follows that $\varphi$ defines a group homomorphism $A_{\Gamma^\prime}\rightarrow A_\Gamma$.
+\end{proof}
+
 \bibliography{References}

### 2014-07-22 Paper.tex
More Section 5 Changes
improved section 6

@@
 
+\todo[inline]{directions of arrows within squares?}
 \begin{lem}\label{lem:chordless_cycles}
@@
 
-\begin{lem}
+\begin{lem}\label{lem:extra_square_relation}
 Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that 
@@
 \begin{lem}\label{lem:op_homomorphism}
-Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2) and (R3) in A$_{\Gamma^{op}}$.
+Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$.
+Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2) and (R3) in A$_{\Gamma^{op}}$.
+In particular, A$_{\Gamma}$ $\cong$ A$_{\Gamma^{op}}$.
 \end{lem}
@@
 \begin{enumerate}[i)]
-\item We have that \todo{refer to lemma}
+\item We have that
 \begin{align*}
@@
 \end{align*}
+
+Where the second equality follows from Lemma \ref{lem:extra_square_relation}.
 
@@
 \begin{proof}
-We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that the corresponding cycle relations hold in each case.
-By Lemmas \todo{add relevant lemma references}, we will only need one relation for each cycle, as this relation holding will imply that the others hold as well.
+We know that every chordless cycle in $\Gamma'$ arises from a subdiagram of $\Gamma$ in the form of one of the cases of Lemma \ref{lem:chordless_cycles}, so we simply need to check that a cycle relation holds in each case.
+We follow the labeling of the vertices used in Lemma \ref{lem:chordless_cycles}.
 
 \begin{enumerate}[a)]
-\item We have $t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_k^{-1}t_it_kt_j$
-
-\item We have $t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_is_j = t_k^{-1}t_it_kt_j$
-
-\item We have $ t_jt_k^{-1}t_it_k = s_js_k^{-1}s_ks_is_k^{-1}s_k = s_js_i = s_is_j = t_it_j$
-
-\item We have that
-\begin{align*}
-t_it_j^{-1}t_kt_jt_i^{-1}t_j^{-1}s_k^{-1}t_j &= s_ks_is_k^{-1}s_j^{-1}s_ks_js_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
-&= s_ks_is_js_ks_j^{-1}s_k^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
-&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}s_k^{-1}s_j\\
-&= s_ks_is_js_ks_j^{-1}s_i^{-1}s_js_k^{-1}s_j^{-1}s_k^{-1}\\
-&= s_ks_js_ks_j^{-1}s_is_i^{-1}s_js_k^{-1}s_j^{-1}s_k\\
+\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$
+
+\item We have $ t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_3t_1$
+
+\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_3s_1 = t_2^{-1}t_3t_2t_1$
+
+\item We have
+\begin{align*}
+t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1 &= s_2s_3s_2^{-1}s_1^{-1}s_2s_1s_2s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
+&= s_2s_3s_1s_2s_1^{-1}s_2^{-1}s_2s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
+&= s_2s_3s_1s_2s_1^{-1}s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
+&= s_2s_3s_1s_2s_1^{-1}s_3^{-1}s_1s_2^{-1}s_1^{-1}s_2^{-1}\\
+&= s_2s_1s_2s_1^{-1}s_3s_3^{-1}s_1s_2^{-1}s_1^{-1}s_2\\
 &= e\\
@@
 
-\item
-Without loss of generality we label the vertices as follows:\todo{insert diagrams}
-
+\item We have
 \begin{align*}
@@
 
-\item
-\begin{align*}
-t_4^{-1}t_1^{-1}t_2^{-1}t_3t_2t_1 &= s_4\underline{s_1^{-1}s_1}s_2^{-1}\underline{s_1^{-1}s_3s_1}s_2 \underline{s_1^{-1}s_1}\\
-&= s_4s_2^{-1}s_3s_2\\
-&= s_2^{-1}s_3s_2s_4\\
-&= (s_1^{-1}s_1)s_2^{-1}(s_1^{-1}\underline{s_1)s_3(s_1^{-1}}s_1)s_2(s_1^{-1}s_1s_4\\
-&= s_1^{-1}1s_2^{-1}s_1^{-1}s_3s_1s_2s_1^{-1}s_1s_4\\
-&= t_1^{-1}t_1^{-1}t_3t_2t_1t_4\\
-\end{align*}
-
-\item
+\item We have
+\begin{align*}
+t_1t_2^{-1}t_3^{-1}t_4t_3t_2 &= s_1\underline{s_2^{-1}s_2}s_3^{-1}\underline{s_2^{-1}s_4s_2}s_3 \underline{s_2^{-1}s_2}\\
+&= s_1s_3^{-1}s_4s_3\\
+&= s_3^{-1}s_4s_3s_1\\
+&= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
+&= s_2^{-1}2s_3^{-1}s_2^{-1}s_4s_2s_3s_2^{-1}s_2s_1\\
+&= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
+\end{align*}
+
+\item We have
 \begin{align*}
@@
 
-\item
-\begin{align*}
-t_2t_3^{-1}t_4t_3 &= s_2s_3^{-1}\underline{s_1s_4s_1^{-1}}s_3\\
-&= s_2s_3^{-1}s_4^{-1}s_1s_4s_3\\
-&= s_3^{-1}\underline{s_4^{-1}s_1s_4}s_3s_2\\
-&= s_3^{-1}s_1s_4s_1^{-1}s_3s_2\\
-&= t_3^{-1}t_4t_3t_2\\
-\end{align*}
-
-\item
+\item We have
+\begin{align*}
+t_3t_4^{-1}t_1t_4 &= s_3s_4^{-1}\underline{s_2s_1s_2^{-1}}s_4\\
+&= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
+&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3\\
+&= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
+&= t_4^{-1}t_1t_4t_3\\
+\end{align*}
+
+\item We have
 \begin{align*}
@@
 
-\item
+\item We have
 \begin{align*}

### 2014-07-24 Paper.tex
added some of emily's comments to aarons section

@@
 \begin{defn}
-
 The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
@@
 \label{cycle_types}
-Let $\Gamma$ be a diagram of finite type.
+\cite[Proposition 2.1]{BM13} Let $\Gamma$ be a diagram of finite type.
 Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$.
-Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a triangle with two edges of weight 2 and one of weight 1, or a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below.
+Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below, or a triangle with two edges of weight 2 and one of weight 1.
 
@@
 \end{prop}
-\begin{proof}
-See \cite[Proposition 2.1]{BM13}.
-\end{proof}
 
@@
 \label{local_three_picture}
-Let $\Gamma$ be a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$
+\cite[Corollary 2.3]{BM13} Let $\Gamma$ be a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$
 
@@
 \end{cor}
-\begin{proof}
-See \cite[Corollary 2.3]{BM13}.
-\end{proof}
 
@@
 
-In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin Group associated to a finite type diagram.
+In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin group associated to a finite type diagram.
 This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
@@
 \begin{defn}
-For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix which whose entries can take values in the real numbers or infinity, satisfying $m_{i,j} = m_{j,i}$ we define the associated {\it Artin Group} in terms of generators and relations by
+\cite[Beginning of section 1.2]{artin} \todo{put reference for artin, found at the bottom, in bibliography, but I don't know how to use this bibliography format.}
+For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
 \begin{align*}
@@
 \begin{rem}
-Each Artin group has an associated Coxeter Group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type.
+Each Artin group has an associated Coxeter group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type.
 To each Artin group of finite type we can assign it the same Dynkin diagram which is assigned to the Coxeter group associated to the Artin group.
@@
 
-Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
+Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin group as follows.
 The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
@@
 
-\item[(R3)] For every ordered chordless cycle of the form
-
-\begin{tikzcd}
-i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
-\end{tikzcd}
-
-such that either
+\item[(R3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally,
 \begin{enumerate}
@@
 \begin{rem}
-In the above definition, the chordless cycle is ordered, which means that two cycles are considered different if they are cyclic rotations of each other.
+In the above definition, the tuple cycle is ordered, and so we may have multiple relations corresponding to the same set $\{i_0,\ldots, i_{d-1}\},$ corresponding to cyclic rotations of the tuple $(i_0,\ldots, i_{d-1}).$ However, we shall see in Section ~\ref{sec:one_relation} that many of these relations are redundant.
 \end{rem}
@@
 We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3.
-Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of section 3 in \cite{BM13}.
+Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of rem 3 in \cite{BM13}.
 \end{rem}
@@
 Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that Dynkin diagram.
-This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin Group.
+This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin group.
 \end{rem}
@@
 
+artin: http://people.brandeis.edu/~charney/papers/RAAGfinal.pdf
+
 \end{document}

### 2014-07-29 Paper.tex
emily edits to section 1/2

@@
 \begin{abstract}
-In 2003, Fomin and Zelevinsky proved that finite-type cluster algebras can be classified by Dynkin diagrams.
+In 2003, Fomin and Zelevinsky proved that finite type cluster algebras can be classified by Dynkin diagrams.
 Then in 2013, Barot and Marsh defined the presentation of a reflection group associated to a Dynkin diagram in terms of an edge-weighted, oriented graph, and proved that this group is invariant (up to isomorphism) under diagram mutations.
@@
 Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations.
-Of particular interest were \textit{finite-type} cluster algebras, that is, cluster algebras whose variables are generated through mutation on a finite number of \textit{seeds}.
+Of particular interest were \textit{finite type} cluster algebras, that is, cluster algebras whose variables are generated through mutation on a finite number of \textit{seeds}.
 In the sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3.
-In particular, this proves that finite-type cluster algebras can be classified by Dynkin diagrams.
+In particular, this proves that finite type cluster algebras can be classified by Dynkin diagrams.
 \\
-\indent Barot and Marsh extended Fomin and Zelevinsky's results in \cite{BM13}, providing a presentation of the reflection group associated to a Dynkin diagram with generators that correspond to elements of a companion basis associated to a seed of a finite-type cluster algebra.
+\indent Barot and Marsh extended Fomin and Zelevinsky's results in \cite{BM13}, providing a presentation of the reflection group associated to a Dynkin diagram with generators that correspond to elements of a companion basis associated to a seed of a finite type cluster algebra.
 They also proved that this group presentation is invariant up to isomorphism under the mutation equivalence relation.That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
@@
 \end{displaymath}
-and $\textbf{x}^{\prime} = {x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n}$. 
-Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = {x_1, \ldots, x_n}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables.
+and $\textbf{x}^{\prime} = \left{ x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n \right}$. 
+Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = \left{ x_1, \ldots, x_n \right}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables.
 \\
@@
 The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge.
-A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in {1, \ldots, n}$.
+A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in \left{ 1, \ldots, n \right}$.
 By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically.
@@
 \begin{itemize}
-\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
+\item Reverse the orientations of all edges in $\Gamma(B)$ incident to $k$ (leaving the weights unchanged)
 \item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e.
@@
 \item $(s_is_j)^{m_{ij}} = e$ for all $i \neq j$;
-\item For any chordless cycle $C$ in $\Gamma$, where
+\item For any chordless cycle (as defined in Definition \ref{chordlesscycle} $C$ in $\Gamma$, where
 \begin{displaymath}
-C = i_0 \rightarrow i_1 \rightarrow \cdots \rightarrow i_{d-1} \rightarrow i_0
+C = i_0 \xrightarrow{w_1} i_1 \xrightarrow{w_2} \cdots \xrightarrow{w_{d-1}} i_{d-1} \xrightarrow{w_0} i_0
 \end{displaymath}
@@
 \end{displaymath}
-\todo{Maybe it's worth presenting definition 2.4 before this, and then saying it is equivalent to removing certain the (R3)(b) relations.
+%\todo{Maybe it's worth presenting definition 2.4 before this, and then saying it is equivalent to removing certain the (R3)(b) relations.
 Don't they actually present the definition you refer to in Definition 2.4 as the presentation?
@@
 The rest of the paper will be devoted to building up analogous relations, defined in ~\ref{grp def} to prove a similar result in the case of Artin groups.
-For $\Gamma$ a diagram of finite type, we define the associated Artin Group as follows.
-
-\begin{defn}
-The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
-\begin{itemize}
-	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
-	$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$
-
-\item[(R3)] For every ordered chordless cycle of the form
-
-\begin{tikzcd}
-i_0 \arrow{r} & i_1 \arrow{r} & \cdots \arrow{r} & i_{d-1} \arrow{r} & i_0
-\end{tikzcd}
-
-such that either
-\begin{enumerate}
-	\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
-	\item All edges in the chordless cycle have weight $1.$
-\end{enumerate}
-we include the relation
-\begin{align*}
-	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
-\end{align*}
-where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
-\end{itemize}
-\end{defn}
-
- We will use these group relations to prove the mutation invariance of $A_{\Gamma}$ in Section \ref{sec:proof_of_main}
+For $\Gamma$ a diagram of finite type, we define the Artin group associated to $\Gamma$ as in Section \ref{sec:defn_artingroup}.
+We will then use the group relations presented in this definition to prove the mutation invariance of $A_{\Gamma}$ in Section \ref{sec:proof_of_main}.
 
@@
 \begin{defn}
+\label{chordlesscycle}
 A {\it chordless cycle} of an unoriented graph $G$ is a connected subgraph $H \subset G$ such that the number of vertices in $H$ is equal to the number of edges in $H,$ and the edges in $H$ form a single cycle.

### 2014-07-30 Paper.tex
"aaron's section edits in T"

@@
 \newtheorem{conj}[thm]{Conjecture}
+\newtheorem{longfig}[thm]{Figure}
 
@@
 Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below, or a triangle with two edges of weight 2 and one of weight 1.
-
+\\
+\hspace*{-1.2cm}
 \begin{tikzpicture}[baseline=-0.5ex]
@@
  \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (5,0)
   {
@@
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (10,0)
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (9,0)
   {
@@
 
-\todo[inline]{directions of arrows within squares?}
-\begin{lem}\label{lem:chordless_cycles}
-Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
+\begin{longfig}
+\label{fig:cycle_types}
+Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
 Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.
-Every chordless cycle in $\Gamma'$ is of one of these types.
 
@@
 
-    \item $C$ is an oriented cycle in $\Gamma$ with exactly one vertex in $C$ connected to $k$ by an edge of either weight 1 or 2. Then, $C'$ is the corresponding cycle in $\Gamma'.$  
+      \item
+   \begin{tikzpicture}[baseline=-0.5ex]
+    \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
+  {
+    & & |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& |[name = mm]|\circ &&& |[name = mr]|\vdots \\
+    %
+    & & |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (mm) to node[above] {1} (ml)
+  ;
+  \draw[->]
+  (mm) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(mm)
+  ;
+    \node at (ml.west){$k$};
+    \node at (mm.north){h};
+    \node at (um.north){1};
+    \node at (ur.north){2};
+    \node at (dr.south){$h-2$};
+    \node at (dm.south){$h-1$};
+  \node [yshift = -.9 cm] at (ur){$C'$};
+   \matrix[matrix of math nodes,column sep={40pt,between origins},row
+    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    & & |[name = um]|\circ & |[name = ur]|\circ&\\
+    %
+    |[name = ml]|\bullet& |[name = mm]|\circ &&& |[name = mr]|\vdots \\
+    %
+    & & |[name = dm]|\circ & |[name = dr]|\circ&\\
+  };
+\draw[->]
+  (ml) to node[above] {1} (mm)
+  ;
+  \draw[->]
+  (mm) to node[above]{1}(um)
+  ;
+  \draw[->]
+  (um) to node[above]{1}(ur)
+  ;
+  \draw[->]
+  (ur) [bend left] to (mr)
+  ;
+  \draw[->]
+  (mr) [bend left] to (dr)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dm)
+  ;
+  \draw[->]
+  (dm) to node[below]{1}(mm)
+  ;
+    \node at (ml.west){$k$};
+    \node at (mm.north){h};
+    \node at (um.north){1};
+    \node at (ur.north){2};
+    \node at (dr.south){$h-2$};
+    \node at (dm.south){$h-1$};
+  \node [yshift = -.9 cm] at (ur){$C'$};
+   \end{tikzpicture}
 \end{enumerate}
-
+\end{longfig}
+
+\begin{lem}\label{lem:chordless_cycles}
+\cite[Lemma 2.5]{BM13} Every chordless cycle in $\Gamma'$ is of one of the types listed in Figure ~\ref{fig:cycle_types}.
 \end{lem}
-\begin{proof}
-See \cite[Lemma 2.5]{BM13}.
-\end{proof}
 
@@
 \begin{itemize}
-	\item[(R2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
+\item[(T2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
 $\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$
 
-\item[(R3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally,
+\item[(T3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally,
 \begin{enumerate}
@@
 \begin{align*}
-	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
+s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} s_{a}^{-1}\dots s_{a-2}^{-1}s_{a-1}^{-1}s_{a-2}s_{a-3} \dots s_{a+1} = e
 \end{align*}
-where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
+where subscripts are taken $\pmod d.$ We will denote this relation by $t(a,a+1) = e$.
 \end{itemize}
@@
 \begin{rem}
-We purposely include relations $(R2),(R3)$ but not $(R1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3.
-Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of rem 3 in \cite{BM13}.
+We purposely include relations $(T2),(T3)$ but not $(T1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3.
+Note that if we add the additional relation $(T1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of rem 3 in \cite{BM13}.
 \end{rem}
@@
 \begin{rem}
-Throughout the remainder of the paper, we shall frequently discuss relations on one diagram of finite type, $\Gamma,$ and another diagram of finite type $\Gamma^\prime.$ In order to distinguish the relations in these two groups, we shall refer to the relations on $\Gamma$ as $(R2),(R3)$ and the relations on $\Gamma^\prime$ as $(R2^\prime),(R3^\prime).$
+Throughout the remainder of the paper, we shall frequently discuss relations on one diagram of finite type, $\Gamma,$ and another diagram of finite type $\Gamma^\prime.$ In order to distinguish the relations in these two groups, we shall refer to the relations on $\Gamma$ as $(T2),(T3)$ and the relations on $\Gamma^\prime$ as $(T2^\prime),(T3^\prime).$
 \end{rem}
@@
 \begin{ex}
-The relations $(R2),(R3)$ in that $\Gamma$ is a square with all edges of weight 1 are as follows:
+The relations $(T2),(T3)$ in that $\Gamma$ is a square with all edges of weight 1 are as follows:
 \[\Gamma =\begin{tikzpicture}[baseline=-0.5ex]
@@
    \begin{enumerate}
-	\item[(R2)]
+\item[(T2)]
 \begin{itemize}
@@
 \end{itemize}
-	\item[(R3)]
+\item[(T3)]
 \begin{itemize}
-	\item $s_{1}s_{2}^{-1}s_{3}^{-1}s_4s_{3}s_2 = s_{2}^{-1}s_{3}^{-1}s_4s_3s_{2}s_{1}$
-	\item $s_{2}s_{3}^{-1}s_{4}^{-1}s_1s_{4}s_3 = s_{3}^{-1}s_{4}^{-1}s_1s_4s_{3}s_{2}$
-	\item $s_{3}s_{4}^{-1}s_{1}^{-1}s_2s_{1}s_4 = s_{4}^{-1}s_{1}^{-1}s_2s_1s_{4}s_{3}$
-	\item $s_{4}s_{1}^{-1}s_{2}^{-1}s_3s_{2}s_1 = s_{1}^{-1}s_{2}^{-1}s_3s_2s_{1}s_{4}$
+\item $s_{1}s_{2}^{-1}s_{3}^{-1}s_4s_{3}s_2s_1^{-1}s_2^{-1}s_3^{-1}s_4^{-1}s_3s_2 = e$
+\item $s_{2}s_{3}^{-1}s_{4}^{-1}s_1s_{4}s_3s_2^{-1}s_3^{-1}s_4^{-1}s_1^{-1}s_4s_3 = e$
+\item $s_{3}s_{4}^{-1}s_{1}^{-1}s_2s_{1}s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4 = e$
+\item $s_{4}s_{1}^{-1}s_{2}^{-1}s_3s_{2}s_1s_4^{-1}s_1^{-1}s_2^{-1}s_3^{-1}s_2s_1 = e$
 \end{itemize}
@@
 Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that Dynkin diagram.
-This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(R2'),$ which define the Artin group.
+This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(T2'),$ which define the Artin group.
 \end{rem}

### 2014-07-30 Paper.tex
edits to section 6 and fixed typos in section 4

--- 2014-07-29 Paper.tex
@@
 Our main result is to show that this Artin group presentation is invariant up to isomorphism under the mutation equivalence relation.
-We state the result here, but present the detailed proof in Section \ref{sec:proof_of_main}.
+We state the result here, but present the detailed proof in Section \ref{sec:main_result}.
 
@@
 Section \ref{sec:one_relation} specifies how certain relations in chordless cycles imply other relations in those chordless cycles.
-Finally, Section \ref{sec:proof_of_main} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
+Finally, Section \ref{sec:main_result} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
 \\
@@
 \end{displaymath}
-and $\textbf{x}^{\prime} = \left{ x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n \right}$. 
-Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = \left{ x_1, \ldots, x_n \right}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables.
+and $\textbf{x}^{\prime} = { x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n}$. 
+Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = { x_1, \ldots, x_n}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables.
 \\
@@
 The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge.
-A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in \left{ 1, \ldots, n \right}$.
+A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in { 1, \ldots, n }$.
 By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically.
@@
 For $\Gamma$ a diagram of finite type, we define the Artin group associated to $\Gamma$ as in Section \ref{sec:defn_artingroup}.
-We will then use the group relations presented in this definition to prove the mutation invariance of $A_{\Gamma}$ in Section \ref{sec:proof_of_main}.
+We will then use the group relations presented in this definition to prove the mutation invariance of $A_{\Gamma}$ in Section \ref{sec:main_result}.
 
@@
   ;
-    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){k};
+    \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
    \node  [yshift = .4 cm,xshift = .4 cm] at (ur){k=2};
@@
 \end{align*}
-That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k.$
+That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k$.  We also write $\langle x_i,x_j\rangle^{-k}$ to denote $\left(\langle x_i,x_j\rangle^k\right)^{-1}$
 
@@
 
-\section{Proof of Main Result}\label{sec:proof_of_main}
-
-\noindent In this section we prove our main result:
+\section{Main Result}\label{sec:main_result}
+\noindent In Section \ref{sec:proof_of_main_result} we prove our main result:
 
@@
 
-Throughout this section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.
+Throughout the section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.
 We will write $s_i$, $r_i$, $q_i$, and $u_i$ for the generators corresponding to vertex $i$ of $A_{\Gamma}$, $A_{\Gamma^\prime}$, $A_{\Gamma^{op}}$, and $A_{\left(\Gamma^\prime\right)^{op}}$, respectively.
-We will also abuse notation and write $u_i$ for the generators of $A_{\left(\Gamma^{op}\right)^\prime}$ as well, making use of the fact that $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.
-
-In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, whose proof we will defer until after the proof of Theorem \ref{thm:main} and then split into Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.
+Note that the $u_i$ are generators $A_{\left(\Gamma^{op}\right)^\prime}$ as well, since $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.
+In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.
 
@@
 
+\subsection{Proof of Main Result}\label{sec:proof_of_main_result}
+
 \todo{do we define $m_{ij}'$ somewhere?}
@@
 \begin{proof}[Proof of Theorem \ref{thm:main}]
-By Proposition \ref{prop:ti_relations} $\varphi\colon A_{\Gamma^\prime}\rightarrow A_\Gamma$ is a group homomorphism.
-We also abuse notation and write $\varphi\colon A_{\Gamma^{op}}\rightarrow A_{\left(\Gamma^{op}\right)^\prime}$ by letting $\varphi(q_i)$ equal $u_ku_iu_k^{-1}$ if there is an arrow $i\rightarrow k$ in $\left(\Gamma^{op}\right)^\prime$, and $u_i$ otherwise, and this is a homomorphism by Proposition \ref{prop:ti_relations} as well.
-By Lemma \ref{lem:op_homomorphism}, the homormorphism $\Delta$ that sends $s_i\in A(\Gamma)$ to $q_i^{-1}\in A(\Gamma^{op})$ and $u_i\in A_{\left(\Gamma^\prime\right)^{op}}$ to $r_i\in A_{\Gamma^\prime}$ is well-defined.
+By Proposition \ref{prop:ti_relations} $\varphi\colon A_{\Gamma^\prime}\rightarrow A_\Gamma$ is a group homomorphism and $\varphi_{op}\colon A_{\Gamma^{op}}\rightarrow A_{\left(\Gamma^{op}\right)^\prime}$ defined by
+
+\begin{displaymath}
+\varphi_{op}(q_i) = \begin{cases}    u_ku_iu_k^{-1} & \mbox{if there is a (possibly weighted) arrow } i \rightarrow k \mbox{ in } \left(\Gamma^{op}\right)^\prime\\
+				u_i & \mbox{otherwise}\\
+	\end{cases}
+\end{displaymath}
+
+\noindent is a group homomorphism as well.
+By Lemma \ref{lem:op_homomorphism}, there exist two well-defined homomorphisms $\Delta\colon A_{\Gamma}\rightarrow A_\Gamma^{op}$ defined by $\Delta(s_i) = q_i^{-1}$ and $\Delta^\prime\colon A_{\left(\Gamma^\prime\right)^{op}} \rightarrow A_{\Gamma^\prime}$ defined by $\Delta^\prime(u_i) = r_i^{-1}$.
 We then have a homomorphism
-$$\psi = \Delta\circ\varphi\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
+
+$$\psi = \Delta^\prime\circ\varphi_{op}\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
 
@@
 
-$$\psi\circ\varphi(r_i) = \Delta(\varphi(\Delta(\varphi(r_i)))) = \Delta(\varphi(\Delta(s_ks_is_k^{-1}))) = \Delta(\varphi(q_k^{-1}q_i^{-1}q_k)) = \Delta(u_i^{-1}) = r_i$$
+$$\psi\circ\varphi(r_i) = \Delta^\prime(\varphi_{op}(\Delta(\varphi(r_i)))) = \Delta^\prime(\varphi_{op}(\Delta(s_ks_is_k^{-1}))) = \Delta^\prime(\varphi_{op}(q_k^{-1}q_i^{-1}q_k)) = \Delta^\prime(u_i^{-1}) = r_i$$
 
@@
 
-$$\psi\circ\varphi(r_i) = \Delta(\varphi(\Delta(\varphi(r_i)))) = \Delta(\varphi(\Delta(s_i))) = \Delta(\varphi(q_i^{-1})) = \Delta(u_i^{-1}) = r_i$$
-
-Thus $\psi\circ\varphi$ is the identity map on $A(\Gamma^{\prime})$.  By a similar argument $\varphi\circ\psi$ is the identity map on $A(\Gamma)$, and hence $A(\Gamma)\cong A(\Gamma^{\prime}))$.
+$$\psi\circ\varphi(r_i) = \Delta^\prime(\varphi_{op}(\Delta(\varphi(r_i)))) = \Delta^\prime(\varphi_{op}(\Delta(s_i))) = \Delta^\prime(\varphi_{op}(q_i^{-1})) = \Delta^\prime(u_i^{-1}) = r_i$$
+
+Thus $\psi\circ\varphi$ is the identity map on $A_{\Gamma^{\prime}}$.  By a similar argument $\varphi\circ\psi$ is the identity map on $A_\Gamma$, and hence $A_\Gamma\cong A_{\Gamma^{\prime}}$.
 \end{proof}
 
+\subsection{Proof of Proposition \ref{prop:ti_relations}}\label{sec:proof_of_ti_relations}
+
 We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(R2^\prime)$ and $(R3^\prime)$ relations in $A_{\Gamma^\prime}$.
-Proofs that the $t_i$ satisfy these relations are divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.
+The proof that the $\varphi(r_i)$ satisfy these relations is divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.
 Throughout the proofs we write $t_i = \varphi(r_i)$ for convenience.
@@
 \begin{enumerate}[(a)]
-\item If $i=k$ or $j=k$, then $\langle t_it_j \rangle^k = e$.
-\item If at most of $i,j$ is connected to $k$ in $\Gamma$, then $\langle t_it_j \rangle^k = e$.
+\item If $i=k$ or $j=k$, then $\langle t_it_j \rangle^{m_{ij}^\prime} = \langle t_jt_i \rangle^{m_{ij}^\prime}$.
+\item If at most one of $i,j$ is connected to $k$ in $\Gamma$, then $\langle t_it_j \rangle^{m_{ij}^\prime} = \langle t_jt_i \rangle^{m_{ij}^\prime}$.
 \end{enumerate}
@@
 The only nontrivial case is when there is an arrow $j\rightarrow k =i$.
-Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3,4, or 6.
+Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3, 4, or 6.
 
@@
 {\sf Case $m_{ij} = 3$}.
-Here we have $s_js_is_j = s_is_js_i$, so $s_is_j = s_js_is_js_i^{-1}$, so
-
-$$t_it_jt_i = s_is_is_js_i^{-1}s_i = s_is_is_j = s_is_js_is_js_i^{-1} = t_jt_it_j$$
+Here $\langle s_js_i \rangle^{3} = \langle s_is_j \rangle^{3}$, so $s_is_j = s_js_is_js_i^{-1}$ and we have
+
+$$\langle t_it_j \rangle^{3} = t_it_jt_i = s_is_is_js_i^{-1}s_i = s_is_is_j = s_is_js_is_js_i^{-1} = t_jt_it_j = \langle t_jt_i \rangle^{3}$$
 
@@
 \noindent
-{\sf Case $m_{ij} = 4$}.  Here we have $s_is_js_is_j = s_js_is_js_i$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore
-
-$$t_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_is_js_is_js_i^{-1} = s_is_js_is_j = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_i$$
+{\sf Case $m_{ij} = 4$}.  Here $\langle s_is_j \rangle^{4} = \langle s_js_i \rangle^{4}$, so $s_is_is_js_is_js_i^{-1} = s_is_js_is_j$ and therefore
+
+$$\langle t_it_j \rangle^{4} = s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_is_js_is_js_i^{-1} = s_is_js_is_j = s_is_js_i^{-1}s_is_is_js_i^{-1}s_i = \langle t_jt_i \rangle^{4}$$
 
@@
 \noindent
-{\sf Case $m_{ij} = 6$}.  Here we have $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$.  As in the previous case, we add an remove pairs $s_is_i^{-1}$ as necessary, giving
-
-$$t_it_jt_it_jt_it_j = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = t_jt_it_jt_it_jt_i$$
+{\sf Case $m_{ij} = 6$}.
+Here $\langle s_is_j \rangle^{6} = \langle s_js_i \rangle^{6}$, so $s_is_is_js_is_js_is_js_i^{-1} = s_is_js_is_js_is_j$.
+As in the previous case, we add and remove pairs $s_is_i^{-1}$ as necessary, giving
+
+$$\langle t_it_j \rangle^{6} = s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1} = s_is_js_i^{-1}s_is_is_js_i^{-1}s_is_is_js_i^{-1}s_i = \langle t_it_j \rangle^{6}$$
 
@@
 \noindent
-{\sf Case $m_{ij} = 2$}.  Here $s_is_j = s_js_i$, so we have that
+{\sf Case $m_{ij} = 2$}.  Here $s_is_j = s_js_i$, so $s_j$ commutes with both $s_i$ and $s_k$ and we have that
 
@@
 \noindent
-{\sf Case $m_{ij} = 3$}.  Here $s_is_js_i = s_js_is_j$, so we have that
-
-$$t_it_jt_i = s_ks_is_k^{-1}s_js_ks_is_k^{-1} = s_ks_is_js_is_k^{-1} = s_ks_js_is_js_k^{-1} = s_js_ks_is_k^{-1}s_j = t_jt_it_j$$
+{\sf Case $m_{ij} = 3$}.  Here $\langle s_is_j \rangle^{3} = \langle s_js_i \rangle^{3}$, so we have that
+
+$$\langle t_it_j \rangle^{3} = s_ks_is_k^{-1}s_js_ks_is_k^{-1} = s_ks_is_js_is_k^{-1} = s_ks_js_is_js_k^{-1} = s_js_ks_is_k^{-1}s_j = \langle t_jt_i \rangle^{3}$$
 
@@
 \noindent
-{\sf Case $m_{ij} = 4$}.  Here $s_is_js_is_j = s_js_is_js_i$, so we have that
-
-$$t_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = t_jt_it_jt_i$$
+{\sf Case $m_{ij} = 4$}.  Here $\langle s_is_j \rangle^{4} = \langle s_js_i \rangle^{4}$, so we have that
+
+$$\langle t_it_j \rangle^{4} = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_k^{-1} = s_ks_js_is_js_is_k^{-1} = s_js_ks_is_k^{-1}s_js_ks_is_k^{-1} = \langle t_jt_i \rangle^{4}$$
 
@@
 \noindent
-{\sf Case $m_{ij} = 6$}.  Here $s_is_js_is_js_is_j = s_js_is_js_is_js_i$, so we have that
-
-$$t_it_jt_it_jt_it_j = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_is_js_k^{-1} = s_ks_js_is_js_is_js_is_k^{-1} = t_jt_it_jt_it_jt_i$$
-
+{\sf Case $m_{ij} = 6$}.  Here $\langle s_is_j \rangle^{6} = \langle s_js_i \rangle^{6}$, so we have that
+
+$$\langle t_it_j \rangle^{6} = s_ks_is_k^{-1}s_js_ks_is_k^{-1}s_js_ks_is_k^{-1}s_j = s_ks_is_js_is_js_is_js_k^{-1} = s_ks_js_is_js_is_js_is_k^{-1} = \langle t_it_j \rangle^{6}$$
 \end{proof}
@@
 \begin{lem}\label{lem:r2b_relations}
-Let $i,j$ be distinct vertices of $\Gamma$ such that $i$ and $j$ are connected.  Then $\langle t_it_j \rangle^k = e$.
+Let $i,j$ be distinct vertices of $\Gamma$ such that $i$ and $j$ are connected.  Then $\langle t_it_j \rangle^{m_{ij}^\prime} = \langle t_jt_i \rangle^{m_{ij}^\prime}$.
 \end{lem}
@@
 We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.
-We also check that the corresponding $(R3^\prime)$ relations hold in cases (b), (d), (e), and (f).
-Within each case we view the subdiagram on the left as a subdiagram of $\Gamma$ in the subcase $(i)$ and as a subdiagram of $\Gamma^\prime$ in the subcase $(ii)$.\todo{Disaster.
-Open to suggestions for how to make this more clear}
+Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in the figure in Corollary \ref{local_three_picture}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in the figure in Corollary \ref{local_three_picture}.
 
@@
 \begin{enumerate}[i)]
-\item We have $t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$.
-\item We have $t_it_j = s_is_j = s_js_i = t_jt_i$.
+\item We have $\langle t_it_j \rangle^{2} = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = \langle t_jt_i \rangle^{2}$.
+\item We have $\langle t_it_j \rangle^{2} = s_is_j = s_js_i = \langle t_jt_i \rangle^{2}$.
 \end{enumerate}
@@
 \begin{align*}
-t_it_jt_i &= s_ks_i\underline{s_k^{-1}s_js_k}s_is_k^{-1}\\
+\langle t_it_j \rangle^{3} &= s_ks_i\underline{s_k^{-1}s_js_k}s_is_k^{-1}\\
 &= s_k\underline{s_is_j}s_k\underline{s_j^{-1}s_i}s_k^{-1}\\
@@
 &= s_js_ks_is_k^{-1}s_j\\
-&= t_it_jt_i
-\end{align*}
-
-\item We have $t_it_j = s_i\underline{s_ks_js_k^{-1}} = \underline{s_is_j^{-1}s_ks_j} = \underline{s_j^{-1}s_ks_j}s_i = s_ks_js_k^{-1}s_i = t_jt_i$
+&= \langle t_jt_i \rangle^{3}
+\end{align*}
+
+\item We have $\langle t_it_j \rangle^{2} = s_i\underline{s_ks_js_k^{-1}} = \underline{s_is_j^{-1}s_ks_j} = \underline{s_j^{-1}s_ks_j}s_i = s_ks_js_k^{-1}s_i = \langle t_jt_i \rangle^{2}$
 \end{enumerate}
@@
 \begin{enumerate}[i)]
-\item We have $t_it_j = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = t_jt_i$
-\item We have $t_it_j = s_is_j = s_js_i = t_jt_i$
+\item We have $\langle t_it_j \rangle^{2} = s_ks_is_k^{-1}s_ks_js_k^{-1} = s_ks_is_js_k^{-1} = s_ks_js_is_k^{-1} = \langle t_jt_i \rangle^{2}$
+\item We have $\langle t_it_j \rangle^{2} = s_is_j = s_js_i = \langle t_jt_i \rangle^{2}$
 \end{enumerate}
@@
 \begin{align*}
-t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= s_ks_is_k^{-1}s_js_ks_i\underline{s_k^{-1}s_js_k}s_i^{-1}\underline{s_k^{-1}s_j^{-1}s_k}s_i^{-1}s_k^{-1}s_j^{-1}\\
+\langle t_it_j \rangle^{4}\langle t_jt_i \rangle^{-4} &= t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1}\\
+ &= s_ks_is_k^{-1}s_js_ks_i\underline{s_k^{-1}s_js_k}s_i^{-1}\underline{s_k^{-1}s_j^{-1}s_k}s_i^{-1}s_k^{-1}s_j^{-1}\\
 &=s_ks_is_k^{-1}\underline{s_js_ks_is_j}s_k\underline{s_j^{-1}s_i^{-1}s_j}s_k^{-1}s_j^{-1}s_i^{-1}s_k^{-1}s_j^{-1}\\
@@
 &=s_ks_j\underline{s_is_ks_is_ks_i^{-1}s_k^{-1}s_i^{-1}s_k^{-1}}s_j^{-1}s_k^{-1}\\
+&= s_ks_j\langle s_is_j \rangle^{4}\langle s_js_i \rangle^{-4}s_j^{-1}s_k^{-1} \\
 &= e
@@
 
-\item We have $t_it_j = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = t_jt_i$
+\item We have $\langle t_it_j \rangle^{2} = s_is_ks_js_k^{-1} = s_is_j^{-1}s_ks_j = s_j^{-1}s_ks_js_i = s_ks_js_k^{-1}s_i = \langle t_jt_i \rangle^{2}$
 \end{enumerate}
@@
 \begin{align*}
-t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1} &= \underline{s_ks_is_k^{-1}}s_j\underline{s_ks_is_k^{-1}}s_j\underline{s_ks_i^{-1}s_k^{-1}}s_j^{-1}\underline{s_ks_i^{-1}s_k^{-1}}s_j^{-1}\\
+\langle t_it_j \rangle^{4}\langle t_jt_i \rangle^{-4} &= t_it_jt_it_jt_i^{-1}t_j^{-1}t_i^{-1}t_j^{-1}\\
+&= \underline{s_ks_is_k^{-1}}s_j\underline{s_ks_is_k^{-1}}s_j\underline{s_ks_i^{-1}s_k^{-1}}s_j^{-1}\underline{s_ks_i^{-1}s_k^{-1}}s_j^{-1}\\
 &= s_i^{-1}s_k\underline{s_is_js_i^{-1}}s_k\underline{s_is_js_i^{-1}}s_k^{-1}\underline{s_is_j^{-1}s_i^{-1}}s_k^{-1}\underline{s_is_j^{-1}}\\
 &= s_i^{-1}\underline{s_ks_js_ks_js_k^{-1}s_j^{-1}s_k^{-1}s_j^{-1}}s_i\\
+&= s_i^{-1}\langle t_kt_j \rangle^{4}\langle t_jt_k \rangle^{-4}s_i\\
 &= e
@@
 
-$$t_it_jt_i^{-1}t_j^{-1} = s_is_k\underline{s_js_k^{-1}s_i^{-1}s_k}s_j^{-1}s_k^{-1} = s_is_ks_k^{-1}s_i^{-1}s_ks_js_j^{-1}s_k^{-1} = e$$
+\begin{align*}
+\langle t_it_j \rangle^{2}\langle t_jt_i \rangle^{-2} &= t_it_jt_i^{-1}t_j^{-1}\\
+&= s_is_k\underline{s_js_k^{-1}s_i^{-1}s_k}s_j^{-1}s_k^{-1}\\
+&= s_is_ks_k^{-1}s_i^{-1}s_ks_js_j^{-1}s_k^{-1}\\
+&= e\\
+\end{align*}
 
@@
 \begin{align*}
-s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1}s_k &= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
+s_k^{-1}\langle t_it_j \rangle^{3}\langle t_jt_i \rangle^{-3}s_k &= s_k^{-1}t_it_jt_it_j^{-1}t_i^{-1}t_j^{-1}s_k\\
+&= s_is_k^{-1}s_js_ks_is_k^{-1}s_j^{-1}s_ks_i^{-1}s_k^{-1}s_j^{-1}s_k\\
 &= e
@@
 
-Where the second equality follows from Lemma \ref{lem:extra_square_relation}.
+Where the second equality follows from Lemma \ref{lem:extra_square_relation}.  It follows that $\langle t_it_j \rangle^{4} = \langle t_jt_i \rangle^{4}$.
 
@@
 We follow the labeling of the vertices used in Lemma \ref{lem:chordless_cycles}.
+We denote by $r^\prime(m,n)$ the expression given by replacing the generators $r_i$ in the corresponding expression $r(m,n)$ in $A_{\Gamma^\prime}$ with $t_i$.
+When helpful we note uses of $(R3)$ relations in $A_\Gamma$ by referencing the particular cycle relation used next to the manipulation.
 
 \begin{enumerate}[a)]
-\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$
-
-\item We have $ t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_3t_1$
-
-\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_3s_1 = t_2^{-1}t_3t_2t_1$
+\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.
+
+\item We have $ t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.
+
+\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.
 
@@
 \begin{align*}
-t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1 &= s_2s_3s_2^{-1}s_1^{-1}s_2s_1s_2s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
-&= s_2s_3s_1s_2s_1^{-1}s_2^{-1}s_2s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
-&= s_2s_3s_1s_2s_1^{-1}s_3^{-1}s_2^{-1}s_1^{-1}s_2^{-1}s_1\\
-&= s_2s_3s_1s_2s_1^{-1}s_3^{-1}s_1s_2^{-1}s_1^{-1}s_2^{-1}\\
-&= s_2s_1s_2s_1^{-1}s_3s_3^{-1}s_1s_2^{-1}s_1^{-1}s_2\\
-&= e\\
-\end{align*}
+s_2^{-1}r^\prime(3,1)s_2 &= s_2^{-1}t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1s_2\\
+&= s_3\underline{s_2^{-1}s_1^{-1}s_2s_1s_2}s_3^{-1}\underline{s_2^{-1}s_1^{-1}s_2^{-1}s_1s_2}\\
+&= s_3s_1\underline{s_2s_1^{-1}s_3^{-1}s_1}s_2^{-1}s_1^{-1}\\
+&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &r(2,1)\\
+&= e
+\end{align*}
+
+\noindent Hence $r^\prime(3,1) = e$.
 
@@
 &= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
-&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}}\\
+&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &r(2,3)\\
 &= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
@@
 
+\noindent Hence $r^\prime(1,2) = e$.
+
 \item We have
@@
 &= s_1s_3^{-1}s_4s_3\\
-&= s_3^{-1}s_4s_3s_1\\
+&= s_3^{-1}s_4s_3s_1 &r(1,3)\\
 &= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
-&= s_2^{-1}2s_3^{-1}s_2^{-1}s_4s_2s_3s_2^{-1}s_2s_1\\
+&= s_2^{-1}s_2s_3^{-1}s_2^{-1}s_4s_2s_3s_2^{-1}s_2s_1\\
 &= t_2^{-1}t_3^{-1}t_4t_3t_2t_1\\
@@
 
+\noindent Hence $r^\prime(1,2) = e$.
+
 \item We have
 \begin{align*}
-t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4 &= \underline{s_3s_1}s_4^{-1}s_1^{-1}s_2s_1s_4\underline{s_1^{-1}s_3^{-1}s_1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4s_1^{-1}\\
+r^\prime(3,4) &= t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4\\
+&= \underline{s_3s_1}s_4^{-1}s_1^{-1}s_2s_1s_4\underline{s_1^{-1}s_3^{-1}s_1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4s_1^{-1}\\
 &= s_1\underline{s_3s_4^{-1}s_1^{-1}s_2s_1s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4}s_1^{-1}\\
+&= s_1r(3,4)s_1^{-1}\\
 &= s_1s_1^{-1}\\
@@
 &= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
-&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3\\
+&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &r(3,4)\\
 &= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
@@
 
+\noindent Hence $r^\prime(3,4) = e$.
+
 \item We have
 \begin{align*}
-& t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
+&r^\prime(1,2)\\
+&= t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
 &= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_hs_k^{-1}}s_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}\underline{s_ks_h^{-1}s_k^{-1}}s_{h-1}\cdots s_2\\
 &= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
+&= r(1,2)\\
 &= e\\
@@
 
-\item We have
-\begin{align*}
-& t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
+\item Here $s_k$ commutes with $s_i$ for all $i\ne 1,h$, so we have
+\begin{align*}
+& r^\prime(h,1)\\
+&= t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
 &= s_h\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots \underline{s_k}s_1\underline{s_k^{-1}s_k}s_h^{-1}\underline{s_k^{-1}s_k}s_1^{-1}\underline{s_k^{-1}}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2 \underline{s_k}s_1\underline{s_k^{-1}s_k}\\
 &= s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_2s_1s_h^{-1}s_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2s_1\\
+&= r(h,1)\\
 &= e\\
 \end{align*}
+
+\item Here $t_i = s_i$ for all vertices $i$ in $C^\prime$, so the case is trivial.
+
+\item  If the edge between $k$ and $h$ points towards $h$, then $t_i = s_i$ for all $i\in C^\prime$ and the case is trivial.
+If the edge points towards $k$ then $t_h = s_ks_hs_k^{-1}$ and $s_k$ commutes with $s_i$ for all vertices $i\ne h$ in $C^\prime$, so we have
+
+\begin{align*}
+t_1t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2 &= s_1s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2\\
+&= s_k\underline{s_1s_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2}s_k^{-1}\\
+&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &r(1,2)\\
+&= s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2s_1\\
+&= t_2^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1\\
+\end{align*}
+
+\noindent Hence $r^\prime(1,2) = e$.
 \end{enumerate}

### 2014-07-30 Paper.tex

@@
 \end{displaymath}
-and $\textbf{x}^{\prime} = { x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n}$. 
-Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = { x_1, \ldots, x_n}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables.
+
+and $\textbf{x}^{\prime} = \left\{ x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n \right\}$.
+Such a mutation or a sequence of such mutations generate \textit{seeds} which in turn generate all cluster variables in that, for each $\textbf{x} = \left\{ x_1, \ldots, x_n \right\}$ corresponding to a seed of the cluster algebra, the entries $x_i$ are the cluster variables.
 \\
@@
 The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge.
-A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in { 1, \ldots, n }$.
+A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in \left\{ 1, \ldots, n \right\}$.
 By \cite[7.5]{FZ02}, we have that if $B$ is 2-finite, all 3-cycles in the unoriented graph underlying our diagram must be oriented cyclically.
@@
   ;
+
     \node [yshift = .4 cm,xshift = -.4 cm] at (ul){1};
@@
 \begin{defn}
-\cite[Beginning of section 1.2]{artin} \todo{put reference for artin, found at the bottom, in bibliography, but I don't know how to use this bibliography format.}
+\cite[Beginning of section 1.2]{artin} \todo{put reference for artin, found at the bottom, in bibliography, but I don't know how to use this bibliography format.
+- it's just BibTex, which you'll almost certainly want to learn at some point.
+Try editing References.bib, and if you have trouble feel free to ask me for help - David}
 For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
@@
 \begin{align*}
-	s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} = s_{a+1}^{-1}\dots s_{a-3}^{-1}s_{a-2}^{-1}s_{a-1}s_{a-2}\dots s_{a+1}s_{a},
-\end{align*}
-where subscripts are taken $\pmod d.$ We will denote this relation by r(a, a+1). 
+s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} s_{a}^{-1}\dots s_{a-2}^{-1}s_{a-1}^{-1}s_{a-2}s_{a-3} \dots s_{a+1} = e
+\end{align*}
+where subscripts are taken $\pmod d.$ We will denote this relation by $t(a,a+1) = e$.
 \end{itemize}
@@
 Note that $m_{ij}^\prime = m_{ij}$.
-The only nontrivial case is when there is an arrow $j\rightarrow k =i$.
+The only nontrivial case is when there is an arrow $j\rightarrow k = i$.
 Since $i$ and $j$ are connected in this case, $m_{ij}$ is one of 3, 4, or 6.

### 2014-07-30 Paper.tex
Updated Section 5 and added Lemma 2.4 of BM13

@@
 \end{cor}
+
+\begin{lem} \cite[Lemma 2.4]{BM13}
+Suppose that a vertex k is connected to at least one vertex of a chordless cycle in a diagram $\Gamma$ of finite type.
+Then k is connected to at most two vertices in the cycle, and if it is connected to two vertices, they must be adjacent in the cycle.
+\end{lem}
 
@@
 
-Given the relations (R2), many of the relations in (R3) become redundant. For example,
+Given the relations (T2), many of the relations in (T3) become redundant. For example,
 
@@
 so that all edges have weight 1.
-Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (R2) and $r(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (R3) hold for C.
+Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
 \end{lem}
@@
 \begin{proof}
-As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $A_{\Gamma}$ satisfies the relation r(0, 1). Then we have
-\begin{align*}
-& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
+It suffices to prove that the relation t(0, 1) implies the relation t(d-1, 0), as the other relations will follow by induction. So suppose $A_{\Gamma}$ satisfies the relation t(0, 1). Then we have
+\begin{align*}
+s_{d-1}p_{d-1, 0} & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
 &= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} &\text{by (T2)} \\
 &= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
+&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} &\text{by (T2)}\\
+&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by t(0, 1)}\\
+&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by (T2)}\\
 &= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}
+&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} &\text{by (T2)}\\
+&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p_{d-1, 0}s_{d-1}
 \end{align*}
@@
    \end{tikzpicture}
-and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations r(i, j) and r(k, i) are equivalent.
+and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) and t(k, i) are equivalent.
 \end{lem}
@@
 \begin{align*}
+& s_{k}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{k} \\
 & s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
 &= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
-&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i}
+&= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i} \\
+&= s_{k}^{-1}p_{k, i}s_{k}p_{k, i}^{-1}
 \end{align*}
@@
 Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that
-$$s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
+$$s_{j}p_{j, k}s_{j}p_{j, k}^{-1}s_{j}^{-1}p_{j, k}^{-1} := s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
 \end{lem}
@@
 \end{tikzpicture}
-and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations r(i, j) and r(k, l) are equivalent.
+and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) and t(k, l) are equivalent.
 \end{lem}
@@
 \begin{align*}
-& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{l}^{-1}s_{k}s_{j})s_{j}^{-1}s_{l}s_{k} \\
+& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{l}s_{k} \\
+&= s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{l}^{-1}s_{k}s_{j})s_{j}^{-1}s_{l}s_{k} \\
 &= s_{k}^{-1}s_{l}^{-1}(s_{j}s_{i}s_{j}^{-1})(s_{k}^{-1}s_{l}s_{k})(s_{j}s_{i}^{-1}s_{j}^{-1})s_{k}^{-1}s_{l}^{-1}s_{k}s_{l}s_{k} \\
 &= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{k}^{-1}(s_{l}^{-1}s_{k}s_{l})s_{k} \\
-&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{l}
+&= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{l} \\
+&= s_{k}^{-1}p_{k, l}s_{k}p_{k, l}^{-1}
 \end{align*}
@@
 \begin{lem}\label{lem:op_homomorphism}
-Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$.
-Then $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (R2) and (R3) in A$_{\Gamma^{op}}$.
-In particular, A$_{\Gamma}$ $\cong$ A$_{\Gamma^{op}}$.
+Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$, and let A$_{\Gamma^{op}}$ be generated by $r_{1}, \dots, r_{n}$.
+Then the map $$\Delta: s_{i} \rightarrow r_{i}^{-1}$$ defines an isomorphism between A$_{\Gamma}$ and A$_{\Gamma^{op}}.$
 \end{lem}
 \begin{proof}
-One can see that the inverse elements satisfy (R2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$.
-To see that the elements satisfy (R3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation r(0,1) in (R3) in A$_{\Gamma}$.
-But then applying relations from (R2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation r(0, d-1) in A$_{\Gamma^{op}}.$
-
-For a triangle labeled as in ~\ref{2tri}, by the relation r(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation r(k, j) in A$_{\Gamma^{op}}$.
-
-Finally, given a square labeled as in ~\ref{2sqr} and the relations r(1, 2) and r(3, 4), we have
+It suffices to show that the map is well-defined, or that the elements $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfy the relations (T2) and (T3) of A$_{\Gamma^{op}}$.
+One can see that the inverse elements satisfy (T2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$.
+To see that the elements satisfy (T3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation t(0,1) in (T3) in A$_{\Gamma}$.
+But then applying relations from (T2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation t(0, d-1) in A$_{\Gamma^{op}}.$
+
+For a triangle labeled as in ~\ref{2tri}, by the relation t(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation t(k, j) in A$_{\Gamma^{op}}$.
+
+Finally, given a square labeled as in ~\ref{2sqr} and the relations t(1, 2) and t(3, 4), we have
 \begin{align*}
@@
 \end{align*}
-But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy r(j, i) in A$_{\Gamma^{op}}$. Therefore, we are done.
+But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy t(j, i) in A$_{\Gamma^{op}}$. Therefore, we are done.
 \end{proof}

### 2014-07-30 Paper.tex
"Additional edits to t notation aaron"

@@
 
+\begin{note}
+\label{defn:mij}
 \indent Given a diagram $\Gamma$, Barot and Marsh define for $i, j \in \V$,
 \begin{displaymath}
-\label{mij_defn}
 m_{ij} = \begin{cases} 2 & \mbox{if } i \mbox{ and } j \mbox{ are not connected;} \\
@@
 \end{displaymath}	
+\end{note}
 
@@
 
+Finally, we are ready to define the Artin group we associate to a diagram of finite type. First, we shall need a tiny bit more notation.
+
+\begin{note}
+Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}} s_{i_{a}}^{-1}.$$ Additionally, let $$t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1}) p(i_a,i_{a+1})^{-1} s_{i_a}^{-1}.$$
+\end{note}
+
 \begin{defn} \label{grp def}
-
-Recall from Section \ref{sec:main_definitions} that for $\Gamma$ a diagram of finite type, we define the associated Artin group as follows.
-The associated Artin group $A_\Gamma$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
+The {\it associated Artin group} to a diagram $\Gamma$ of finite type, denoted $A_\Gamma,$ is generated by $s_i,$ where there is one $s_i$ for each vertex $i$ in $\Gamma.$ These generators are subject to the following relations
 \begin{itemize}
-\item[(T2)] With $m_{ij}$ as defined in ~\ref{mij_defn}, for all $i \neq j,$ we add the relations
+\item[(T2)] With $m_{ij}$ as defined in Definition ~\ref{defn:mij}, for all $i \neq j,$ we add the relations
 $\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$
 
-\item[(T3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally,
+\item[(T3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally, one of the following two conditions hold,
 \begin{enumerate}
@@
 \end{enumerate}
-we include the relation
-\begin{align*}
-s_{a}s_{a+1}^{-1}s_{a+2}^{-1}\dots s_{a-2}^{-1}s_{a-1}s_{a-2}s_{a-3}\dots s_{a+1} s_{a}^{-1}\dots s_{a-2}^{-1}s_{a-1}^{-1}s_{a-2}s_{a-3} \dots s_{a+1} = e
-\end{align*}
-where subscripts are taken $\pmod d.$ We will denote this relation by $t(a,a+1) = e$.
+then, we include the relation
+$t(i_0,i_1) = e.$
 \end{itemize}

### 2014-08-01 Paper.tex
Minor Edit
small edits

@@
 
-\todo{do we define $m_{ij}'$ somewhere?}
-
 \begin{proof}[Proof of Theorem \ref{thm:main}]
@@
 
-We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(R2^\prime)$ and $(R3^\prime)$ relations in $A_{\Gamma^\prime}$.
+We prove Proposition \ref{prop:ti_relations} by showing that that the elements $\varphi(r_i)\in A_\Gamma$ satisfy the $(T2^\prime)$ and $(T3^\prime)$ relations in $A_{\Gamma^\prime}$.
 The proof that the $\varphi(r_i)$ satisfy these relations is divided among Lemmas \ref{lem:r2a_relations}, \ref{lem:r2b_relations}, and \ref{lem:r3_relations}.
-Throughout the proofs we write $t_i = \varphi(r_i)$ for convenience.
+Throughout the proofs we write $t_i = \varphi(r_i)$ and $m_{ij}^\prime$ for the weight of the edge between $i$ and $j$ in $\Gamma^\prime$.
 
@@
 The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.
-We show that $t_i$ and $t_j$ satisfy the $(R2^\prime)$ relations by checking each case.
+We show that $t_i$ and $t_j$ satisfy the $(T2^\prime)$ relations by checking each case.
 Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in the figure in Corollary \ref{local_three_picture}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in the figure in Corollary \ref{local_three_picture}.
@@
 \begin{lem}\label{lem:r3_relations}
-The elements $t_i$ satisfy the $(R3^\prime)$ relations in $\Gamma^\prime$.
+The elements $t_i$ satisfy the $(T3^\prime)$ relations in $\Gamma^\prime$.
 \end{lem}
@@
 We follow the labeling of the vertices used in Lemma \ref{lem:chordless_cycles}.
-We denote by $r^\prime(m,n)$ the expression given by replacing the generators $r_i$ in the corresponding expression $r(m,n)$ in $A_{\Gamma^\prime}$ with $t_i$.
-When helpful we note uses of $(R3)$ relations in $A_\Gamma$ by referencing the particular cycle relation used next to the manipulation.
+We denote by $t^\prime(m,n)$ the expression given by replacing the generators $r_i$ in the corresponding expression $t(m,n)$ in $A_{\Gamma^\prime}$ with $t_i$.
+When helpful we note uses of $(T3)$ relations in $A_\Gamma$ by referencing the particular cycle relation used next to the manipulation.
 
 \begin{enumerate}[a)]
-\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.
-
-\item We have $ t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.
-
-\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $r^\prime(1,2) = e$.
+\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $t^\prime(1,2) = e$.
+
+\item We have $ t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_1s_3 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $t^\prime(1,2) = e$.
+
+\item We have $t_1t_2^{-1}t_3t_2 = s_1s_2^{-1}s_2s_3s_2^{-1}s_2 = s_3s_1 = t_2^{-1}t_3t_2t_1$, hence $t^\prime(1,2) = e$.
 
@@
 \begin{align*}
-s_2^{-1}r^\prime(3,1)s_2 &= s_2^{-1}t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1s_2\\
+s_2^{-1}t^\prime(3,1)s_2 &= s_2^{-1}t_3t_1^{-1}t_2t_1t_3^{-1}t_1^{-1}s_2^{-1}t_1s_2\\
 &= s_3\underline{s_2^{-1}s_1^{-1}s_2s_1s_2}s_3^{-1}\underline{s_2^{-1}s_1^{-1}s_2^{-1}s_1s_2}\\
 &= s_3s_1\underline{s_2s_1^{-1}s_3^{-1}s_1}s_2^{-1}s_1^{-1}\\
-&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &r(2,1)\\
+&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &t(2,1)\\
 &= e
@@
 
-\noindent Hence $r^\prime(3,1) = e$.
+\noindent Hence $t^\prime(3,1) = e$.
 
@@
 &= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
-&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &r(2,3)\\
+&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &t(2,3)\\
 &= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
@@
 
-\noindent Hence $r^\prime(1,2) = e$.
+\noindent Hence $t^\prime(1,2) = e$.
 
@@
 &= s_1s_3^{-1}s_4s_3\\
-&= s_3^{-1}s_4s_3s_1 &r(1,3)\\
+&= s_3^{-1}s_4s_3s_1 &t(1,3)\\
 &= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
@@
 \begin{align*}
-r^\prime(3,4) &= t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4\\
+t^\prime(3,4) &= t_3t_4^{-1}t_2t_4t_3^{-1}t_4^{-1}t_2^{-1}t_4\\
 &= \underline{s_3s_1}s_4^{-1}s_1^{-1}s_2s_1s_4\underline{s_1^{-1}s_3^{-1}s_1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4s_1^{-1}\\
 &= s_1\underline{s_3s_4^{-1}s_1^{-1}s_2s_1s_4s_3^{-1}s_4^{-1}s_1^{-1}s_2^{-1}s_1s_4}s_1^{-1}\\
-&= s_1r(3,4)s_1^{-1}\\
+&= s_1t(3,4)s_1^{-1}\\
 &= s_1s_1^{-1}\\
@@
 &= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
-&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &r(3,4)\\
+&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &t(3,4)\\
 &= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
@@
 
-\noindent Hence $r^\prime(3,4) = e$.
+\noindent Hence $t^\prime(3,4) = e$.
 
@@
 \begin{align*}
-&r^\prime(1,2)\\
+&t^\prime(1,2)\\
 &= t_1t_2^{-1}t_3^{-1}\cdots t_{h-1}^{-1}t_ht_{h-1}\cdots t_2t_1^{-1}t_2^{-1}\cdots t_{h-1}^{-1}t_h^{-1}t_{h-1}\cdots t_2\\
@@
 &= s_1s_2^{-1}s_3^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_ks_hs_{h-1}\cdots s_2s_1^{-1}s_2^{-1}\cdots s_{h-1}^{-1}s_h^{-1}s_k^{-1}s_hs_{h-1}\cdots s_2\\
-&= r(1,2)\\
+&= t(1,2)\\
 &= e\\
@@
 \begin{align*}
-& r^\prime(h,1)\\
+& t^\prime(h,1)\\
 &= t_ht_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}t_{h-2}\cdots t_1t_kt_h^{-1}t_k^{-1}t_1^{-1}t_2^{-1}\cdots t_{h-2}^{-1}t_{h-1}^{-1}t_{h-2}\cdots t_2t_1t_k\\
@@
 &= s_hs_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}s_{h-2}\cdots s_2s_1s_h^{-1}s_1^{-1}s_2^{-1}\cdots s_{h-2}^{-1}s_{h-1}^{-1}s_{h-2}\cdots s_2s_1\\
-&= r(h,1)\\
+&= t(h,1)\\
 &= e\\
@@
 &= s_k\underline{s_1s_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2}s_k^{-1}\\
-&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &r(1,2)\\
+&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &t(1,2)\\
 &= s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2s_1\\
@@
 
-\noindent Hence $r^\prime(1,2) = e$.
+\noindent Hence $t^\prime(1,2) = e$.
 \end{enumerate}
@@
 \begin{proof}[Proof of Proposition \ref{prop:ti_relations}]
-Lemma \ref{lem:r2a_relations} and Lemma \ref{lem:r2b_relations} show that the elements $t_i$ satisfy the $(R2^\prime)$ relations for $A_{\Gamma^\prime}$.
-Lemma \ref{lem:r3_relations} shows that they satisfy the $(R3^\prime)$ relations.
+Lemma \ref{lem:r2a_relations} and Lemma \ref{lem:r2b_relations} show that the elements $t_i$ satisfy the $(T2^\prime)$ relations for $A_{\Gamma^\prime}$.
+Lemma \ref{lem:r3_relations} shows that they satisfy the $(T3^\prime)$ relations.
 Since these are all of the relations defining $A_{\Gamma^\prime}$, it follows that $\varphi$ defines a group homomorphism $A_{\Gamma^\prime}\rightarrow A_\Gamma$.

### 2014-08-01 Paper.tex
"Put in Charney to paper"

@@
 
-\begin{lem} \cite[Lemma 2.4]{BM13}
-Suppose that a vertex k is connected to at least one vertex of a chordless cycle in a diagram $\Gamma$ of finite type.
-Then k is connected to at most two vertices in the cycle, and if it is connected to two vertices, they must be adjacent in the cycle.
-\end{lem}
+%\begin{lem} \cite[Lemma 2.4]{BM13}
+%Suppose that a vertex k is connected to at least one vertex of a chordless cycle in a diagram $\Gamma$ of finite type.
+Then k is connected to at most two vertices in the cycle, and if it is connected to two vertices, %they must be adjacent in the cycle.
+%\end{lem}
 
@@
 \begin{defn}
-\cite[Beginning of section 1.2]{artin} \todo{put reference for artin, found at the bottom, in bibliography, but I don't know how to use this bibliography format.
-- it's just BibTex, which you'll almost certainly want to learn at some point.
-Try editing References.bib, and if you have trouble feel free to ask me for help - David}
+\cite[Beginning of section 1.2]{C06}
 For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
@@
 
-artin: http://people.brandeis.edu/~charney/papers/RAAGfinal.pdf
-
 \end{document}

### 2014-08-01 Paper.tex
"edits to section 4, corrected t(a,b)

@@
 Second, in Corollary ~\ref{local_three_picture} all possible local pictures between a mutated vertex and two adjacent vertices are drawn.
-Finally, in ~\ref{lem:chordless_cycles}, all chordless cycles introduced from a mutation are drawn.
+Finally, in Lemma ~\ref{lem:chordless_cycles}, all chordless cycles introduced from a mutation are drawn.
 These three lemmas will be crucial in proving the main result Theorem ~\ref{thm:main}, as they will allow us to inspect precisely which relations are added and removed after mutating at a prescribed vertex.
@@
 Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$.
-Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, as pictured below, or a triangle with two edges of weight 2 and one of weight 1.
+Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, or a triangle with two edges of weight 2 and one of weight 1, as pictured below.
 \\
@@
 That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k$.  We also write $\langle x_i,x_j\rangle^{-k}$ to denote $\left(\langle x_i,x_j\rangle^k\right)^{-1}$
-
 \end{note}
+
 \begin{defn}
 \cite[Beginning of section 1.2]{C06}
-For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i}$ we define the associated {\it Artin group} in terms of generators and relations by
-\begin{align*}
-A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } m_{i,j}<\infty \rangle,
+For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i},$ we define the associated {\it Artin group} in terms of generators and relations by
+\begin{align*}
+A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } M_{i,j}<\infty \rangle,
 \end{align*}
@@
 \begin{rem}
-Each Artin group has an associated Coxeter group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type.
-To each Artin group of finite type we can assign it the same Dynkin diagram which is assigned to the Coxeter group associated to the Artin group.
+Each Artin group has an associated Coxeter group defined by adding in the additional relations $s_i^2 = e$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type.
+To each Artin group of finite type we can assign to it the same Dynkin diagram which is assigned to the Coxeter group associated to the Artin group.
 \end{rem}
@@
 
-\begin{note}
-Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}} s_{i_{a}}^{-1}.$$ Additionally, let $$t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1}) p(i_a,i_{a+1})^{-1} s_{i_a}^{-1}.$$
-\end{note}
+\begin{defn}
+\label{defn:cycle_tuple}
+Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Call such an ordered tuple a {\it chordless cycle tuple.} Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}}.$$ Additionally, let $$t(i_a,i_{a+1}) = [s_{i_a},p(i_a,i_{a+1})]$$ where $[a,b] = aba^{-1}b^{-1}$ is the commutator.
+\end{defn}
 
@@
 
-\item[(T3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $(i_0,\ldots, i_{d-1})$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1},$ where subscripts $k$ are taken $\pmod d.$ If $(i_0,\ldots, i_{d-1})$ is such an ordered tuple, and additionally, one of the following two conditions hold,
+\item[(T3)] Let $(i_0,i_1,\ldots,i_{d-1})$ be a chordless cycle tuple, as defined in Definition ~\ref{defn:cycle_tuple}. If additionally one of the following two conditions hold,
 \begin{enumerate}
-\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
-\item All edges in the chordless cycle have weight $1.$
+\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2,
+\item All edges in the chordless cycle have weight $1,$
 \end{enumerate}
 then, we include the relation
-$t(i_0,i_1) = e.$
+$t(i_0,i_1)=e.$
 \end{itemize}
@@
 \begin{rem}
-In the above definition, the tuple cycle is ordered, and so we may have multiple relations corresponding to the same set $\{i_0,\ldots, i_{d-1}\},$ corresponding to cyclic rotations of the tuple $(i_0,\ldots, i_{d-1}).$ However, we shall see in Section ~\ref{sec:one_relation} that many of these relations are redundant.
+In the above definition, the chordless cycle tuple is ordered, and so we may have other relations corresponding to chordless cycle tuples which are cyclic reorderings the chordless cycle tuple $(i_0,\ldots, i_{d-1}).$ However, we shall see in Section ~\ref{sec:one_relation} that many of these relations are redundant.
 \end{rem}
@@
 We purposely include relations $(T2),(T3)$ but not $(T1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3.
-Note that if we add the additional relation $(T1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of rem 3 in \cite{BM13}.
+Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of in \cite[Remark 3]{BM13}.
 \end{rem}
@@
 \begin{itemize}
-\item $\langle s_1,s_2 \rangle^3 = \langle s_2,s_21 \rangle^3$
+\item $\langle s_1,s_2 \rangle^3 = \langle s_2,s_1 \rangle^3$
 \item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3$
@@
 \begin{rem}
-Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the corresponding Artin group corresponding to that Dynkin diagram.
+Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the Artin group corresponding to that Dynkin diagram.
 This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(T2'),$ which define the Artin group.

### 2014-08-03 Paper.tex
Small Changes to Section 5

@@
 \begin{align*}
-s_{d-1}p_{d-1, 0} & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
+s_{d-1}p(d-1, 0) & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
 &= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
@@
 &= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} &\text{by (T2)}\\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p_{d-1, 0}s_{d-1}
+&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p(d-1, 0)s_{d-1}
 \end{align*}
@@
 \begin{align*}
-& s_{k}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{k} \\
+& s_{k}^{-1}s_{j}(s_{i}p(i, j)s_{i}^{-1}p(i, j)^{-1})s_{j}^{-1}s_{k} \\
 & s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
@@
 &= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i} \\
-&= s_{k}^{-1}p_{k, i}s_{k}p_{k, i}^{-1}
+&= s_{k}^{-1}p(k, i)s_{k}p(k, i)^{-1}
 \end{align*}
@@
 Suppose $\Gamma$ contains a 3-cycle with edges of weight 2, labeled as in ~\ref{2tri}, and suppose that A$_{\Gamma}$ is generated by $s_{1}, \dots s_{n}$. Then we have that
-$$s_{j}p_{j, k}s_{j}p_{j, k}^{-1}s_{j}^{-1}p_{j, k}^{-1} := s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
+$$s_{j}p(j, k)s_{j}p(j, k)^{-1}s_{j}^{-1}p(j, k)^{-1} := s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}^{-1}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
 \end{lem}
@@
 \begin{align*}
-& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{l}s_{k} \\
+& s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}p(i, j)s_{i}^{-1}p(i, j)^{-1})s_{j}^{-1}s_{l}s_{k} \\
 &= s_{k}^{-1}s_{l}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}^{-1}s_{l}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{l}^{-1}s_{k}s_{j})s_{j}^{-1}s_{l}s_{k} \\
@@
 &= s_{k}^{-1}s_{l}^{-1}s_{i}^{-1}s_{j}s_{i}s_{l}s_{k}s_{l}^{-1}s_{i}^{-1}s_{j}^{-1}s_{i}s_{l} \\
-&= s_{k}^{-1}p_{k, l}s_{k}p_{k, l}^{-1}
+&= s_{k}^{-1}p(k, l)s_{k}p(k, l)^{-1}
 \end{align*}

### 2014-08-03 Presentation/Presentation/Prob6.tex
fixed issues from practice talk

\documentclass{beamer}
%
% Choose how your presentation looks.
%
% For more themes, color themes and font themes, see:
% http://deic.uab.es/~iblanes/beamer_gallery/index_by_theme.html
%
\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{crane} % or try albatross, beaver, crane, ...
  \usefonttheme{structureitalicserif}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{caption}[numbered]
}

\usepackage[english]{babel}
%\usepackage[utf8x]{inputenc}
\usepackage{mathrsfs}

\newtheorem{proposition}{Proposition}
\newtheorem{rem}{Remark}
\newtheorem{goal}{Goal}

\title[Artin Group Presentations]{Artin Group Presentations Arising from Cluster Algebras}
\author{Jacob Haley*, David Hemminger, Aaron Landesman, 
Hailee Peck*}
\institute{University of Minnesota, Twin Cities REU}
\date{\today}

\begin{document}

\begin{frame}
  \titlepage
  \let\thefootnote\relax\footnote{* denotes speaker}
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
\end{frame}

\begin{frame}{Brief History}
Fomin and Zelevinsky introduced \textit{cluster algebras}, generated from seed variables. These algebras are of finite type if they are generated from a finite number of seeds. Fomin and Zelevinsky also showed that cluster algebras of finite type can be classified by Dynkin diagrams.
\begin{figure}
\centering
\includegraphics[scale = .25]{dynkindiagrams.PNG}
\caption{Dynkin diagrams}
\end{figure}
\end{frame}

\begin{frame}{Example}
\begin{figure}
\centering
\includegraphics[scale = .65]{DynkinA3.PNG}
\caption{Dynkin diagram of type $A_3$}
\end{figure}

Coxeter group relations:
\begin{itemize}
\item $s_1^2 = s_2^2 = s_3^2 = e$
\item $(s_1s_2)^3 = (s_2s_3)^3 = e$
\item $(s_1s_3)^2 = e$
\end{itemize}

Artin group relations:
\begin{itemize}
\item $\langle s_1, s_2 \rangle ^3 = \langle s_2, s_1 \rangle ^3$
\item $\langle s_2, s_3 \rangle ^3 = \langle s_3, s_2 \rangle ^3$
\item $\langle s_1, s_3 \rangle ^2 = \langle s_3, s_1 \rangle ^2$
\end{itemize}
Alternatively, the above relations correspond to 
\begin{itemize}
\item $s_1s_2s_1 = s_2s_1s_2$
\item $s_2s_3s_2 = s_3s_2s_3$
\item $s_1s_3 = s_3s_1$
\end{itemize}

\end{frame}

\begin{frame}
Barot and Marsh extended the Coxeter group presentations to diagrams of finite type (making an allowance for chordless cycles), and proved that this group presentation is isomorphic to the Coxeter group associated to a Dynkin diagram. They also proved mutation invariance, up to isomorphism, for these Coxeter groups.

\pause
\begin{goal}
Develop variations of relations for the Coxeter group associated to a diagram of finite type provided in Barot-Marsh to define the Artin group $A_{\Gamma}$ corresponding to a diagram $\Gamma$. Prove that for $\Gamma^{\prime} = \mu_k(\Gamma)$, we get $A_{\Gamma} \cong A_{\Gamma^{\prime}}$. 
\end{goal}
\end{frame}

\section{Preliminary Definitions}

\begin{frame}
\begin{definition}
We say a matrix $B$ is \textit{skew-symmetrisable} if there exists a diagonal matrix $D$ of the same size such that $|D_{ii}|>0$ and $DB$ is skew-symmetric.
\end{definition}

\pause

\begin{definition}
A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for all $i, j \in \{ 1, \ldots, n \}$.
\end{definition}

\pause

From the skew-symmetrisable matrix associated to a cluster algebra of finite type, we can associate an diagram $\Gamma$ as follows:\\

For $i, j \in V(\Gamma)$, $i \xrightarrow{w} j$ if and only if $B_{ij}>0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge.

\end{frame}

\section{Background Results}

\subsection{Mutation Rules}

\begin{frame}{Mutation Rules}
\begin{proposition}
[Proposition 1.4, Barot-Marsh]
Let $B$ be a $2$-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows:
\begin{itemize}
\item Reverse the orientations of all edges in $\Gamma(B)$ incident with $k$ (leaving the weights unchanged)
\item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e. with $a,b$ positive), let $c$ be the weight on the edge $j \rightarrow i$, taken to be zero if there is no such arrow. Let $c'$ be determined by $c'\geq 0$ and 
$c+c' =$ max$(a,b)$. 
Then $\Gamma(B)$ changes in a predetermined way, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.

%%SHOW THE PREDETERMINED WAY ON THE BOARD
\end{itemize}
\end{proposition}

\end{frame}

\begin{frame}{Mutation Rules}
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{mutationrules.PNG}
\caption{Predetermined method for mutation at $k$}
\end{figure}
\end{frame}

\subsection{Chordless cycles underlying $\Gamma$}

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{proposition}
[Proposition 2.1, Barot-Marsh]
Any chordless cycle in $\Gamma$ must have an unoriented structure that is one of the following. Furthermore, it must be cyclically oriented.
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{chordlesscycles.PNG}
\caption{Possible chordless cycles in a diagram}
\end{figure}

\end{proposition}
\end{frame}

\section{Coxeter group presentation (Barot-Marsh)}

\begin{frame}
\begin{definition}
For a diagram $\Gamma$ and $i, j \in V(\Gamma)$, define 
\begin{displaymath}
m_{ij} = \begin{cases}    2 & \mbox{if } i \mbox{ and } j \mbox{ are not connected;} \\
																	3 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 1;\\
																	4 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 2;\\
																	6 & \mbox{if } i \mbox{ and } j \mbox{ are connected by an edge of weight } 3.\\
					\end{cases}
\end{displaymath}	
\end{definition}

This definition will allow us to present generator relations in the group $W_{\Gamma}$.
\end{frame}

\subsection{Generators and Relations}

\begin{frame}

Given a diagram $\Gamma$ of finite type, Barot and Marsh define the Coxeter group $W_{\Gamma}$ with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations:
\begin{block}

\begin{itemize}
\item{\alert{(R1)}} $s_i^2 = e$ for all $i$
\item{\alert{(R2)}} $\left(s_is_j\right)^{m_{ij}} = e$ for all $i \neq j$
\end{itemize}

Furthermore, for a chordless cycle $C : i_0 \rightarrow i_1 \rightarrow \cdots \rightarrow i_{d-1} \rightarrow i_0$ and for $a = 0,1,2,\ldots, d-1$, define \textbf{$r\left(i_a, i_{a+1}\right) = s_{i_a}s_{i_{a+1}} \cdots s_{i_{a+d-1}}s_{i_{a+d-2}} \cdots s_{i_{a+1}}$}.\\

\vspace{0.1cm}
Then we have the following relations:
\begin{itemize}
\item{\alert{(R3)(a)}} If all the weights in the edges of $C$ are $1$, then $r(i_a, i_{a+1})^2 = e$
\item{\alert{(R3)(b)}} If $C$ has some edges of weight $2$, then $r(i_a, i_{a+1})^k = e$ where $k = 4-w_a$ and $w_a$ is the weight of the edge $i_a\--\ i_{a-1}$
\end{itemize}
\end{block}
\end{frame}

\subsection{Invariance under Mutation Equivalence}

\begin{frame}
Given a diagram $\Gamma$ and the corresponding Coxeter group $W_{\Gamma}$, Barot and Marsh prove that this group is invariant (up to isomorphism) under mutation of $\Gamma$.

\begin{theorem}
[Theorem 5.4, Barot-Marsh]
\begin{enumerate}
\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
\item Let $\mathscr{A}$ be a cluster algebra of finite type. Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
\end{enumerate}
\end{theorem}
\end{frame}

\section{Artin group presentation (HHLP)}

\begin{frame}
\begin{block}

Let
\begin{align*}
\langle x_i,x_j \rangle ^k = \begin{cases}
(x_ix_j)^{\frac{k}{2}}, &\text{ if }k \equiv 0 \pmod 2\\
(x_ix_j)^{\frac{k-1}{2}}x_i &\text{ if } k \equiv 1 \pmod 2
\end{cases}
\end{align*}
That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k$.  We also write $\langle x_i,x_j\rangle^{-k}$ to denote $\left(\langle x_i,x_j\rangle^k\right)^{-1}$.
\end{block}

\begin{block}

Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}}.$$
\end{block}

\end{frame}
\begin{frame}
Now we have 
\begin{align*}
\langle x_i,x_j \rangle ^k = \begin{cases}
(x_ix_j)^{\frac{k}{2}}, &\text{ if }k \equiv 0 \pmod 2\\
(x_ix_j)^{\frac{k-1}{2}}x_i &\text{ if } k \equiv 1 \pmod 2
\end{cases}
\end{align*}
And $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}}.$$

Additionally, let $$t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1})  s_{i_a}^{-1}p(i_a,i_{a+1})^{-1}.$$

These definitions will allow us to present generator relations in the group $A_{\Gamma}$.

\end{frame}

\subsection{Generators and Relations}

\begin{frame}
Given a diagram $\Gamma$ of finite type, we define the Artin group $A_{\Gamma}$ with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations (noting that $t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1})  s_{i_a}^{-1}p(i_a,i_{a+1})^{-1}$):

\begin{block}

\begin{itemize}

\item{\alert{(T2)}} With $m_{ij}$ as defined previously, for all $i \neq j,$ we add the relations
$\langle s_i,s_j \rangle^{m_{ij}}= \langle s_j,s_i \rangle^{m_{ij}}.$

\item{\alert{(T3)}} Let $(i_0,i_1,\ldots,i_{d-1})$ be an ordered tuple as before. If additionally one of the following two conditions hold:
\begin{enumerate}
\item All edges in the chordless cycle are of weight 1 or 2 and the edge $i_{d-1}\rightarrow i_0$ has weight 2.
\item All edges in the chordless cycle have weight $1.$
\end{enumerate}
then we include the relation
$t(i_0,i_1) = e.$

\end{itemize}

\end{block}

\end{frame}

\begin{frame}
\begin{rem}
Each Artin group has an associated Coxeter group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type. To each Artin group of finite type we can assign it the same Dynkin diagram which is assigned to the Coxeter group associated to the Artin group.
\end{rem}
\end{frame}

\subsection{Invariance under Mutation Equivalence}

\begin{frame}
Given a diagram $\Gamma$ and the corresponding Artin group $A_{\Gamma}$, we prove this group is invariant (up to isomorphism) under mutation of $\Gamma$.

\begin{theorem}
Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$. Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$.
\end{theorem}
\end{frame}

\section{Jacob}

\begin{frame}{Unoriented structures underlying $\Gamma$}
\begin{lemma}
[Lemma 2.2, Barot-Marsh]
For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .65]{3vertconnected.PNG}
\caption{Unoriented 3-vertex connected subdiagrams}
\end{figure}
\end{lemma}

\end{frame}

\subsection{Possible mutations for 3-cycles in $\Gamma$}

\begin{frame}{Possible mutations for $i\--\ k\--\ j$}
\begin{corollary}
[Corollary 2.3, Barot-Marsh]
If in $\Gamma$ we have $i,j,k \in V(\Gamma), i \neq k \neq j$, and we have $i\--\ k\--\ j$, then the only possible mutations for this connected path between the three vertices are the following:
\begin{figure}[h]
\centering
\includegraphics[scale = .40]{mutation3path.PNG}
\caption{Mutation of three connected vertices}
\end{figure}
\end{corollary}
\end{frame}

\begin{frame}
\begin{thebibliography}{69}

\bibitem{BM}[1] Barot, M. and Marsh, R., Reflection Group Presentations Arising from Cluster Algebras, \emph{Preprint}, arXiv:1112.2300 (2011)

\end{thebibliography}

\end{frame}

\end{document}

### 2014-08-03 Presentation/Prob6.tex

--- 2014-08-03 Presentation/Presentation/Prob6.tex
@@
 \newtheorem{rem}{Remark}
-\newtheorem{goal}{Goal}
+\newtheorem{question}{REU Problem}
 
@@
   \titlepage
-  \let\thefootnote\relax\footnote{* denotes speaker}
 \end{frame}
@@
 
-\begin{frame}{Brief History}
-Fomin and Zelevinsky introduced \textit{cluster algebras}, generated from seed variables.
-These algebras are of finite type if they are generated from a finite number of seeds.
-Fomin and Zelevinsky also showed that cluster algebras of finite type can be classified by Dynkin diagrams.
-\begin{figure}
-\centering
-\includegraphics[scale = .25]{dynkindiagrams.PNG}
-\caption{Dynkin diagrams}
-\end{figure}
-\end{frame}
-
-\begin{frame}{Example}
-\begin{figure}
-\centering
-\includegraphics[scale = .65]{DynkinA3.PNG}
-\caption{Dynkin diagram of type $A_3$}
-\end{figure}
-
-Coxeter group relations:
-\begin{itemize}
-\item $s_1^2 = s_2^2 = s_3^2 = e$
-\item $(s_1s_2)^3 = (s_2s_3)^3 = e$
-\item $(s_1s_3)^2 = e$
-\end{itemize}
-
-Artin group relations:
-\begin{itemize}
-\item $\langle s_1, s_2 \rangle ^3 = \langle s_2, s_1 \rangle ^3$
-\item $\langle s_2, s_3 \rangle ^3 = \langle s_3, s_2 \rangle ^3$
-\item $\langle s_1, s_3 \rangle ^2 = \langle s_3, s_1 \rangle ^2$
-\end{itemize}
-Alternatively, the above relations correspond to 
-\begin{itemize}
-\item $s_1s_2s_1 = s_2s_1s_2$
-\item $s_2s_3s_2 = s_3s_2s_3$
-\item $s_1s_3 = s_3s_1$
-\end{itemize}
-
-\end{frame}
-
-\begin{frame}
-Barot and Marsh extended the Coxeter group presentations to diagrams of finite type (making an allowance for chordless cycles), and proved that this group presentation is isomorphic to the Coxeter group associated to a Dynkin diagram.
-They also proved mutation invariance, up to isomorphism, for these Coxeter groups.
-
-\pause
-\begin{goal}
+\begin{frame}{REU Problem 6}
+\begin{question}
 Develop variations of relations for the Coxeter group associated to a diagram of finite type provided in Barot-Marsh to define the Artin group $A_{\Gamma}$ corresponding to a diagram $\Gamma$.
 Prove that for $\Gamma^{\prime} = \mu_k(\Gamma)$, we get $A_{\Gamma} \cong A_{\Gamma^{\prime}}$.
-\end{goal}
+\end{question}
 \end{frame}
@@
 \begin{proposition}
-[Proposition 1.4, Barot-Marsh]
+\cite[Proposition 1.4]{BM}
 Let $B$ be a $2$-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows:
@@
 
-\subsection{Chordless cycles underlying $\Gamma$}
+\subsection{Unoriented structures underlying $\Gamma$}
 
@@
 \begin{proposition}
-[Proposition 2.1, Barot-Marsh]
+\cite[Proposition 2.1]{BM}
 Any chordless cycle in $\Gamma$ must have an unoriented structure that is one of the following. Furthermore, it must be cyclically oriented.
@@
 
-\section{Coxeter group presentation (Barot-Marsh)}
+\begin{frame}{Unoriented structures underlying $\Gamma$}
+\begin{lemma}
+\cite[Lemma 2.2]{BM}
+For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
+\begin{figure}[h]
+\centering
+\includegraphics[scale = .65]{3vertconnected.PNG}
+\caption{Unoriented 3-vertex connected subdiagrams}
+\end{figure}
+\end{lemma}
+
+\end{frame}
+
+\subsection{Possible mutations for 3-cycles in $\Gamma$}
+
+\begin{frame}{Possible mutations for $i\--\ k\--\ j$}
+\begin{corollary}
+\cite[Corollary2.3]{BM}
+If in $\Gamma$ we have $i,j,k \in V(\Gamma), i \neq k \neq j$, and we have $i\--\ k\--\ j$, then the only possible mutations for this connected path between the three vertices are the following:
+\begin{figure}[h]
+\centering
+\includegraphics[scale = .40]{mutation3path.PNG}
+\caption{Mutation of three connected vertices}
+\end{figure}
+\end{corollary}
+\end{frame}
+
+\section{$W_{\Gamma}$  presentation}
 
@@
 \begin{theorem}
-[Theorem 5.4, Barot-Marsh]
+\cite[Theorem 5.4]{BM} 
 \begin{enumerate}
@@
 
-\section{Artin group presentation (HHLP)}
+\section{$A_{\Gamma}$ presentation}
 
@@
 
-\section{Jacob}
-
-\begin{frame}{Unoriented structures underlying $\Gamma$}
-\begin{lemma}
-[Lemma 2.2, Barot-Marsh]
-For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
-\begin{figure}[h]
-\centering
-\includegraphics[scale = .65]{3vertconnected.PNG}
-\caption{Unoriented 3-vertex connected subdiagrams}
-\end{figure}
-\end{lemma}
-
-\end{frame}
-
-\subsection{Possible mutations for 3-cycles in $\Gamma$}
-
-\begin{frame}{Possible mutations for $i\--\ k\--\ j$}
-\begin{corollary}
-[Corollary 2.3, Barot-Marsh]
-If in $\Gamma$ we have $i,j,k \in V(\Gamma), i \neq k \neq j$, and we have $i\--\ k\--\ j$, then the only possible mutations for this connected path between the three vertices are the following:
-\begin{figure}[h]
-\centering
-\includegraphics[scale = .40]{mutation3path.PNG}
-\caption{Mutation of three connected vertices}
-\end{figure}
-\end{corollary}
-\end{frame}
-
 \begin{frame}

### 2014-08-03 Presentation/Prob6.tex
Revert "Updated beamer"
This reverts commit d38ecf4a1ba4eb9efaaa745f829e64a12a978cd2.

@@
 \usepackage[english]{babel}
-%\usepackage[utf8x]{inputenc}
+\usepackage[utf8x]{inputenc}
 \usepackage{mathrsfs}
@@
 \newtheorem{rem}{Remark}
-\newtheorem{question}{REU Problem}
+\newtheorem{question}{Question}
 
@@
 \begin{proposition}
-\cite[Proposition 1.4]{BM}
+%%CITE BAROT MARSH PROP 1.4
+%\alert{Proposition 1.4}
 Let $B$ be a $2$-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows:
@@
 \begin{proposition}
-\cite[Proposition 2.1]{BM}
+%%CITE \alert{Proposition 2.1}
 Any chordless cycle in $\Gamma$ must have an unoriented structure that is one of the following. Furthermore, it must be cyclically oriented.
@@
 \begin{lemma}
-\cite[Lemma 2.2]{BM}
+%CITE \alert{Lemma 2.2}
 For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
@@
 \begin{corollary}
-\cite[Corollary2.3]{BM}
+%CITE \alert{Corollary 2.3}
 If in $\Gamma$ we have $i,j,k \in V(\Gamma), i \neq k \neq j$, and we have $i\--\ k\--\ j$, then the only possible mutations for this connected path between the three vertices are the following:
@@
 \begin{theorem}
-\cite[Theorem 5.4]{BM} 
+%CITE \alert{Theorem 5.4} 
 \begin{enumerate}
@@
 
-Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}}.$$
+Let $(i_0,\ldots, i_{d-1})$ be an ordered tuple such that the subgraph of $\Gamma$ on the vertices $i_0,\ldots, i_{d-1}$ is a chordless cycle, with edges of nonzero weight from $i_k$ to $i_{k+1}$, where subscripts are taken $\pmod d.$ Then, denote $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}} s_{i_{a}}^{-1}.$$
 \end{block}
@@
 \end{align*}
-And $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}}.$$
+And $$p(i_a,i_{a+1}) = s_{i_{a+1}}^{-1}s_{i_{a+2}}^{-1}\dots s_{i_{a-2}}^{-1}s_{i_{a-1}}s_{i_{a-2}}s_{i_{a-3}}\dots s_{i_{a+1}} s_{i_{a}}^{-1}.$$
 
-Additionally, let $$t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1})  s_{i_a}^{-1}p(i_a,i_{a+1})^{-1}.$$
+Additionally, let $$t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1}) p(i_a,i_{a+1})^{-1} s_{i_a}^{-1}.$$
 
@@
 \begin{frame}
-Given a diagram $\Gamma$ of finite type, we define the Artin group $A_{\Gamma}$ with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations (noting that $t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1})  s_{i_a}^{-1}p(i_a,i_{a+1})^{-1}$):
+Given a diagram $\Gamma$ of finite type, we define the Artin group $A_{\Gamma}$ with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations:
 
@@
 
-\begin{frame}
-\begin{thebibliography}{69}
-
-\bibitem{BM}[1] Barot, M. and Marsh, R., Reflection Group Presentations Arising from Cluster Algebras, \emph{Preprint}, arXiv:1112.2300 (2011)
-
-\end{thebibliography}
-
-\end{frame}
-
 \end{document}

### 2014-08-04 Presentation/Prob6.tex
Added example for Artin vs coxeter
Presentation Slides and Diagrams

--- 2014-08-03 Presentation/Presentation/Prob6.tex
@@
 \newtheorem{goal}{Goal}
+\newtheorem{Conjecture}{Conjecture}
 
@@
 \end{block}
+\end{frame}
 
+\begin{frame}{Example}
+\begin{figure}
+\centering
+\includegraphics[scale=.5]{4cycle.PNG}
+\caption{A 4 cycle with edge weights of 1 and 2}
+\end{figure}
+
+\small
+Coxeter relations:
+\begin{itemize}
+\item[R1] $s_1^2 = s_2^2 = s_3^2 = s_4^2 = e$
+\item[R2] $(s_1s_2)^3 = (s_3s_4)^3 = e$
+\item[R2] $(s_2s_3)^4 = (s_4s_1)^4 = e$
+\item[R2] $(s_1s_3)^2 = (s_2s_4)^2 = e$
+\item[R3] $r(1,2)^2 = r(3,4)^2 = e$, or $(s_1s_2s_3s_4s_3s_2)^2 = (s_3s_4s_1s_2s_1s_4)^2 = e$
+\item[R3] $r(2,3)^3 = r(4,1)^3 = e$, or $(s_2s_3s_4s_1s_4s_3)^3 = (s_4s_1s_2s_3s_2s_1)^3 = e$
+\end{itemize}
+\end{frame}
+
+\begin{frame}{Example}
+\begin{figure}
+\centering
+\includegraphics[scale=.5]{4cycle.PNG}
+\caption{A 4 cycle with edge weights of 1 and 2}
+\end{figure}
+
+\small
+Artin relations:
+\begin{itemize}
+\item[T2] $\langle s_1, s_2 \rangle ^3 = \langle s_2, s_1 \rangle ^3$, or $s_1s_2s_1 = s_2s_1s_2$
+\item[T2] $\langle s_2, s_3 \rangle ^4 = \langle s_3, s_2 \rangle ^4$, or $s_2s_3s_2s_3 = s_3s_2s_3s_2$
+\item[T2] $\langle s_2, s_4 \rangle ^2 = \langle s_4, s_2 \rangle ^2$, or $s_2s_4 = s_4s_2$
+\end{itemize}
+The T2 relations $\langle s_3, s_4 \rangle, \langle s_4, s_1 \rangle, \langle s_1, s_3 \rangle$ can be defined in a similar manner.
+\begin{itemize}
+\item[T3] $t(1,2) = s_1s_2^{-1}s_3^{-1}s_4s_3s_2s_1^{-1}s_2^{-1}s_3^{-1}s_4^{-1}s_3s_2 = e$, or $s_1s_2^{-1}s_3^{-1}s_4s_3s_2 = s_2^{-1}s_3^{-1}s_4s_3s_2s_1$.
+\end{itemize}
+
+The T3 relation $t(3,4) = e$ can be defined in a similar manner.
 \end{frame}
@@
 
-\section{Jacob}
+\section{Constructing the Isomorphism}
+
+\begin{frame}
+In constructing the isomorphsim between $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we first prove that $A_{\Gamma} \cong A_{\Gamma^{op}}$, where $\Gamma^{op}$ is the diagram obtained by reversing all arrows in $\Gamma$.
+\begin{lemma}
+Let A$_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$, and let A$_{\Gamma^{op}}$ be generated by $r_{1}, \dots, r_{n}$.
+Then the map $$\Delta: s_{i} \rightarrow r_{i}^{-1}$$ defines an isomorphism between A$_{\Gamma}$ and A$_{\Gamma^{op}}.$
+\end{lemma}
+\end{frame}
+
+\begin{frame}
+Now let $A_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$ and let $A_{\Gamma^{\prime}}$ be generated by $u_{1}, \dots, u_{n}$.
+Consider the map $\phi: A_{\Gamma^{\prime}} \rightarrow A_{\Gamma}$ defined as follows:
+$$\phi(u_{i}) = 
+\begin{cases}
+s_{k}s_{i}s_{k}^{-1} &\text{if there is an arrow from i to k in $\Gamma$} \\
+s_{i} &\text{otherwise}
+\end{cases}$$
+
+\begin{lemma}
+The map $\phi$ is a well-defined homomomorphism.
+\end{lemma}
+\end{frame}
 
 \begin{frame}{Unoriented structures underlying $\Gamma$}
+In proving that the map is well-defined, we make use of the fact that diagrams of finite-type have a nice underlying structure. For example, when dealing with the (T2) relations, we have
 \begin{lemma}
 [Lemma 2.2, Barot-Marsh]
-For $\Gamma$, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
+For $\Gamma$ of finite-type, if we have a subdiagram of $\Gamma$ with three connected vertices, then the unoriented graph underlying the subdiagram must be one of the following:
 \begin{figure}[h]
@@
 \end{frame}
-
 \subsection{Possible mutations for 3-cycles in $\Gamma$}
@@
 \begin{frame}
+Now given the maps $\phi$ and $\Delta$, we are able to prove our theorem. Consider the diagram:
+\begin{figure}
+\includegraphics[scale = .50]{Comm-Diag.pdf}
+\end{figure}
+One can check that this diagram commutes, and so we find that the map $\phi$ is actually an isomorphism.
+\end{frame}
+
+\section{Affine Dynkin Diagrams}
+\begin{frame}
+It is natural to ask whether a similar result holds for diagrams that are not of finite type. In particular, we will examine diagrams which are mutation equivalent to affine Dynkin diagrams.
+\begin{figure}
+\includegraphics[scale = .50]{Affine-Diagrams.pdf}
+\caption{Affine Dynkin Diagrams}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+In a paper by Felickson and Tumarkin, the authors obtain a similar result for coxeter groups.
+For a diagram $\Gamma$ of affine type with n+1 nodes, they define a group W$_{\Gamma}$ generated by elements $s_{1}, \dots, s_{n+1}$ and subject to the following relations:
+
+(R1) $s_{i}^{2} = e$ for $i \in \{1, \dots, n\}$.
+
+(R2) $(s_{i}s_{j})^{m_{ij}} = e$ where 
+$$m_{ij} = 
+\begin{cases}
+2 &\text{if there is no arrow between i and j in $\Gamma$} \\
+3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
+4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
+6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
+\infty &\text{otherwise}
+\end{cases}$$
+\end{frame}
+
+\begin{frame}
+(R3) For every chordless oriented cycle:
+$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
+define for l $\in \{0, \dots, d-1\}$, 
+$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
+Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
+$$m(l) =
+\begin{cases}
+2 &\text{if $t(l)=0$} \\
+3 &\text{if $t(l)=1$} \\
+4 &\text{if $t(l)=2$} \\
+6 &\text{if $t(l)=3$}
+\end{cases}$$
+\end{frame}
+
+\begin{frame}
+(R4) To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram1.pdf}
+\end{figure}
+we add the relation $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$.
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form 
+\begin{figure}
+\includegraphics[scale = .50]{Diagram2.pdf}
+\end{figure}
+we add the relation $(s_{1}s_{2}s_{3}s_{2}s_{1}s_{4}s_{5} \dots s_{n}s_{n+1}s_{n} \dots s_{5}s_{4})^{2} = e$
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram3.pdf}
+\end{figure}
+we add the relations $(s_{2}s_{3}s_{4}s_{1}s_{4}s_{3})^{2} = e$ and $(s_{2}s_{1}s_{4}s_{3}s_{4}s_{1})^{2} = e$.
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram4.pdf}
+\end{figure}
+we add the relation $(s_{n+1}s_{1}s_{n+1}s_{2}s_{3} \dots s_{n-1}s_{n}s_{n-1} \dots s_{3}s_{2})^{2} = e$.
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram5.pdf}
+\end{figure}
+we add the relations $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$
+\end{frame}
+
+\begin{frame}
+\begin{theorem}[Felickson-Tumarkin]
+The group $W_{\Gamma}$ is invariant up to isomorphism under diagram mutation.
+\end{theorem}
+\end{frame}
+
+\begin{frame}
+In their paper, Felickson and Tumarkin show that all of the (R4) relations are necessary for this theorem to be true.
+For example, consider the mutation of \includegraphics[scale = .30]{Diagram2.pdf} at the vertex 1, which is the diagram
+\begin{figure}
+\includegraphics[scale = .30]{Diagram6.pdf}
+\end{figure}
+\end{frame}
+
+\begin{frame}
+Let $\Gamma$ be a diagram of affine type on n+1 nodes. Then we define $A_{\Gamma}$ to be the group generated by $s_{1}, \dots, s_{n+1}$ satisfying the relations
+
+(T2) $\langle s_{i}, s_{j} \rangle^{m_{ij}} = \langle s_{j}, s_{i} \rangle^{m_{ij}}$ where
+$$m_{ij} = 
+\begin{cases}
+2 &\text{if there is no arrow between i and j in $\Gamma$} \\
+3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
+4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
+6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
+\infty &\text{otherwise}
+\end{cases}$$
+\end{frame}
+
+\begin{frame}
+(T3)  For every chordless oriented cycle:
+$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
+define for l $\in \{0, \dots, d-1\}$, 
+$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
+Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
+$$m(l) =
+\begin{cases}
+2 &\text{if $t(l)=0$} \\
+3 &\text{if $t(l)=1$} \\
+4 &\text{if $t(l)=2$} \\
+6 &\text{if $t(l)=3$}
+\end{cases}$$
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram1.pdf}
+\end{figure}
+we add the relation $(s_{2}s_{1}s_{2}^{-1})s_{3}^{-1}s_{4}s_{3} = s_{3}^{-1}s_{4}s_{3}(s_{2}s_{1}s_{2}^{-1}).$
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram2.pdf}
+\end{figure}
+we add the relation
+$s_{2}(s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}(s_{1}s_{n+1}s_{1}^{-1})s_{n} \dots s_{4}s_{3})$
+\newline $= (s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}(s_{1}s_{n+1}s_{1}^{-1})s_{n} \dots s_{4}s_{3})s_{2}$
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram3.pdf}
+\end{figure}
+we add the relations $s_{2}s_{3}^{-1}(s_{4}s_{1}s_{4}^{-1})s_{3} = s_{3}^{-1}(s_{4}s_{1}s_{4}^{-1})s_{3}s_{2}$ and \\
+$s_{2}s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1} = s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1}s_{2}$.
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram4.pdf}
+\end{figure}
+we add the relation $s_{1}(s_{2}^{-1} \dots s_{n-1}^{-1}(s_{n+1}s_{n}s_{n+1}^{-1})s_{n-1} \dots s_{2}) = (s_{2}^{-1} \dots s_{n-1}^{-1}(s_{n+1}s_{n}s_{n+1}^{-1})s_{n-1} \dots s_{2})s_{1}$.
+\end{frame}
+
+\begin{frame}
+To a subdiagram of the form
+\begin{figure}
+\includegraphics[scale = .50]{Diagram5.pdf}
+\end{figure}
+we add the relations $s_{2}s_{1}^{-1}(s_{2}s_{3}s_{2}^{-1})s_{1} = s_{1}^{-1}(s_{2}s_{3}s_{2}^{-1})s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$.
+\end{frame}
+
+\begin{frame}
+\begin{Conjecture}
+$A_{\Gamma}$ is invariant up to isomorphism under diagram mutation.
+\end{Conjecture}
+\end{frame}
+
+\begin{frame}
 \begin{thebibliography}{69}

### 2014-08-05 Presentation/Prob6.tex
deleted remark slide

@@
 
-\begin{frame}
-\begin{rem}
-Each Artin group has an associated Coxeter group defined by adding in the additional relations $s_i^2 = 1$ for all $i.$ An Artin group is said to be of {\it finite type} if its associated Coxeter group is of finite type.
-To each Artin group of finite type we can assign it the same Dynkin diagram which is assigned to the Coxeter group associated to the Artin group.
-\end{rem}
-\end{frame}
-
 \subsection{Invariance under Mutation Equivalence}
@@
 \begin{frame}
-In constructing the isomorphsim between $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we first prove that $A_{\Gamma} \cong A_{\Gamma^{op}}$, where $\Gamma^{op}$ is the diagram obtained by reversing all arrows in $\Gamma$.
+In constructing the isomorphism between $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we first prove that $A_{\Gamma} \cong A_{\Gamma^{op}}$, where $\Gamma^{op}$ is the diagram obtained by reversing all arrows in $\Gamma$.
 \begin{lemma}

### 2014-08-05 Presentation/Prob6.tex
Made Small Edit to Conjecture in Presentation
edits from practice today

@@
 Fomin and Zelevinsky introduced \textit{cluster algebras}, generated from seed variables.
-These algebras are of finite type if they are generated from a finite number of seeds.
+These algebras are of finite type if they are generated from a finite number of cluster variables.
 Fomin and Zelevinsky also showed that cluster algebras of finite type can be classified by Dynkin diagrams.
@@
 \begin{itemize}
-\item $s_1^2 = s_2^2 = s_3^2 = e$
-\item $(s_1s_2)^3 = (s_2s_3)^3 = e$
-\item $(s_1s_3)^2 = e$
+\item $s_i^2 = e$ :  $s_1^2 = s_2^2 = s_3^2 = e$ 
+\item $(s_is_j)^{m_{ij}} = e$ :  $(s_1s_2)^3 = (s_2s_3)^3 = e$
+\item  $(s_is_j)^{m_{ij}} = e$ :  $(s_1s_3)^2 = e$
 \end{itemize}
@@
 Artin group relations:
-\begin{itemize}
-\item $\langle s_1, s_2 \rangle ^3 = \langle s_2, s_1 \rangle ^3$
-\item $\langle s_2, s_3 \rangle ^3 = \langle s_3, s_2 \rangle ^3$
-\item $\langle s_1, s_3 \rangle ^2 = \langle s_3, s_1 \rangle ^2$
-\end{itemize}
-Alternatively, the above relations correspond to 
 \begin{itemize}
@@
 \begin{frame}
-Barot and Marsh extended the Coxeter group presentations to diagrams of finite type (making an allowance for chordless cycles), and proved that this group presentation is isomorphic to the Coxeter group associated to a Dynkin diagram.
-They also proved mutation invariance, up to isomorphism, for these Coxeter groups.
+Barot and Marsh extended the Coxeter group presentations to diagrams of finite type (making an allowance for chordless cycles).
+\begin{theorem}
+[Theorem 5.4, Barot-Marsh]
+\begin{enumerate}
+\item Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $W_{\Gamma} \cong W_{\Gamma^{\prime}}$.
+\item Let $\mathscr{A}$ be a cluster algebra of finite type.
+Then the groups $W_{\Gamma}$ associated to the diagrams $\Gamma$ arising from the seeds of $\mathscr{A}$ are all isomorphic (to the reflection group associated to the Dynkin diagram associated to $\mathscr{A}$).
+\end{enumerate}
+\end{theorem}
 
 \pause
-\begin{goal}
-Develop variations of relations for the Coxeter group associated to a diagram of finite type provided in Barot-Marsh to define the Artin group $A_{\Gamma}$ corresponding to a diagram $\Gamma$.
-Prove that for $\Gamma^{\prime} = \mu_k(\Gamma)$, we get $A_{\Gamma} \cong A_{\Gamma^{\prime}}$.
-\end{goal}
+\begin{theorem}{(HHLP, 14)}
+ Let $\Gamma$ be a diagram of finite type and $\Gamma^{\prime} = \mu_k(\Gamma)$ the mutation of $\Gamma$ at vertex $k$. Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$. 
+\end{theorem}
 \end{frame}
@@
 \begin{definition}
-We say a matrix $B$ is \textit{skew-symmetrisable} if there exists a diagonal matrix $D$ of the same size such that $|D_{ii}|>0$ and $DB$ is skew-symmetric.
+We say a matrix $B$ is \textit{skew-symmetrisable} if there exists a diagonal matrix $D$ of the same size such that $D_{ii}>0$ and $DB$ is skew-symmetric.
 \end{definition}
@@
 \begin{proposition}
-[Proposition 2.1, Barot-Marsh]
+[Proposition 9.7, Fomin-Zelevinsky II]
 Any chordless cycle in $\Gamma$ must have an unoriented structure that is one of the following. Furthermore, it must be cyclically oriented.
@@
 
+\begin{frame}
+\tableofcontents 
+\end{frame}
+
 \section{Coxeter group presentation (Barot-Marsh)}
 
-\begin{frame}
+\begin{frame}{Coxeter group presentation}
 \begin{definition}
@@
 
-\begin{frame}
+\begin{frame}{Coxeter group presentation}
 
@@
 
-\begin{frame}
+\begin{frame}{Coxeter group invariance}
 Given a diagram $\Gamma$ and the corresponding Coxeter group $W_{\Gamma}$, Barot and Marsh prove that this group is invariant (up to isomorphism) under mutation of $\Gamma$.
@@
 
-\section{Artin group presentation (HHLP)}
+\section{Artin group presentation (HHLP, 14)}
 
-\begin{frame}
+\begin{frame}{Artin group presentation}
 \begin{block}
@@
 \end{align*}
-That is, $\langle x_i,x_j \rangle$ is just an alternating sequence of $x_i$ and $x_j$ of length $k$.
-We also write $\langle x_i,x_j\rangle^{-k}$ to denote $\left(\langle x_i,x_j\rangle^k\right)^{-1}$.
 \end{block}
@@
 \end{frame}
-\begin{frame}
+\begin{frame}{Artin group presentation}
 Now we have 
@@
 
-\begin{frame}
+\begin{frame}{Artin group presentation}
 Given a diagram $\Gamma$ of finite type, we define the Artin group $A_{\Gamma}$ with generators $s_i, i = 1,2,\ldots, n$, subject to the following relations (noting that $t(i_a,i_{a+1}) = s_{i_a} p(i_a,i_{a+1})  s_{i_a}^{-1}p(i_a,i_{a+1})^{-1}$):
@@
 
-\begin{frame}
+\begin{frame}{Artin group invariance}
 Given a diagram $\Gamma$ and the corresponding Artin group $A_{\Gamma}$, we prove this group is invariant (up to isomorphism) under mutation of $\Gamma$.
 
-\begin{theorem}
+\begin{theorem}{(HHLP, 14)}
 Let $\Gamma$ be a diagram of finite type, and let $\Gamma^{\prime} = \mu_k(\Gamma)$ be the mutation of $\Gamma$ at vertex $k$. Then $A_{\Gamma} \cong A_{\Gamma^{\prime}}$.
@@
 \end{figure}
-we add the relation $(s_{2}s_{1}s_{2}^{-1})s_{3}^{-1}s_{4}s_{3} = s_{3}^{-1}s_{4}s_{3}(s_{2}s_{1}s_{2}^{-1}).$
+we add the relation $(s_{2}s_{1}s_{2}^{-1})s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}(s_{2}s_{1}s_{2}^{-1}).$
 \end{frame}
@@
 \bibitem{BM}[1] Barot, M. and Marsh, R., Reflection Group Presentations Arising from Cluster Algebras, \emph{Preprint}, arXiv:1112.2300 (2011)
+\bibitem{FZ}[2] Fomin, S. and Zelevinsky, A., Cluster Algebras I. Foundations, \emph{J. Amer. Math. Soc.}, \textbf{15} (2002), 497-529.
+\bibitem{FZ}[3] Fomin, S. and Zelevinsky, A., Cluster Algebras II. Finite type classification, \emph{Invent. Math.}, \textbf{154} (2003), 63-121.
 

### 2014-08-06 Presentation/Prob6.tex
Edits to Presentation

@@
 
-\begin{frame}
-In constructing the isomorphism between $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we first prove that $A_{\Gamma} \cong A_{\Gamma^{op}}$, where $\Gamma^{op}$ is the diagram obtained by reversing all arrows in $\Gamma$.
+\begin{frame}{Constructing the Isomorphism}
+To prove this theorem, our strategy will be to construct homomorphisms so that the following diagram commutes.
+\begin{figure}
+\includegraphics[scale = .50]{Comm-Diag.pdf}
+\end{figure}
+Then the map $\phi$ will give us the desired isomorphism.
+\end{frame}
+
+\begin{frame}{Constructing the Isomorphism}
+We first prove that $A_{\Gamma} \cong A_{\Gamma^{op}}$, where $\Gamma^{op}$ is the diagram obtained by reversing all arrows in $\Gamma$.
 \begin{lemma}
@@
 
-\begin{frame}
+\begin{frame}{Constructing the Isomorphism}
 Now let $A_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$ and let $A_{\Gamma^{\prime}}$ be generated by $u_{1}, \dots, u_{n}$.
@@
 
-\begin{frame}
-Now given the maps $\phi$ and $\Delta$, we are able to prove our theorem. Consider the diagram:
+\begin{frame}{Sketch of Proof of the Main Theorem}
+Now consider the diagram:
 \begin{figure}
@@
 \end{figure}
-One can check that this diagram commutes, and so we find that the map $\phi$ is actually an isomorphism.
+One can check that this diagram commutes, and so we find that the map $\phi$ is actually an isomorphism, which proves our theorem.
 \end{frame}
@@
 \section{Affine Dynkin Diagrams}
-\begin{frame}
+\begin{frame}{Extending Result to Other Diagrams}
 It is natural to ask whether a similar result holds for diagrams that are not of finite type. In particular, we will examine diagrams which are mutation equivalent to affine Dynkin diagrams.
@@
 
-\begin{frame}
+\begin{frame}{Extending the Barot-Marsh Presentation}
 In a paper by Felickson and Tumarkin, the authors obtain a similar result for coxeter groups.
@@
 
-\begin{frame}
+\begin{frame}{Extending the Barot-Marsh Presentation}
 (R3) For every chordless oriented cycle:
@@
 
-\begin{frame}
+\begin{frame}{Extending the Barot-Marsh Presentation}
 (R4) To a subdiagram of the form
@@
 
-\begin{frame}
+\begin{frame}{Extending the Barot-Marsh Presentation}
 To a subdiagram of the form 
@@
 
-\begin{frame}
+\begin{frame}{Extending the Barot-Marsh Presentation}
 To a subdiagram of the form
@@
 
-\begin{frame}
+\begin{frame}{Purpose of (R4) Relations}
 In their paper, Felickson and Tumarkin show that all of the (R4) relations are necessary for this theorem to be true.
@@
 
-\begin{frame}
+\begin{frame}{Extending our Artin Group Presentations}
 Let $\Gamma$ be a diagram of affine type on n+1 nodes. Then we define $A_{\Gamma}$ to be the group generated by $s_{1}, \dots, s_{n+1}$ satisfying the relations
@@
 
-\begin{frame}
+\begin{frame}{Extending our Artin Group Presentations}
 (T3)  For every chordless oriented cycle:
@@
 
-\begin{frame}
-To a subdiagram of the form
+\begin{frame}{Extending our Artin Group Presentations}
+(T4) To a subdiagram of the form
 \begin{figure}
@@
 
-\begin{frame}
+\begin{frame}{Extending our Artin Group Presentations}
 To a subdiagram of the form
@@
 \bibitem{BM}[1] Barot, M. and Marsh, R., Reflection Group Presentations Arising from Cluster Algebras, \emph{Preprint}, arXiv:1112.2300 (2011)
-\bibitem{FZ}[2] Fomin, S. and Zelevinsky, A., Cluster Algebras I. Foundations, \emph{J. Amer. Math. Soc.}, \textbf{15} (2002), 497-529.
-\bibitem{FZ}[3] Fomin, S. and Zelevinsky, A., Cluster Algebras II. Finite type classification, \emph{Invent. Math.}, \textbf{154} (2003), 63-121.
+\bibitem{FT}[2] Felikson, A. and Tumarkin, P., Coxeter groups and their quotients arising from cluster algebras, \emph{Preprint}, arXiv{1307.0672} (2013)
+\bibitem{FZ}[3] Fomin, S. and Zelevinsky, A., Cluster Algebras I. Foundations, \emph{J. Amer. Math. Soc.}, \textbf{15} (2002), 497-529.
+\bibitem{FZ}[4] Fomin, S. and Zelevinsky, A., Cluster Algebras II. Finite type classification, \emph{Invent. Math.}, \textbf{154} (2003), 63-121.
 

### 2014-08-07 Paper.tex
changed coxeter to lowercase c

--- 2014-08-01 Paper.tex
@@
 In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin group associated to a finite type diagram.
-This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
+This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to Coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
 

### 2014-08-08 Paper.tex
fixed intro and address
My computer doesn't like some of the packages so I am only updating the
tex file...if someone could compile the pdf that would be great

--- 2014-08-01 Paper.tex
@@
 
-\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
+%\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
 %\def\ltblue{blue!20!white}
@@
 \address{you can put addresses for authors\\
-here \\
-Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556}
+ \\
+Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556 \\
+Hailee: 1184 W Main St; Decatur, IL 62522 }
 \email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
@@
 
-In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras in order to make further strides in the areas of representation theory, Lie theory, and total positivity.
-Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations.
-Of particular interest were \textit{finite type} cluster algebras, that is, cluster algebras whose variables are generated through mutation on a finite number of \textit{seeds}.
-In the sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3.
-In particular, this proves that finite type cluster algebras can be classified by Dynkin diagrams.
-\\
-\indent Barot and Marsh extended Fomin and Zelevinsky's results in \cite{BM13}, providing a presentation of the reflection group associated to a Dynkin diagram with generators that correspond to elements of a companion basis associated to a seed of a finite type cluster algebra.
-They also proved that this group presentation is invariant up to isomorphism under the mutation equivalence relation.That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
+In \cite{FZ02}, Fomin and Zelevinsky first introduced the concept of cluster algebras.
+Barot and Marsh extended Fomin and Zelevinsky's results in \cite{BM13}, providing a presentation of the reflection group associated to a Dynkin diagram with generators that correspond to elements of a companion basis associated to a seed of a finite type cluster algebra.
+They define generator relations corresponding to chordless cycles arising in diagrams of finite type in order to give a Coxeter group presentation for these diagrams.
+They also proved that this Coxeter group presentation is invariant up to isomorphism under the mutation equivalence relation.That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
 
@@
 
+The initial introduction of cluster algebras by Fomin and Zelevinsky was aimed at making further strides in the areas of representation theory, Lie theory, and total positivity.
+Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations.
+Of particular interest were \textit{finite type} cluster algebras.
+In the sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3.
+In particular, this proves that finite type cluster algebras can be classified by Dynkin diagrams.
+\\
 A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations.

### 2014-08-12 Paper.tex
added acknowledgements

@@
 
+\section{Acknowledgements}
+
+We would like to thank Gregg Musiker for mentoring this project as well as Emily Gunawan for carefully reading over the paper and suggesting many helpful improvements.
+Additional thanks goes to Vic Reiner for suggesting the problem.
+This research was supported by the RTG grant NSF/DMS-1148634. We thank the University of Minnesota School of Mathematics for hosting us.
+
 \bibliography{References}

### 2014-08-12 Paper.tex

--- 2014-08-08 Paper.tex
@@
 \begin{align*}
-A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}}\forall i,j \text{ with } M_{i,j}<\infty \rangle,
+A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}} = \langle x_j,x_i \rangle^{M_{i,j}} \forall i,j \text{ with } M_{i,j}<\infty \rangle,
 \end{align*}
@@
 \end{rem}
+
+One of the most well-known Artin groups is the braid group on n strands, which was shown to have an Artin group structure in \cite{FN61}. The associated Coxeter group is the symmetric group $S_{n}$.
 
@@
 
+\section{Acknowledgements}
+\thanks{This work was supported by the RTG grant NSF/DMS-1148634.
+We'd also like to thank the University of Minnesota School of Mathematics for hosting us, and we'd like to thank Gregg Musiker and Emily Gunawan for their useful comments on our work.
+
 \bibliography{References}

### 2014-08-12 Paper.tex
edited acknowledgements

@@
 \author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
-\address{you can put addresses for authors\\
- \\
-Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556 \\
-Hailee: 1184 W Main St; Decatur, IL 62522 }
+\address{Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556 \\
+Hailee: 1184 W Main St; Decatur, IL 62522}
 \email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
@@
 \thanks{This work was supported by the RTG grant NSF/DMS-1148634.
-We'd also like to thank the University of Minnesota School of Mathematics for hosting us, and we'd like to thank Gregg Musiker and Emily Gunawan for their useful comments on our work.
+We would also like to thank the University of Minnesota School of Mathematics for hosting us.
+We are greatly appreciative of Gregg Musiker's mentoring, support, and guidance on this problem.
+We thank Emily Gunawan for her useful comments on our work.
+We also thank Vic Reiner for helping Gregg Musiker pose the problem.}
 

### 2014-08-14 Paper.tex
added changes suggested by Gregg

--- 2014-08-12 Paper.tex
@@
 Using this group presentation, Barot and Marsh state the following result:
-\begin{thm}\cite[Theorem A]{BM13}
+\begin{thm}\label{thm:barot_and_marsh_A}\cite[Theorem A]{BM13}
 Let $\Gamma$ be the diagram associated to a seed in a cluster algebra of finite type. Then $W(\Gamma)$ is isomorphic to the corresponding reflection group.
@@
 Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$.
-Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, or a triangle with two edges of weight 2 and one of weight 1, as pictured below.
-\\
+Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, or a triangle with two edges of weight 2 and one of weight 1, as pictured in Figure \ref{fig:cycle_types}
+
+\begin{figure}[h]\label{fig:cycle_types}
 \hspace*{-1.2cm}
@@
    \end{tikzpicture}
-
+\caption{Possible chordless cycles in a diagram of finite type}
+\end{figure}
 \end{prop}
@@
 
+The structure of the proof will be analogous to the structure of the proof of Theorem \ref{thm:barot_and_marsh_A}, but with most of the details changed to account for the fact that the $(R1)$ relations are not included.
+In particular, many of the computations used to prove the supporting lemmas and propositions of Theorem \ref{thm:barot_and_marsh_A} rely heavily on the $(R1)$ relations and therefore did not apply to the supporting lemmas and propositions of Theorem \ref{thm:main}.
+
 Throughout the section we will fix a diagram of finite type $\Gamma$, a vertex $k$ of $\Gamma$, and write $\Gamma^{\prime} = \mu_k(\Gamma)$.
@@
 $$\psi\circ\varphi(r_i) = \Delta^\prime(\varphi_{op}(\Delta(\varphi(r_i)))) = \Delta^\prime(\varphi_{op}(\Delta(s_i))) = \Delta^\prime(\varphi_{op}(q_i^{-1})) = \Delta^\prime(u_i^{-1}) = r_i$$
+
+In other words, starting at any node in the square below and following the maps around gives the identity map.
+
+\begin{figure*}[h]
+\hspace*{-4em}
+\begin{tikzpicture}[baseline=-0.5ex]
+\matrix[matrix of math nodes,column sep={60pt,between origins},row
+    sep={60pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+  {
+    & |[name = ul]|{A_{\Gamma^{op}}}\circ& |[name = ur]|\circ{A_{\left(\Gamma^\prime\right)^{op}}}\\
+    %
+    &|[name=dl]|{A_{\Gamma}} \circ &|[name=dr]| \circ{A_{\Gamma^\prime}} \\
+  };
+\draw[->]
+  (ul) to node[above]{$\varphi_{op}$} (ur)
+  ;
+  \draw[->]
+  (dl) to node[left]{$\Delta$}(ul)
+  ;
+  \draw[->]
+  (dr) to node[below]{$\varphi$}(dl)
+  ;
+  \draw[->]
+  (ur) to node[right]{$\Gamma^\prime$} (dr)
+  ;
+\end{tikzpicture}
+\end{figure*}
 
@@
 &= s_3s_1\underline{s_2s_1^{-1}s_3^{-1}s_1}s_2^{-1}s_1^{-1}\\
-&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &t(2,1)\\
+&= s_3s_1s_1^{-1}s_3^{-1}s_1s_2s_2^{-1}s_1^{-1} &\text{by } t(2,1)\\
 &= e
@@
 &= s_1s_2^{-1}s_1^{-1}\underline{s_2s_3^{-1}s_4s_3}s_1s_2s_1^{-1}\\
-&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &t(2,3)\\
+&= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3\underline{s_2s_1s_2s_1^{-1}} &\text{by } t(2,3)\\
 &= s_1s_2^{-1}s_1^{-1}s_3^{-1}s_4s_3s_1s_2s_1^{-1}s_1\\
@@
 &= s_1s_3^{-1}s_4s_3\\
-&= s_3^{-1}s_4s_3s_1 &t(1,3)\\
+&= s_3^{-1}s_4s_3s_1 &\text{by } t(1,3)\\
 &= (s_2^{-1}s_2)s_3^{-1}(s_2^{-1}\underline{s_2)s_4(s_2^{-1}}s_2)s_3(s_2^{-1}s_2s_1\\
@@
 &= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
-&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &t(3,4)\\
+&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &\text{by} t(3,4)\\
 &= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\
@@
 &= s_k\underline{s_1s_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2}s_k^{-1}\\
-&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &t(1,2)\\
+&= s_ks_2^{-1}\cdots s_{h-1}^{-1}s_hs_{h-1}\cdots s_2s_1s_k^{-1} &\text{by } t(1,2)\\
 &= s_2^{-1}\cdots s_{h-1}^{-1}s_ks_hs_k^{-1}s_{h-1}\cdots s_2s_1\\

### 2014-08-16 Paper.tex
made greggs responses to section 3,4

@@
    \end{tikzpicture}
-\caption{Possible chordless cycles in a diagram of finite type}
+\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}}
 \end{figure}
@@
 \label{local_three_picture}
-\cite[Corollary 2.3]{BM13} Let $\Gamma$ be a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in one of the following figures, either from left to right or right to left, up to switching $i$ and $j,$
-
+\cite[Corollary 2.3]{BM13} Let $\Gamma$ be a graph of finite type and suppose there are three vertices, labeled $i,j,k$ with both $i,j$ connected to $k.$ Then mutation at $k$ on the induced subdiagram appear as in Figure \ref{fig:local_three}, either from left to right or right to left, up to switching $i$ and $j,$
+\end{cor}
+
+\begin{figure}
+\label{fig:local_three}
 \begin{enumerate}[(a)]
@@
 \end{enumerate}
-
-\end{cor}
+\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}}
+\end{figure}
 
@@
 %\end{lem}
-
-\begin{longfig}
-\label{fig:cycle_types}
-Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ Below, we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
-Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.
-
+\begin{figure}
+\label{fig:cycle_types_a}
 \begin{enumerate}[(a)]
@@
     \end{tikzpicture}
-
-   \item
+    \end{enumerate}
+\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
+\end{figure}
+
+\begin{figure}
+\label{fig:cycle_types_b}
+\begin{enumerate}
+   \item[(i)]
    \begin{tikzpicture}[baseline=-0.5ex]
@@
 
-   \item
+   \item[(j)]
    \begin{tikzpicture}[baseline=-0.5ex]
@@
 
-    \item $C$ is an oriented cycle in $\Gamma$ not connected to $k$ and $C'$ is the corresponding cycle in $\Gamma'.$
-
-      \item
+    \item[(k)] $C$ is an oriented cycle in $\Gamma$ not connected to $k$ and $C'$ is the corresponding cycle in $\Gamma'.$
+
+      \item[(l)]
    \begin{tikzpicture}[baseline=-0.5ex]
@@
 \end{enumerate}
-\end{longfig}
+
+\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
+\end{figure}
 
 \begin{lem}\label{lem:chordless_cycles}
-\cite[Lemma 2.5]{BM13} Every chordless cycle in $\Gamma'$ is of one of the types listed in Figure ~\ref{fig:cycle_types}.
+\cite[Lemma 2.5]{BM13} 
+Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ In figures \ref{fig:cycle_types_a} and \ref{fig:cycle_types_b} we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
+Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.
+
+Every chordless cycle in $\Gamma'$ is of one of the types listed in Figure \ref{fig:cycle_types_a} or Figure \ref{fig:cycle_types_b}.
 \end{lem}
@@
 In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin group associated to a finite type diagram.
-This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require $s_i^2 = e.$ Since Artin Groups are very similar to Coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
+This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require relation $(R1),$ i.e., $s_i^2 = e.$ Since Artin Groups are very similar to Coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
 
@@
 \cite[Beginning of section 1.2]{C06}
-For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a matrix whose entries can take values in the real numbers or infinity, satisfying $M_{i,j} = M_{j,i},$ we define the associated {\it Artin group} in terms of generators and relations by
+For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a symmetric matrix whose entries can take values in the integers or infinity, we define the associated {\it Artin group} in terms of generators and relations by
 \begin{align*}
-A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}} = \langle x_j,x_i \rangle^{M_{i,j}} \forall i,j \text{ with } M_{i,j}<\infty \rangle,
+A = \langle x_1,\ldots, x_n| \langle x_i,x_j \rangle^{M_{i,j}} = \langle x_j,x_i \rangle^{M_{i,j}} \text{ for all } i,j \text{ with } M_{i,j}<\infty \rangle,
 \end{align*}
@@
 
-Finally, we are ready to define the Artin group we associate to a diagram of finite type. First, we shall need a tiny bit more notation.
+We are now ready to define the Artin group we associate to a diagram of finite type.
 
@@
 then, we include the relation
-$t(i_0,i_1)=e.$
+$t(i_0,i_1)=e.$ That is, $s_{i_0}$ and $p(i_0,i_1)$ commute.
 \end{itemize}
@@
 We purposely include relations $(T2),(T3)$ but not $(T1)$ in order to make our relation labeling analogous to that of \cite{BM13} at the beginning of Section 3.
-Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of in \cite[Remark 3]{BM13}.
+Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of Section 3 in \cite{BM13}.
 \end{rem}
@@
 \begin{itemize}
-\item $\langle s_1,s_2 \rangle^3 = \langle s_2,s_1 \rangle^3$
-\item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3$
-\item $\langle s_3,s_4 \rangle^3 = \langle s_4,s_3 \rangle^3$
-\item $\langle s_4,s_1 \rangle^3 = \langle s_1,s_4 \rangle^3$
+\item $\langle s_1,s_2 \rangle^3 = \langle s_2,s_1 \rangle^3,$ i.e., $s_1s_2s_1 = s_2s_1s_2$
+\item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3,$ i.e., $s_2s_3s_2 = s_3s_2s_3$
+\item $\langle s_3,s_4 \rangle^3 = \langle s_4,s_3 \rangle^3,$ i.e., $s_3s_4s_3 = s_4s_3s_4$
+\item $\langle s_4,s_1 \rangle^3 = \langle s_1,s_4 \rangle^3,$ i.e., $s_4s_1s_4 = s_1s_4s_1$
 \end{itemize}
@@
 
+\begin{ex}
+The relations $(T2),(T3)$ in that $\Gamma$ is a triangle with two edges of weight 2 and one of weight 1 are as follows:
+\[\Gamma = \begin{tikzpicture}[baseline=-0.5ex]
+\matrix[matrix of math nodes,column sep={25pt,between origins},row
+    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+  {
+    && |[name = u]|\circ& \\
+    %
+    &|[name=dl]| \circ & &|[name=dr]| \circ \\
+  };
+\draw[->]
+   (u) to node[right] {2}(dr)
+  ;
+  \draw[->]
+  (dl) to node[left]{2}(u)
+  ;
+  \draw[->]
+  (dr) to node[below]{1}(dl)
+  ;
+  \node [yshift = .4 cm] at (u){1};
+    \node [yshift = -.4 cm,xshift = .4 cm] at (dr){2};
+    \node [yshift = -.4 cm,xshift = -.4 cm] at (dl){3};
+   \end{tikzpicture}\]
+   \begin{enumerate}
+\item[(T2)]
+\begin{itemize}
+\item $\langle s_1,s_2 \rangle^4 = \langle s_2,s_1 \rangle^4,$ i.e., $s_1s_2s_1s_2 = s_2s_1s_2s_1$
+\item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3,$ i.e., $s_2s_3s_2 = s_3s_2s_3$
+\item $\langle s_3,s_4 \rangle^4 = \langle s_4,s_3 \rangle^4,$ i.e., $s_3s_4s_3s_4 = s_4s_3s_4s_3$              
+\end{itemize}
+\item[(T3)]
+\begin{itemize}
+\item $s_1s_2^{-1}s_3^{-1}s_2s_1^{-1}s_2^{-1}s_3s_2 = e$
+
+\item $s_2s_3^{-1}s_1^{-1}s_3s_2^{-1}s_3^{-1}s_1s_3 =e$
+
+\end{itemize}
+\end{enumerate}
+\end{ex}
+
 \begin{rem}
 Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the Artin group corresponding to that Dynkin diagram.
-This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(T2'),$ which define the Artin group.
+This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(T2),$ which define the Artin group.
 \end{rem}

### 2014-08-17 Paper.tex
Updated changes for sections 1 and 2

@@
 They define generator relations corresponding to chordless cycles arising in diagrams of finite type in order to give a Coxeter group presentation for these diagrams.
-They also proved that this Coxeter group presentation is invariant up to isomorphism under the mutation equivalence relation.That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group representations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
+They also proved that this Coxeter group presentation is invariant up to isomorphism under the mutation equivalence relation.
+That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group presentations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
 
@@
 In our paper, we define $A_{\Gamma}$ to be the Artin group presentation arising from a cluster algebra, where $\Gamma$ is the diagram associated to the cluster algebra.
-We provide the necessary relations for the generators of the group, and show that these relations hold under mutations of chordless cycles in a diagram.
-Our main result is to show that this Artin group presentation is invariant up to isomorphism under the mutation equivalence relation.
+We provide the necessary relations for the generators of the group, and show that these relations hold under mutations of vertices in a diagram.
+Our main result is to show that this Artin group presentation is invariant, up to isomorphism, under the mutation equivalence relation.
 We state the result here, but present the detailed proof in Section \ref{sec:main_result}.
@@
 We begin by introducing some preliminary notations and definitions which will aid the reader in understanding the results in the following sections.
-For further references on cluster algebras, we refer the reader to \cite{FZ02} and \cite{FZ03} and for a more detailed description of Artin group presentations, we direct attention to \cite{FN61}.
+For further references on cluster algebras, we refer the reader to \cite{FZ02, FZ03}, and for a more detailed description of Artin group presentations, we direct attention to \cite{FN61}.
 We also provide references to several lemmas and propositions from \cite{BM13} which were helpful in formulating our own results.
@@
 Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations.
-Of particular interest were \textit{finite type} cluster algebras.
+Of particular interest were \textit{finite type} cluster algebras, those with a finite number of distinguished generators.
 In the sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3.
@@
 \\
+
 A \textit{cluster algebra} is an integral domain which can be generated by a set of elements called \textit{cluster variables} that satisfy certain exchange relations.
@@
 \end{displaymath}
-
 and $\textbf{x}^{\prime} = \left\{ x_1, x_2, \ldots, x_{k-1}, x_k^{\prime}, x_{k+1}, \ldots, x_n \right\}$.
@@
 We will denote two connected vertices by $i \rightarrow j$, or by $i\--\ j$ if the orientation is not specified.
-The diagram is determined by, for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge.
+The diagram is determined by the following: for $i, j \in \V$, $i \xrightarrow{w} j$ if and only if $B_{ij} > 0$ and $w = |B_{ij}B_{ji}|$ is the weight of the edge.
 A skew-symmetrisable matrix $B$ is \textit{2-finite} if $|B_{ij}B_{ji}| \leq 3$ for $i, j \in \left\{ 1, \ldots, n \right\}$.
@@
 \item $(s_is_j)^{m_{ij}} = e$ for all $i \neq j$;
-\item For any chordless cycle (as defined in Definition \ref{chordlesscycle} $C$ in $\Gamma$, where
+\item For any chordless cycle (as defined in Definition \ref{chordlesscycle}) $C$ in $\Gamma$, where
 \begin{displaymath}
@@
 
-In Section 3 of \cite{BM13}, Barot and Marsh provide an alteration of the group $W(\Gamma)$ in order to extend the group definition to any diagram of finite type. The group they define is as follows:
+In Section 3 of \cite{BM13}, Barot and Marsh provide an alteration of the group $W(\Gamma)$ in order to extend the group definition to any diagram of finite type.
+More specifically, they provide relations such that $W_{\Gamma}$, as defined below, is isomorphic to $W(\Gamma)$ (\cite[Proposition 4.5]{BM13}).
 
@@
 
-The rest of the paper will be devoted to building up analogous relations, defined in ~\ref{grp def} to prove a similar result in the case of Artin groups.
+The rest of the paper will be devoted to building up analogous relations, defined in Definition~\ref{grp def} to prove a similar result in the case of Artin groups.
 For $\Gamma$ a diagram of finite type, we define the Artin group associated to $\Gamma$ as in Section \ref{sec:defn_artingroup}.

### 2014-08-18 Paper.tex
Section 5 Edits

@@
 \author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
-\address{Jacob: 225 St. Edward's Hall; Notre Dame, IN 46556 \\
+\address{Jacob: University of Notre Dame \\
 Hailee: 1184 W Main St; Decatur, IL 62522}
@@
 
-\section{Symmetry among (R3) Relations}
+\section{Symmetry among the (R3) Relations}
 \label{sec:one_relation}
@@
 
-\begin{lem}
+\begin{lem} \label{Sym-Lem}
 Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
@@
 so that all edges have weight 1.
-Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1})$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
+Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
 \end{lem}
 
-\begin{proof}
-It suffices to prove that the relation t(0, 1) implies the relation t(d-1, 0), as the other relations will follow by induction. So suppose $A_{\Gamma}$ satisfies the relation t(0, 1). Then we have
+In the proof of this Lemma and throughout the rest of the paper, we will frequently employ the following relations, which follow from the (T2) relations.
+
+\begin{lem} \label{Extra-Rel}
+Let $\Gamma$ be a diagram of finite type, and let $A_{\Gamma}$ be generated by $s_{1}, \dots, s_{n}$. Then we have that 
+\begin{enumerate}[(a)]
+\item $s_{i}s_{j}s_{i}^{-1} = s_{j}^{-1}s_{i}s_{j}$ if there is an arrow of weight 1 from i to j in $\Gamma$ \\
+\item $s_{i}s_{j}s_{i}^{-1}s_{j}^{-1} = s_{j}^{-1}s_{i}^{-1}s_{j}s_{i}$ if there is an arrow of weight 2 from i to j in $\Gamma$
+\end{enumerate}
+\end{lem}
+
+\begin{proof}[Proof of \ref{Extra-Rel}]
+The relation in (a) follows immediately from the (T2) relation $s_{j}s_{i}s_{j} = s_{i}s_{j}s_{i}$ by left multiplying both sides by $s_{j}^{-1}$ and right multiplying both sides by $s_{i}^{-1}$.
+Similarly, the relation in (b) arises from the (T2) relation $s_{j}s_{i}s_{j}s_{i} = s_{i}s_{j}s_{i}s_{j}$ by left multiplying both sides by $s_{i}^{-1}s_{j}^{-1}$ and right multiplying both sides by $s_{j}^{-1}s_{i}^{-1}$
+\end{proof}   
+\begin{proof}[Proof of \ref{Sym-Lem}]
+It suffices to prove that the relation t(0, 1) = e implies that t(d-1, 0) = e, as the other relations will follow by induction. So suppose $A_{\Gamma}$ satisfies the relation t(0, 1) = e. Then we have
 \begin{align*}
-s_{d-1}p_{d-1, 0} & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
+s_{d-1}p(d-1, 0) & = s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
 &= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
@@
 &= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} &\text{by (T2)}\\
-&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by t(0, 1)}\\
+&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by t(0, 1) = e}\\
 &= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} &\text{by (T2)}\\
+&= s_{0}^{-1}(s_{d-1}^{-1}s_{d-1})s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
 &= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
 &= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} &\text{by (T2)}\\
-&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p_{d-1, 0}s_{d-1}
+&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} = p(d-1, 0)s_{d-1}
 \end{align*}
@@
    \end{tikzpicture}
-and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) and t(k, i) are equivalent.
+and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) = e and t(k, i) = e are equivalent.
 \end{lem}
@@
 \begin{align*}
-& s_{k}^{-1}s_{j}(s_{i}p_{i, j}s_{i}^{-1}p_{i, j}^{-1})s_{j}^{-1}s_{k} \\
-& s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
+& s_{k}^{-1}s_{j}(s_{i}p(i, j)s_{i}^{-1}p(i, j)^{-1})s_{j}^{-1}s_{k} \\
+&= s_{k}^{-1}s_{j}(s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1}s_{k}^{-1}s_{j})s_{j}^{-1}s_{k} \\
 &= s_{k}^{-1}s_{j}s_{i}s_{j}^{-1}s_{k}s_{j}s_{i}^{-1}s_{j}^{-1} \\
 &= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i} \\
-&= s_{k}^{-1}p_{k, i}s_{k}p_{k, i}^{-1}
+&= s_{k}^{-1}p(k, i)s_{k}p(k, i)^{-1}
 \end{align*}
@@
 \begin{proof}
-We first show that
+We show that
 $$s_{j}^{-1}s_{k}^{-1}s_{i}s_{k}s_{j}s_{k}^{-1}s_{i}s_{k}s_{j}^{-1}s_{k}^{-1}s_{i}^{-1}s_{k} = e.$$
@@
 \end{tikzpicture}
-and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) and t(k, l) are equivalent.
+and let A be the group with generators $s_{1}, \dots, s_{n}$ defined by $\Gamma$. Then the relations t(i, j) = e and t(k, l) = e are equivalent.
 \end{lem}
@@
 One can see that the inverse elements satisfy (T2) in A$_{\Gamma^{op}}$ by taking the inverse of both sides of the corresponding relation in A$_{\Gamma}$.
-To see that the elements satisfy (T3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{0} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}$$ by the relation t(0,1) in (T3) in A$_{\Gamma}$.
-But then applying relations from (T2), we have that $$s_{0}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{0} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1},$$ and since the cycle is chordless, we then have $$s_{0}^{-1}s_{d-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{d-1}^{-1}s_{0} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}.$$ Repeating this process, we find that $$s_{0}^{-1}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation t(0, d-1) in A$_{\Gamma^{op}}.$
-
-For a triangle labeled as in ~\ref{2tri}, by the relation t(k, i) we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation t(k, j) in A$_{\Gamma^{op}}$.
-
-Finally, given a square labeled as in ~\ref{2sqr} and the relations t(1, 2) and t(3, 4), we have
+To see that the elements satisfy (T3) in A$_{\Gamma^{op}}$, note that for a chordless cycle in $\Gamma$ with all weights equal to one, we have $$s_{0}s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1} = s_{1}^{-1}\dots s_{d-2}^{-1}s_{d-1}s_{d-2}\dots s_{1}s_{0}$$ by the relation t(0,1) = e in (T3) in A$_{\Gamma}$.
+But then applying relations from (T2), we have that $$s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1} = s_{1}^{-1}\dots s_{d-1}s_{d-2}s_{d-1}^{-1}\dots s_{1}s_{0},$$ and since the cycle is chordless, we then have $$s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1} = s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}.$$ Repeating this process, we find that $$s_{0}s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1} = s_{d-1}s_{d-2}\dots s_{2}s_{1}s_{2}^{-1}\dots s_{d-2}^{-1}s_{d-1}^{-1}s_{0}.$$ But this occurs if and only if $s_{1}^{-1}, \dots, s_{n}^{-1}$ satisfies the relation t(0, d-1) = e in A$_{\Gamma^{op}}.$
+
+For a triangle labeled as in ~\ref{2tri}, by the relation t(k, i) = e we have $$s_{k}s_{i}^{-1}s_{j}s_{i}s_{k}^{-1} = s_{i}^{-1}s_{j}s_{i}.$$ Hence $$s_{k}s_{j}s_{i}s_{j}^{-1}s_{k}^{-1} = s_{j}s_{i}s_{j}^{-1}.$$ But as before, this can occur if and only if $s_{i}^{-1}, s_{j}^{-1}, s_{k}^{-1}$ satisfy the relation t(k, j) = e in A$_{\Gamma^{op}}$.
+
+Finally, given a square labeled as in ~\ref{2sqr} and the relations t(1, 2) = e and t(3, 4) = e, we have
 \begin{align*}
@@
 \end{align*}
-But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy t(j, i) in A$_{\Gamma^{op}}$. Therefore, we are done.
+But this relation holds if and only if $s_{i}^{-1}, \dots, s_{l}^{-1}$ satisfy t(j, i) = e in A$_{\Gamma^{op}}$. Therefore, we are done.
 \end{proof}

### 2014-08-20 Paper.tex
Added Conjecture

@@
 Section \ref{sec:one_relation} specifies how certain relations in chordless cycles imply other relations in those chordless cycles.
-Finally, Section \ref{sec:main_result} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
+Section \ref{sec:main_result} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
+Finally, in Section \ref{sec:affine}, we will state a conjecture which could extend the main result to diagrams of affine type.
 \\
@@
 Just as we can define mutations of the seeds of a cluster variable, we can also define mutations of a diagram associated to a cluster algebra of finite type by the following set of rules:
-\begin{prop}\cite[Proposition 1.4]{BM13}
+\begin{prop}\cite{FZ03}
 Let $B$ be a 2-finite skew-symmetrisable matrix. Then $\Gamma(\mu_k(B))$ is uniquely determined by $\Gamma(B)$ as follows:
@@
 Let $c'$ be determined by $c'\geq 0$ and
-$c+c' =$ max$(a,b)$.
+$\pm \sqrt{c} \pm \sqrt{c'} = \sqrt{ab}$, 
+where the sign before $\sqrt{c}$ (respectively, $\sqrt{c'}$) is positive if the arrows form an oriented cycle and negative otherwise.
 Then $\Gamma(B)$ changes as in Figure \ref{mutation}, taking the case $c' = 0$ to mean no arrow between $i$ and $j$.
@@
 
+\section{Extension to Affine Type Diagrams} \label{sec:affine}
+It is natural to ask whether one can obtain similar results for diagrams that are not of finite type, particularly those of affine type (i.e.
+mutation equivalent to an affine Dynkin diagram).
+In \cite{FT13}, the authors associated the following group to a diagram of affine type.
+
+\begin{def}\cite[Definition 4.1]{FT13}
+Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $W_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
+\begin{enumerate}
+\item[(R1)] $s_{i}^{2} = e$ for all i = 1, \dots, n
+\item[(R2)] $(s_{i}s_{j})^{m_{ij}} = e$ where 
+$$m_{ij} = 
+\begin{cases}
+2 &\text{if there is no arrow between i and j in $\Gamma$} \\
+3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
+4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
+6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
+\infty &\text{otherwise}
+\end{cases}$$
+\item[R(3)] For every chordless oriented cycle:
+$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
+define for l $\in \{0, \dots, d-1\}$, 
+$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
+Then take the relation $(s_{i_{l}}p(i_{l}, i_{l+1}))^{m(l)} = e$ where
+$$m(l) =
+\begin{cases}
+2 &\text{if $t(l)=0$} \\
+3 &\text{if $t(l)=1$} \\
+4 &\text{if $t(l)=2$} \\
+6 &\text{if $t(l)=3$}
+\end{cases}$$
+\item[R(4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
+\end{enumerate}
+\end{def}
+
+Given this definition of $W_{\Gamma}$, which generalizes the definition of $W_{\Gamma}$ found in \cite{BM13}, one obtains the following result.
+
+\begin{thm} \cite[Theorem 4.6]{FT13}
+Let W be an affine Weyl group and let $\Gamma$ be a diagram mutation equivalent to an orientation of a Dynkin diagram of the same type as W. Then W is isomorphic to $W_{\Gamma}$.
+\end{thm}
+
+\begin{table} \label{table1}
+\begin{tabular}{| p{3.5cm} | p{7cm} |}
+\hline
+Subdiagram & (R4) Relation \\ \hline
+\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $(s_{1}s_{2}s_{3}s_{4}s_{3}s_{2})^{2} = e$ \\ \hline
+
+\begin{center}\includegraphics[scale = .30]{Diagram2.pdf}\end{center} 
+& $(s_{1}s_{2}s_{3}s_{2}s_{1}s_{4}s_{5} \dots s_{n}s_{n+1}s_{n} \dots s_{5}s_{4})^{2} = e$ \\ \hline
+
+\begin{center}\includegraphics[scale = .30]{Diagram3.pdf}\end{center} & $(s_{2}s_{3}s_{4}s_{1}s_{4}s_{3})^{2} = e$ and $(s_{2}s_{1}s_{4}s_{3}s_{4}s_{1})^{2} = e$\\ \hline
+
+\begin{center}\includegraphics[scale = .30]{Diagram4.pdf}\end{center} & $(s_{n+1}s_{1}s_{n+1}s_{2}s_{3} \dots s_{n-1}s_{n}s_{n-1} \dots s_{3}s_{2})^{2} = e$ \\ \hline
+
+\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $(s_{2}s_{1}s_{2}s_{1}s_{2}s_{3})^{2} = e$ and $(s_{2}s_{3}s_{2}s_{3}s_{2}s_{1})^{2} = e$ \\ \hline
+\end{tabular}
+\caption{(R4) Relations}
+\end{table}
+
+In seeking an analogous result for Artin groups, we generalize A$_{\Gamma}$ as follows:
+
+\begin{defn}
+Let $\Gamma$ be a diagram of affine type with n + 1 vertices. Then we define $A_{\Gamma}$ to be the diagram with generators $s_{1}, \dots, s_{n}$ and satisfying the following relations:
+\begin{enumerate}
+\item[(T2)] $\langle s_{i}, s_{j} \rangle^{m_{ij}} = \langle s_{j}, s_{i} \rangle^{m_{ij}}$ where
+$$m_{ij} = 
+\begin{cases}
+2 &\text{if there is no arrow between i and j in $\Gamma$} \\
+3 &\text{if there is an arrow of weight 1 between i and j in $\Gamma$} \\
+4 &\text{if there is an arrow of weight 2 between i and j in $\Gamma$} \\
+6 &\text{if there is an arrow of weight 3 between i and j in $\Gamma$} \\
+\infty &\text{otherwise}
+\end{cases}$$
+\item[(T3)] For every chordless oriented cycle:
+$$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
+define for l $\in \{0, \dots, d-1\}$, 
+$$t(l) = (\prod_{j=l}^{l+d-2}{\sqrt{w_{i_{j}}}} - \sqrt{w_{i_{l+d-1}}})^{2}.$$
+Then take the relation $\langle s_{i_{l}}p(i_{l}, i_{l+1}) \rangle^{m(l)} = \langle p(i_{l}, i_{l+1})s_{i_{l}} \rangle^{m(l)}$ where
+$$m(l) =
+\begin{cases}
+2 &\text{if $t(l)=0$} \\
+3 &\text{if $t(l)=1$} \\
+4 &\text{if $t(l)=2$} \\
+6 &\text{if $t(l)=3$}
+\end{cases}$$
+\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table2}, we add the relation(s) listed in the second column.
+\end{enumerate}
+\end{defn}
+
+\begin{conj}
+Let $\Gamma$ be a diagram of affine type, and let $\Gamma^{\prime}$ be the mutation of $\Gamma$ at a node k. Then $A_{\Gamma}$ $\cong$ $A_{\Gamma^{\prime}}$.
+\end{conj}
+
+\begin{table} \label{table2}
+\begin{tabular}{| p{3.5cm} | p{7cm} |}
+\hline
+Subdiagram & (T4) Relation \\ \hline
+\begin{center}\includegraphics[scale = .30]{Diagram1.pdf}\end{center} & $s_{2}s_{1}s_{2}^{-1}s_{4}^{-1}s_{3}s_{4} = s_{4}^{-1}s_{3}s_{4}s_{2}s_{1}s_{2}^{-1}$ \\ \hline
+
+\begin{center}\includegraphics[scale = .30]{Diagram2.pdf}\end{center} 
+& $s_{2}s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}s_{1}s_{n+1}s_{1}^{-1}s_{n} \dots s_{4}s_{3}$
+\newline $= s_{3}^{-1}s_{4}^{-1}\dots s_{n}^{-1}s_{1}s_{n+1}s_{1}^{-1}s_{n} \dots s_{4}s_{3}s_{2}$\\ \hline
+
+\begin{center}\includegraphics[scale = .30]{Diagram3.pdf}\end{center} & $s_{2}s_{3}^{-1}s_{4}s_{1}s_{4}^{-1}s_{3} = s_{3}^{-1}s_{4}s_{1}s_{4}^{-1}s_{3}s_{2}$ and
+$s_{2}s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1} = s_{1}s_{4}^{-1}s_{3}s_{4}s_{1}^{-1}s_{2}$\\ \hline
+
+\begin{center}\includegraphics[scale = .30]{Diagram4.pdf}\end{center} & $s_{1}s_{2}^{-1} \dots s_{n-1}^{-1}s_{n+1}s_{n}s_{n+1}^{-1}s_{n-1} \dots s_{2} = s_{2}^{-1} \dots s_{n-1}^{-1}s_{n+1}s_{n}s_{n+1}^{-1}s_{n-1} \dots s_{2}s_{1}$ \\ \hline
+
+\begin{center}\includegraphics[scale = .30]{Diagram5.pdf}\end{center} & $s_{2}s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1} = s_{1}^{-1}s_{2}s_{3}s_{2}^{-1}s_{1}s_{2}$ and $s_{1}s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1} = s_{2}s_{3}s_{2}s_{3}^{-1}s_{2}^{-1}s_{1}$ \\ \hline
+\end{tabular}
+\caption{(T4) Relations}
+\end{table}
+
 \section{Acknowledgements}

### 2014-08-20 Paper.tex
Added Reference

@@
 \end{cases}$$
-\item[R(3)] For every chordless oriented cycle:
+\item[(R3)] For every chordless oriented cycle:
 $$i_{0} \stackrel{w_{i_{0}}}{\longrightarrow} i_{1} \stackrel{w_{i_{1}}}{\longrightarrow} \dots \stackrel{w_{i_{d-2}}}{\longrightarrow} i_{d-1} \stackrel{w_{i_{d-1}}}{\longrightarrow} i_{0},$$
@@
 \end{cases}$$
-\item[R(4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
+\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
 \end{enumerate}

### 2014-09-02 Paper.tex
tried to move diagrams, but failed
made all of greg's comments for sections 3,4 except first

@@
 \newtheorem{conj}[thm]{Conjecture}
-\newtheorem{longfig}[thm]{Figure}
-
 %\usepackage[all]{xy}
@@
 
-\begin{figure}[h]\label{fig:cycle_types}
+\begin{figure}[h]
 \hspace*{-1.2cm}
@@
    \end{tikzpicture}
+   \label{fig:cycle_types}
 \caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}}
@@
 \begin{figure}
-\label{fig:local_three}
 \begin{enumerate}[(a)]
@@
 \end{enumerate}
+
+\label{fig:local_three}
 \caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}}
@@
 \begin{figure}
-\label{fig:cycle_types_a}
 \begin{enumerate}[(a)]
@@
     \end{tikzpicture}
+    \end{enumerate}
+
+\label{fig:cycle_types_a}
+\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
+\end{figure}
+
+\begin{figure}
+\begin{enumerate}
 
@@
     \end{tikzpicture}
-    \end{enumerate}
-\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
-\end{figure}
-
-\begin{figure}
-\label{fig:cycle_types_b}
-\begin{enumerate}
    \item[(i)]
@@
 
+\label{fig:cycle_types_b}
 \caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
@@
 \cite[Lemma 2.5]{BM13} 
-Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ In figures \ref{fig:cycle_types_a} and \ref{fig:cycle_types_b} we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
+Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ In Figure \ref{fig:cycle_types_a} and Figure \ref{fig:cycle_types_b} we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
 Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.
@@
 \cite[Beginning of section 1.2]{C06}
-For $M \in M_{n \times n}(\mathbb Z \cup \infty)$ a symmetric matrix whose entries can take values in the integers or infinity, we define the associated {\it Artin group} in terms of generators and relations by
+Let $Sym_n(R)$ denote the set of $n \times n$ symmetric matrices with entries in $R$.
+For $M \in Sym_n(\mathbb Z \cup \infty)$ a symmetric matrix whose entries can take values in the integers or infinity, we define the associated {\it Artin group} in terms of generators and relations by
 \begin{align*}
@@
 Note that if $\Gamma$ is the graph associated to a Dynkin diagram, then $W_\Gamma$ as we have defined it is precisely the Artin group corresponding to that Dynkin diagram.
-This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relation of the form $(T2),$ which define the Artin group.
+This occurs because, in this case, we have no cycles in $\Gamma,$ and so we only have relations of the form $(T2),$ which define the Artin group.
 \end{rem}
@@
 \begin{proof}
-The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Corollary \ref{local_three_picture}.
+The possibilities for the subdiagram induced by $i$, $j$, and $k$ are enumerated in Figure \ref{fig:local_three}.
 We show that $t_i$ and $t_j$ satisfy the $(T2^\prime)$ relations by checking each case.
-Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in the figure in Corollary \ref{local_three_picture}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in the figure in Corollary \ref{local_three_picture}.
+Within each case, subcase $(i)$ is when the subdiagram of $\Gamma$ is the diagram on the left in Figure \ref{fig:local_three}, and subcase $(ii)$ is when the subdiagram of $\Gamma$ is the diagram on the right in Figure \ref{fig:local_three}.
 
@@
 
-\begin{table} \label{table1}
+\begin{table}[!h] \label{table1}
 \begin{tabular}{| p{3.5cm} | p{7cm} |}
@@
 
-\begin{table} \label{table2}
+\begin{table}[!h] \label{table2}
 \begin{tabular}{| p{3.5cm} | p{7cm} |}

### 2014-09-02 Paper.tex
made all of greg's comments for sections 3,4 except first, removed
tried to fix figure numbers, failed

@@
 Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$.
-Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, or a triangle with two edges of weight 2 and one of weight 1, as pictured in Figure \ref{fig:cycle_types}
+Furthermore, the unoriented graph underlying the cycle must either be a cycle such that all edges have weight 1, a square with two opposite edges of weight 2 and two opposite edges of weight 1, or a triangle with two edges of weight 2 and one of weight 1, as pictured in Figure \ref{fig:cycle_types}.
+\end{prop}
 
@@
 \end{figure}
-\end{prop}
 
@@
     \end{enumerate}
-
-\label{fig:cycle_types_a}
+\label{fig:first_cycle_types}
 \caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
@@
 
-\label{fig:cycle_types_b}
+\label{fig:second_cycle_types}
 \caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
@@
 \cite[Lemma 2.5]{BM13} 
-Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ In Figure \ref{fig:cycle_types_a} and Figure \ref{fig:cycle_types_b} we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
+Let $\Gamma$ be a diagram of finite type with $\Gamma' = \mu_k(\Gamma),$ the mutation of $\Gamma$ at vertex $k.$ In Figure \ref{fig:first_cycle_types} and Figure \ref{fig:second_cycle_types} we list induced subdiagrams in $\Gamma$ on the left and the resulting induced subdiagrams in $\Gamma'$ with chordless cycles $C'$ on the right, after mutation at $k.$ We draw the diagrams so that $C'$ always has a clockwise cycle.
 Furthermore, in case $(i),$ we assume $C'$ has at least three vertices, while in case $(j),$ we assume $C'$ has at least four vertices.
 
-Every chordless cycle in $\Gamma'$ is of one of the types listed in Figure \ref{fig:cycle_types_a} or Figure \ref{fig:cycle_types_b}.
+Every chordless cycle in $\Gamma'$ is of one of the types listed in Figure \ref{fig:first_cycle_types} or Figure \ref{fig:second_cycle_types}.
 \end{lem}
@@
 
-\begin{table}[!h] \label{table1}
+\begin{table}[h] \label{table1}
 \begin{tabular}{| p{3.5cm} | p{7cm} |}
@@
 
-\begin{table}[!h] \label{table2}
+\begin{table}[h] \label{table2}
 \begin{tabular}{| p{3.5cm} | p{7cm} |}

### 2014-09-05 Paper.tex
Labels Fixed

@@
 
+\begin{figure}
 \begin{center}
 \begin{tikzpicture}[baseline=-0.5ex]
-\label{mutation}
 
@@
    \end{center}
+
+\caption{Mutation of $\Gamma$ at a node k}\label{mutation}
+\end{figure}
 
@@
    \end{tikzpicture}
-   \label{fig:cycle_types}
-\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}}
+
+\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}} \label{fig:cycle_types}
 \end{figure}
@@
 
-\label{fig:local_three}
-\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}}
+\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}} \label{fig:local_three}
 \end{figure}
@@
     \end{enumerate}
-\label{fig:first_cycle_types}
-\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
+
+\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}} \label{fig:first_cycle_types}
 \end{figure}
@@
 
-\label{fig:second_cycle_types}
-\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
+\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}} \label{fig:second_cycle_types}
 \end{figure}
@@
 \end{cases}$$
-\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
+\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of Table \ref{table1}, we add the relation(s) listed in the second column.
 \end{enumerate}
@@
 
-\begin{table}[h] \label{table1}
+\begin{table}[h] 
 \begin{tabular}{| p{3.5cm} | p{7cm} |}
@@
 \end{tabular}
-\caption{(R4) Relations}
+\caption{(R4) Relations} \label{table1}
 \end{table}
@@
 \end{cases}$$
-\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table2}, we add the relation(s) listed in the second column.
+\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of Table \ref{table2}, we add the relation(s) listed in the second column.
 \end{enumerate}
@@
 
-\begin{table}[h] \label{table2}
+\begin{table}[h] 
 \begin{tabular}{| p{3.5cm} | p{7cm} |}
@@
 \end{tabular}
-\caption{(T4) Relations}
+\caption{(T4) Relations} \label{table2}
 \end{table}

### 2014-09-08 Paper.tex
More Edits

@@
 
-   \item
+   \item[(h)]
    \begin{tikzpicture}[baseline=-0.5ex]
@@
 Let $\Gamma$ be a diagram of finite type which contains a chordless cycle C:
-
 \begin{equation*}
@@
 \end{equation*}
-
 so that all edges have weight 1.
@@
 
-The structure of the proof will be analogous to the structure of the proof of Theorem \ref{thm:barot_and_marsh_A}, but with most of the details changed to account for the fact that the $(R1)$ relations are not included.
-In particular, many of the computations used to prove the supporting lemmas and propositions of Theorem \ref{thm:barot_and_marsh_A} rely heavily on the $(R1)$ relations and therefore did not apply to the supporting lemmas and propositions of Theorem \ref{thm:main}.
+The structure of the proof will be analogous to the structure of the proof of Theorem A in \cite{BM13}, but with most of the details changed to account for the fact that the $(R1)$ relations are not included.
+In particular, many of the computations used to prove the supporting lemmas and propositions of Theorem A rely heavily on the $(R1)$ relations and therefore do not apply to the supporting lemmas and propositions of Theorem \ref{thm:main}.
 
@@
 Note that the $u_i$ are generators $A_{\left(\Gamma^{op}\right)^\prime}$ as well, since $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.
-In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.
+In order to distinguish the relations in the groups $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we shall refer to the relations on $A_{\Gamma}$ as $(T2),(T3)$ and the relations on $A_{\Gamma^\prime}$ as $(T2^\prime),(T3^\prime).$ In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.
 
@@
 
-\item This follows from part (i) by symmetry
+\item This follows from part (i) by symmetry.
 \end{enumerate}
@@
 We thank Emily Gunawan for her useful comments on our work.
-We also thank Vic Reiner for helping Gregg Musiker pose the problem.}
+We also thank Vic Reiner for motivating this problem.}
 

### 2014-09-08 Paper.tex
Small Change

@@
 Note that the $u_i$ are generators $A_{\left(\Gamma^{op}\right)^\prime}$ as well, since $\left(\Gamma^\prime\right)^{op} = \left(\Gamma^{op}\right)^\prime$.
-In order to distinguish the relations in the groups $A_{\Gamma}$ and $A_{\Gamma^{\prime}}$, we shall refer to the relations on $A_{\Gamma}$ as $(T2),(T3)$ and the relations on $A_{\Gamma^\prime}$ as $(T2^\prime),(T3^\prime).$ In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.
+In the proof of Theorem \ref{thm:main} we will use Lemma \ref{lem:op_homomorphism} along with the following proposition, which we prove in Section \ref{sec:proof_of_ti_relations}.
 

### 2014-09-08 Paper.tex
removed todos

--- 2014-09-05 Paper.tex
@@
 
-%The package below let's us add todos to the document in a way that will stand out at a glance.
-It will also list all of the current things to do, with their respective page numbers on the first page of the document.
-You can add a todo like this:
-%
-% Text text text \todo{change this text to something useful!}
-%
-%Among other things, you can edit the color of a todo:
-%
-% \todo[color=\ltblue]{this todo will have a light blue background!}
-%
-%And you can include the todo as a line in the text, rather than in the margins:
-%
-% \todo[inline]{this will appear in the middle of the page}
-
-%\usepackage[colorinlistoftodos, textsize=tiny]{todonotes}
 %\def\ltblue{blue!20!white}
@@
 
-\makeatletter
-\providecommand\@dotsep{5}
-\def\listtodoname{List of Todos}
-\def\listoftodos{\@starttoc{tdo}\listtodoname}
-\makeatother
-
 \begin{document}
-%This adds the list of todos to the first page.
-\listoftodos
 
@@
 \author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
-\address{Jacob: University of Notre Dame \\
-Hailee: 1184 W Main St; Decatur, IL 62522}
 \email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
@@
 Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$.
-We will define an \textit{intial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix.
+We will define an \textit{initial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix.
 Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
@@
 
-\begin{figure}
 \begin{center}
 \begin{tikzpicture}[baseline=-0.5ex]
+\label{mutation}
 
@@
    \end{center}
-
-\caption{Mutation of $\Gamma$ at a node k}\label{mutation}
-\end{figure}
 
@@
 \end{displaymath}
-%\todo{Maybe it's worth presenting definition 2.4 before this, and then saying it is equivalent to removing certain the (R3)(b) relations.
-Don't they actually present the definition you refer to in Definition 2.4 as the presentation?
-You say it is an alteration there, but I think it's the original definition}
 \end{enumerate}
@@
    \end{tikzpicture}
-
-\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}} \label{fig:cycle_types}
+   \label{fig:cycle_types}
+\caption{Possible chordless cycles in a diagram of finite type, as found in \cite[Figure 2]{BM13}}
 \end{figure}
@@
 
-\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}} \label{fig:local_three}
+\label{fig:local_three}
+\caption{Local picture of the mutation of a finite type diagram, as found in \cite[Figure 4]{BM13}}
 \end{figure}
@@
     \end{enumerate}
-
-\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}} \label{fig:first_cycle_types}
+\label{fig:first_cycle_types}
+\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 5]{BM13}}
 \end{figure}
@@
 
-\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}} \label{fig:second_cycle_types}
+\label{fig:second_cycle_types}
+\caption{Induced subdiagrams of $\Gamma$ and corresponding chordless cycles in $\Gamma' = \mu_k(\Gamma),$ as found in \cite[Figure 6]{BM13}}
 \end{figure}
@@
 so that all edges have weight 1.
-Then if W is a group generated by $s_{1}, \dots, s_{n}$ satifying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
+Then if W is a group generated by $s_{1}, \dots, s_{n}$ satisfying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
 \end{lem}
@@
 \end{cases}$$
-\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of Table \ref{table1}, we add the relation(s) listed in the second column.
+\item[(R4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table1}, we add the relation(s) listed in the second column.
 \end{enumerate}
@@
 
-\begin{table}[h] 
+\begin{table}[h] \label{table1}
 \begin{tabular}{| p{3.5cm} | p{7cm} |}
@@
 \end{tabular}
-\caption{(R4) Relations} \label{table1}
+\caption{(R4) Relations}
 \end{table}
@@
 \end{cases}$$
-\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of Table \ref{table2}, we add the relation(s) listed in the second column.
+\item[(T4)] For each subdiagram of $\Gamma$ of the form shown in the first column of \ref{table2}, we add the relation(s) listed in the second column.
 \end{enumerate}
@@
 
-\begin{table}[h] 
+\begin{table}[h] \label{table2}
 \begin{tabular}{| p{3.5cm} | p{7cm} |}
@@
 \end{tabular}
-\caption{(T4) Relations} \label{table2}
+\caption{(T4) Relations}
 \end{table}

### 2014-09-25 Paper.tex
New Paragraph

@@
 Section \ref{sec:main_result} will provide the proof that the Artin group defined for a diagram $\Gamma$ is invariant up to isomorphism under mutations of $\Gamma$.
-Finally, in Section \ref{sec:affine}, we will state a conjecture which could extend the main result to diagrams of affine type.
-\\
+Finally, in Section \ref{sec:affine}, we will state a conjecture which could extend the main result to diagrams of affine type.\\
+
+In the process of writing this paper, we became aware of related results obtained independently by Grant and Marsh in \cite{GM14} and Qiu in \cite{Q14}.
+Using different approaches, the two papers found relations for the Artin group in the simply-laced cases.
+However, their relations differ from the ones used in our paper, and our approach to the problem is more combinatorial than the more topological approaches found in \cite{Q14} and \cite{GM14}.
 

### 2014-09-25 Paper.tex
Aaron's Suggestion

@@
 In the process of writing this paper, we became aware of related results obtained independently by Grant and Marsh in \cite{GM14} and Qiu in \cite{Q14}.
-Using different approaches, the two papers found relations for the Artin group in the simply-laced cases.
-However, their relations differ from the ones used in our paper, and our approach to the problem is more combinatorial than the more topological approaches found in \cite{Q14} and \cite{GM14}.
+Using different approaches, the two papers found relations for the Artin group in simply-laced diagrams.
+However, their relations differ from the ones used in our paper, and we show that our results hold for all diagrams of finite type.
+Furthermore, our approach to the problem is more combinatorial than the topological approaches found in \cite{Q14} and \cite{GM14}.
 

### 2014-10-11 Paper.tex
New Bibliography

@@
 \usepackage{enumerate}
-\usepackage{natbib}
 \usepackage[mathscr]{euscript}
@@
 
-\bibliography{References}
-\bibliographystyle{alpha}
+\begin{thebibliography}{9}
+\bibitem{BM13}
+Michael Barot and Robert J. Marsh,
+``Reflection Group Presentations Arising from Cluster Algebras,''
+arXiv: 1112.2300v2, 2013
+
+\bibitem{C06}
+Ruth Charney,
+``An Introduction to Right-Angled Artin Groups,''
+arXiv:math/0610668, 2006
+
+\bibitem{FT13}
+A. Felikson and P. Tumarkin,
+``Coxeter groups and their quotients arising from cluster algebras,''
+arXiv:1307.0672v2, 2013
+
+\bibitem{FZ02}
+Sergey Fomin and Andrei Zelevinsky,
+``Cluster Algebras I: Foundations,''
+\textit{J. Amer. Math. Soc.}, 15, 497-529, 2002
+
+\bibitem{FZ03}
+Sergey Fomin and Andrei Zelevinsky,
+``Cluster Algebras II: Finite type classification,''
+\textit{Invent. Math.}, 154, 63-121, 2003
+
+\bibitem{FN61}
+R. Fox and L. Neuwirth,
+``The Braid Groups,''
+\textit{Mathematica Scandinavica}, 119-126, 1961
+
+\bibitem{GM14}
+Joseph Grant and Robert J. Marsh
+``Braid groups and quiver mutation,''
+arXiv:1408.5267, 2014
+
+\bibitem{Q14}
+Y. Qiu,
+``On the spherical twists on 3-Calabi-Yau categories from marked surfaces,''
+arXiv:1407.0806, 2014
+
+\end{thebibliography}
 

### 2014-10-11 Paper.tex
More Changes

@@
 \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+    sep={40pt,between origins}] at (0,0)
   {
@@
     \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
+    sep={40pt,between origins}] at (4,0)
   {
@@
  \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+    sep={40pt,between origins}] at (0,0)
   {
@@
  \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (5,0)
+    sep={40pt,between origins}] at (5,0)
   {
@@
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (9,0)
+    sep={40pt,between origins}] at (9,0)
   {
@@
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+    sep={40pt,between origins}] at (0,0)
   {
@@
     \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
+    sep={40pt,between origins}] at (4,0)
   {
@@
     \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+    sep={40pt,between origins}] at (0,0)
   {
@@
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (4,0)
+    sep={40pt,between origins}] at (4,0)
   {
@@
     \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+    sep={25pt,between origins}] at (0,0)
   {
@@
     \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (8,0)
+    sep={25pt,between origins}] at (8,0)
   {
@@
    \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={25pt,between origins},nodes={asymmetrical rectangle}] at (0,0)
+    sep={25pt,between origins}] at (0,0)
   {
@@
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
-sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+sep={40pt,between origins}] at (6,0)
 {
@@
    \matrix[matrix of math nodes,column sep={25pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (10,0)
+    sep={40pt,between origins}] at (10,0)
   {
@@
 \matrix[matrix of math nodes,column sep={40pt,between origins},row
-    sep={40pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+    sep={40pt,between origins}] at (6,0)
   {
@@
 \matrix[matrix of math nodes,column sep={60pt,between origins},row
-    sep={60pt,between origins},nodes={asymmetrical rectangle}] at (6,0)
+    sep={60pt,between origins}] at (6,0)
   {

### 2015-08-20 Paper.tex
changed satifying to satisfying

@@
 \end{center}
-
 \caption{Mutation of $\Gamma$ at a node k}\label{mutation}
@@
 
-\begin{thebibliography}{9}
-\bibitem{BM13}
-Michael Barot and Robert J. Marsh,
-``Reflection Group Presentations Arising from Cluster Algebras,''
-arXiv: 1112.2300v2, 2013
-
-\bibitem{C06}
-Ruth Charney,
-``An Introduction to Right-Angled Artin Groups,''
-arXiv:math/0610668, 2006
-
-\bibitem{FT13}
-A. Felikson and P. Tumarkin,
-``Coxeter groups and their quotients arising from cluster algebras,''
-arXiv:1307.0672v2, 2013
-
-\bibitem{FZ02}
-Sergey Fomin and Andrei Zelevinsky,
-``Cluster Algebras I: Foundations,''
-\textit{J. Amer. Math. Soc.}, 15, 497-529, 2002
-
-\bibitem{FZ03}
-Sergey Fomin and Andrei Zelevinsky,
-``Cluster Algebras II: Finite type classification,''
-\textit{Invent. Math.}, 154, 63-121, 2003
-
-\bibitem{FN61}
-R. Fox and L. Neuwirth,
-``The Braid Groups,''
-\textit{Mathematica Scandinavica}, 119-126, 1961
-
-\bibitem{GM14}
-Joseph Grant and Robert J. Marsh
-``Braid groups and quiver mutation,''
-arXiv:1408.5267, 2014
-
-\bibitem{Q14}
-Y. Qiu,
-``On the spherical twists on 3-Calabi-Yau categories from marked surfaces,''
-arXiv:1407.0806, 2014
+\begin{thebibliography}{Cha06}
+
+\bibitem[BM13]{BM13}
+Michael Barot and Robert~J. Marsh.
+\newblock Reflection group presentations arising from cluster algebras.
+\newblock arXiv: 1112.2300v2, 2013.
+
+\bibitem[Cha06]{C06}
+Ruth Charney.
+\newblock An introduction to right-angled artin groups.
+\newblock arXiv:math/0610668, 2006.
+
+\bibitem[FN61]{FN61}
+R.~Fox and L.~Neuwirth.
+\newblock The braid groups.
+\newblock {\em Mathematica Scandinavica}, pages 119--126, 1961.
+
+\bibitem[FT13]{FT13}
+A.~Felikson and P.~Tumarkin.
+\newblock Coxeter groups and their quotients arising from cluster algebras.
+\newblock arXiv:1307.0672v2, 2013.
+
+\bibitem[FZ02]{FZ02}
+Sergey Fomin and Andrei Zelevinsky.
+\newblock Cluster algebras I: Foundations.
+\newblock {\em J. Amer. Math. Soc.}, 15:497--529, 2002.
+
+\bibitem[FZ03]{FZ03}
+Sergey Fomin and Andrei Zelevinsky.
+\newblock Cluster algebras II: Finite type classification.
+\newblock {\em Invent. Math.}, 154:63--121, 2003.
+
+\bibitem[GM14]{GM14}
+Joseph Grant and Robert~J. Marsh.
+\newblock Braid groups and quiver mutation.
+\newblock arXiv:1408.5267, 2014.
+
+\bibitem[Qiu14]{Q14}
+Y.~Qiu.
+\newblock On the spherical twists on 3-calabi-yau categories from marked
+  surfaces.
+\newblock arXiv:1407.0806, 2014.
 

### 2015-08-21 journal-of-pure-and-applied-algebra-submission/journal-of-pure-and-applied-algebra-paper.tex
added hailees version

--- 2015-08-20 Paper.tex
@@
-\documentclass[11pt]{amsart}
+\documentclass[11pt]{elsarticle}
 
@@
 \title{Artin Group Presentations Arising from Cluster Algebras}
-\author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
-\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
+\author{Jacob Haley \fnref{haley}}
+\address{University of Notre Dame, Department of Mathematics\\
+Notre Dame IN 46556}
+
+\author{David Hemminger \fnref{hemminger}}
+\address{Duke University, Mathematics Department \\
+Box 90320, Durham NC 27708-0320}
+
+\author{Aaron Landesman \fnref{landesman}}
+\address{Harvard University, Department of Mathematics\\
+One Oxford Street, Cambridge MA 02138}
+
+\author{Hailee Peck \fnref{peck}}
+\address{Millikin University, Department of Mathematics \\
+1184 W Main St., Decatur IL 62522}
+%\ead{jhaley3@nd.edu}
+%\ead{david.hemminger@duke.edu}
+%\ead{aaronlandesman@college.harvard.com}
+%\ead{hpeck@millikin.edu}
+
+\fntext[haley]{jachaley@umich.edu}
+\fntext[hemminger]{dhemminger@math.ucla.edu}
+\fntext[landesman]{aaronlandesman@college.harvard.com}
+\fntext[peck]{hpeck@millikin.edu}
+
 \date{\today}
-\keywords{Artin group, cluster algebra, diagram representations}
+\begin{keyword} Artin group \sep
+cluster algebra \sep
+diagram mutations
+\end{keyword}
 
@@
 \section{Acknowledgements}
-\thanks{This work was supported by the RTG grant NSF/DMS-1148634.
+This work was supported by the RTG grant NSF/DMS-1148634.
 We would also like to thank the University of Minnesota School of Mathematics for hosting us.
@@
 We thank Emily Gunawan for her useful comments on our work.
-We also thank Vic Reiner for motivating this problem.}
+We also thank Vic Reiner for motivating this problem.
+
+\vspace{0.5cm}
 

### 2016-09-29 Paper.tex
Minor Changes
made simple edits from referee report

@@
 \author{Jacob Haley, David Hemminger, Aaron Landesman, Hailee Peck}
-\email{jhaley3@nd.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
+\email{jachaley@umich.edu, david.hemminger@duke.edu, aaronlandesman@college.harvard.com, hpeck@millikin.edu}
 \date{\today}
@@
 Since then, the study of cluster algebras has provided a motivation for applications in various other areas of mathematics, including quiver representations.
-Of particular interest were \textit{finite type} cluster algebras, those with a finite number of distinguished generators.
+Of particular interest were \textit{finite type} cluster algebras, which we define precisely below.
 In the sequel to their introductory paper (\cite{FZ03}), Fomin and Zelevinsky introduce the concept of \textit{mutation equivalence} between diagrams, proving that a connected graph is mutation equivalent to an oriented Dynkin diagram if and only if all mutation equivalent graphs have edge weights not exceeding 3.
@@
 Let $\mathbb{F} = \mathbb{Q}(u_1, u_2, \ldots, u_n)$ be the field of rational functions in $n$ indeterminates over $\mathbb{Q}$.
-We will define an \textit{initial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetric matrix.
+We will define an \textit{initial seed} for the cluster algebra to be a fixed pair $(\textbf{x}, B)$, where $\textbf{x} = \{x_1, \ldots, x_n\}$ is a free generating set of $\mathbb{F}$ and $B$ is an $n \times n$ skew-symmetrisable matrix.
 Define $x_k^{\prime} \in \mathbb{F}$ by the \textit{exchange relation}
@@
 \begin{itemize}
-\item Reverse the orientations of all edges in $\Gamma(B)$ incident to $k$ (leaving the weights unchanged)
+\item Reverse the orientations of all edges in $\Gamma(B)$ incident to $k$ (leaving the weights unchanged).
 \item For any path in $\Gamma(B)$ of form $i \xrightarrow{a} k \xrightarrow{b} j$ (i.e.
@@
 \end{itemize}
-Furthermore, for a chordless cycle $C : i_0 \rightarrow i_1 \rightarrow \cdots \rightarrow i_{d-1} \rightarrow i_0$ and for $a = 0,1,2,\ldots, d-1$, define \textbf{$r\left(i_a, i_{a+1}\right) = s_{i_a}s_{i_{a+1}} \cdots s_{i_{a+d-1}}s_{i_{a+d-2}} \cdots s_{i_{a+1}}$}.\\
+Furthermore, for a chordless cycle $C : i_0 \rightarrow i_1 \rightarrow \cdots \rightarrow i_{d-1} \rightarrow i_0$ and for $a = 0,1,2,\ldots, d-1$, define \textbf{$r\left(i_a, i_{a+1}\right) = s_{i_a}s_{i_{a+1}} \cdots s_{i_{a+d-1}}s_{i_{a+d-2}} \cdots s_{i_{a+1}}$}, where indices are considered $\bmod d.$\\
 
@@
 \item{(R3)(a)} If all the weights in the edges of $C$ are $1$, then $r(i_a, i_{a+1})^2 = e$
-\item{(R3)(b)} If $C$ has some edges of weight $2$, then $r(i_a, i_{a+1})^k = e$ where $k = 4-w_a$ and $w_a$ is the weight of the edge $i_a\--\ i_{a-1}$
+\item{(R3)(b)} If $C$ has some edges of weight $2$, then $r(i_a, i_{a+1})^k = e$ where $k = 4-w_a$ and $w_a$ is the weight of the edge joining $i_a$ and $i_{a-1}$
 \end{itemize}
@@
 \label{chordlesscycle}
-A {\it chordless cycle} of an unoriented graph $G$ is a connected subgraph $H \subset G$ such that the number of vertices in $H$ is equal to the number of edges in $H,$ and the edges in $H$ form a single cycle.
+A {\it chordless cycle} of an unoriented graph $G$ is a connected induced subgraph $H \subset G$ such that the number of vertices in $H$ is equal to the number of edges in $H,$ and the edges in $H$ form a single cycle.
 \end{defn}
@@
 \label{cycle_types}
-\cite[Proposition 2.1]{BM13} Let $\Gamma$ be a diagram of finite type.
+\cite[Proposition 9.7]{FZ03} Let $\Gamma$ be a diagram of finite type.
 Then, a chordless cycle in the unoriented graph of $\Gamma$ is cyclically oriented in $\Gamma$.
@@
 In order to prove our main result, Theorem ~\ref{thm:main}, we must first define the Artin group associated to a finite type diagram.
-This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require relation $(R1),$ i.e., $s_i^2 = e.$ Since Artin Groups are very similar to Coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
+This definition will be similar to that made in \cite{BM13} at the beginning of Section 3, except that we shall not require relation $(R1),$ i.e., $s_i^2 = e.$ Since Artin groups are very similar to Coxeter groups, with the caveat that the generators are not involutions, we will be able to use these modified relations to great effect.
 
@@
 so that all edges have weight 1.
-Then if W is a group generated by $s_{1}, \dots, s_{n}$ satisfying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
+Then if A is a group generated by $s_{1}, \dots, s_{n}$ satisfying the relations (T2) and $t(i_{a}, i_{a+1}) = e$ for some a $\in \{1, \dots, d\}$, all of the relations in (T3) hold for C.
 \end{lem}
@@
 \noindent is a group homomorphism as well.
-By Lemma \ref{lem:op_homomorphism}, there exist two well-defined homomorphisms $\Delta\colon A_{\Gamma}\rightarrow A_\Gamma^{op}$ defined by $\Delta(s_i) = q_i^{-1}$ and $\Delta^\prime\colon A_{\left(\Gamma^\prime\right)^{op}} \rightarrow A_{\Gamma^\prime}$ defined by $\Delta^\prime(u_i) = r_i^{-1}$.
+By Lemma \ref{lem:op_homomorphism}, there exist two well-defined homomorphisms $\Delta\colon A_{\Gamma}\rightarrow A_{\Gamma^{op}}$ defined by $\Delta(s_i) = q_i^{-1}$ and $\Delta^\prime\colon A_{\left(\Gamma^\prime\right)^{op}} \rightarrow A_{\Gamma^\prime}$ defined by $\Delta^\prime(u_i) = r_i^{-1}$.
 We then have a homomorphism
 
-$$\psi = \Delta^\prime\circ\varphi_{op}\circ\Delta\colon A(\Gamma)\rightarrow A(\Gamma^{op})\rightarrow A(\left(\Gamma^{op}\right)^{\prime}) \rightarrow A(\Gamma^{\prime})$$
+$$\psi = \Delta^\prime\circ\varphi_{op}\circ\Delta\colon A_\Gamma \rightarrow A_{\Gamma^{op}}\rightarrow A_{\left(\Gamma^{op}\right)^{\prime}} \rightarrow A_{\Gamma^{\prime}}$$
 
@@
 &= s_3s_4^{-1}s_1^{-1}s_2s_1s_4\\
-&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &\text{by} t(3,4)\\
+&= s_4^{-1}\underline{s_1^{-1}s_2s_1}s_4s_3 &\text{by } t(3,4)\\
 &= s_4^{-1}s_2s_1s_2^{-1}s_4s_3\\

### 2016-10-21 Paper.tex
Corrections

@@
 They also proved that this Coxeter group presentation is invariant up to isomorphism under the mutation equivalence relation.
-That is, given a diagram $\Gamma$ and a diagram mutation equivalent to $\Gamma$, denoted $\Gamma^{\prime} = \mu_k(\Gamma)$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group presentations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
+That is, given a diagram $\Gamma$ and a diagram $\Gamma^{\prime}$ which is mutation equivalent to $\Gamma$, they proved that $W_{\Gamma} \cong W_{\Gamma^{\prime}}$, where $W_{\Gamma}$ and $W_{\Gamma^{\prime}}$ are the group presentations corresponding to $\Gamma$ and $\Gamma^{\prime}$, respectively.
 
@@
 \end{displaymath}
-Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\boldsymbol{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
+Then, given an initial seed $(\textbf{x}, B)$ and $k \in {1,2,\ldots,n}$, we can define a \textit{mutation} of the seed at $k$, denoted $\mu_k(\textbf{x}, B) = (\textbf{x}^{\prime}, B^{\prime})$ where:
 \begin{displaymath}
@@
 Note that if we add the additional relation $(R1)$ as defined at the beginning of Section 3 of \cite{BM13} (namely, if we add $s_i^2 = e$ for all vertices $i$ in $\Gamma$), then we will precisely obtain the group $W_\Gamma$ as defined at the beginning of Section 3 in \cite{BM13}.
+(It is clear that we obtain the relations of the form $(R2)$ in $W_{\Gamma}$ from the $(T2)$ relations in $A_{\Gamma}$, and we obtain the relations of the form $(R3)(a)$ and $(R3)(b)$ for $k = 1$ in $W_{\Gamma}$ from the $(T3)$ relations in $A_{\Gamma}$.
+From here, we obtain the remaining $(R3)(b)$ relations in $W_{\Gamma}$ by Lemmas 4.2 and 4.3 in \cite{BM13}.
 \end{rem}
@@
 \item $\langle s_2,s_3 \rangle^3 = \langle s_3,s_2 \rangle^3,$ i.e., $s_2s_3s_2 = s_3s_2s_3$
-\item $\langle s_3,s_4 \rangle^4 = \langle s_4,s_3 \rangle^4,$ i.e., $s_3s_4s_3s_4 = s_4s_3s_4s_3$              
+\item $\langle s_3,s_1 \rangle^4 = \langle s_1,s_3 \rangle^4,$ i.e., $s_3s_1s_3s_1 = s_1s_3s_1s_3$              
 \end{itemize}
@@
 \begin{itemize}
-\item $s_1s_2^{-1}s_3^{-1}s_2s_1^{-1}s_2^{-1}s_3s_2 = e$
-
-\item $s_2s_3^{-1}s_1^{-1}s_3s_2^{-1}s_3^{-1}s_1s_3 =e$
+\item $s_1s_2^{-1}s_3s_2s_1^{-1}s_2^{-1}s_3^{-1}s_2 = e$
+
+\item $s_2s_3^{-1}s_1s_3s_2^{-1}s_3^{-1}s_1^{-1}s_3 =e$
 
@@
 &= s_{k}^{-1}s_{i}^{-1}s_{j}s_{i}s_{k}s_{i}^{-1}s_{j}^{-1}s_{i} \\
-&= s_{k}^{-1}p(k, i)s_{k}p(k, i)^{-1}
+&= s_{k}^{-1}p(k, i)s_{k}p(k, i)^{-1},
 \end{align*}
+and from the fact that $s_{k}^{1}p(k,i)s_{k}p(k,i)^{-1} = e$ if and only if $$p(k,i)s_{k} = s_k(s_{k}^{-1}p(k,i)s_{k}p(k,i)^{-1})p(k,i) = s_kp(k,i)$$.
 \end{proof}
@@
 
+Carrying out computations similar to those in Section 6, one can check directly that with this choice of relations, we have that for each diagram $\Gamma$ occuring in the first column of Table \ref{table2} and for each vertex $k$ of $\Gamma$, the map $\phi: A_{\mu_k(\Gamma)} \rightarrow A_{\Gamma}$ defined as in Proposition 6.2 is an isomorphism.
+Thus we conjecture the following:
+
 \begin{conj}
@@
 \bibitem[BM13]{BM13}
-Michael Barot and Robert~J. Marsh.
+M.~Barot and R.~Marsh.
 \newblock Reflection group presentations arising from cluster algebras.
@@
 \bibitem[Cha06]{C06}
-Ruth Charney.
+R.~Charney.
 \newblock An introduction to right-angled artin groups.
@@
 \bibitem[FZ02]{FZ02}
-Sergey Fomin and Andrei Zelevinsky.
+S.~Fomin and A.~Zelevinsky.
 \newblock Cluster algebras I: Foundations.
@@
 \bibitem[FZ03]{FZ03}
-Sergey Fomin and Andrei Zelevinsky.
+S.~Fomin and A.~Zelevinsky.
 \newblock Cluster algebras II: Finite type classification.
@@
 \bibitem[GM14]{GM14}
-Joseph Grant and Robert~J. Marsh.
+J.~Grant and R.~Marsh.
 \newblock Braid groups and quiver mutation.
